---
title: "dry_bean_yield_2023"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

# **Load libraries**

```{r message=FALSE, warning=FALSE}

#Set work directory
setwd("/Users/ey239/Github/IMT/rmarkdowns")

#Load packages 
library(tidyverse) ##install.packages("tidyverse")
library(knitr)
library(patchwork) ##install.packages("patchwork")
library(skimr)     ##install.packages("skimr")
library(readxl)
library(janitor) ##install.packages("janitor")

library(kableExtra) ##install.packages("kableExtra")
library(webshot) ##install.packages("webshot")
webshot::install_phantomjs()
library(viridis) ##install.packages("viridis")
library(lme4) ##install.packages("lme4")
library(lmerTest) ##install.packages("lmerTest")
library(emmeans) ##install.packages("emmeans")
library(rstatix) ##install.packages("rstatix")
#library(Matrix) ##install.packages("Matrix")
library(multcomp) ##install.packages("multcomp")
library(multcompView) ##install.packages("multcompView")
library(ggResidpanel) ##install.packages("ggResidpanel")
#library(car)
#library(TMB)  ##install.packages("TMB")
#library(glmmTMB)  ##install.packages("glmmTMB")
#library(DHARMa)  ##install.packages("DHARMa")

#Load Functions
MeanPlusSe<-function(x) mean(x)+plotrix::std.error(x)

find_logw0=function(x){c=trunc(log(min(x[x>0],na.rm=T)))
d=exp(c)
return(d)}
```

<br>

# **Load and Clean Data**
### **Load individual datasets**
```{r message=FALSE, warning=FALSE}


fh_raw_2023 <- read_excel("~/Github/IMT/raw-data/farmhub_raw_2023.xlsx", 
na = c("na")) # convert na to NA
kable(head(fh_raw_2023))

str(fh_raw_2023$seed_weight)

fh_raw_2024 <- read_excel("~/Github/IMT/raw-data/farmhub_raw_2024.xlsx", 
na = c("na")) # convert na to NA
kable(head(fh_raw_2024))

str(fh_raw_2024$seed_weight)

cu_raw_2023 <- read_excel("~/Github/IMT/raw-data/cornell_raw_2023.xlsx", 
na = c("na")) # convert na to NA
kable(head(cu_raw_2023))

str(cu_raw_2023$seed_weight)

cu_raw_2024 <- read_excel("~/Github/IMT/raw-data/cornell_raw_2024.xlsx", 
na = c("na")) # convert na to NA
kable(head(cu_raw_2024))

str(cu_raw_2024$seed_weight)

me_raw_2023 <- read_excel("~/Github/IMT/raw-data/maine_raw_2023.xlsx", 
                          na = c("na")) # convert na to NA
str(me_raw_2023$seed_weight)

me_raw_2024 <- read_excel("~/Github/IMT/raw-data/maine_raw_2024.xlsx", 
                          na = c("na")) # convert na to NA
kable(head(me_raw_2024))

vt_raw_2023 <- read_excel("~/Github/IMT/raw-data/vermont_raw_2023.xlsx")
kable(head(vt_raw_2023))

vt_raw_2024 <- read_excel("~/Github/IMT/raw-data/vermont_raw_2024.xlsx", 
                          na = c("na")) # convert na to NA
kable(head(vt_raw_2024))

wi_raw_2023 <- read_excel("~/Github/IMT/raw-data/wisconsin_raw_2023.xlsx", 
                          na = c("na")) # convert na to NA
kable(head(wi_raw_2023))

wi_raw_2024 <- read_excel("~/Github/IMT/raw-data/wisconsin_raw_2024.xlsx", 
                          na = c("na")) # convert na to NA
kable(head(wi_raw_2024))

```



<br>

### **Combine all datasets and clean**
```{r}

#combine datasets
datasets <- list(
  fh_raw_2023, fh_raw_2024, cu_raw_2023, cu_raw_2024,
  me_raw_2023, me_raw_2024, vt_raw_2023, vt_raw_2024,
  wi_raw_2023, wi_raw_2024
)

datasets_cleaned <- lapply(datasets, function(df) {
  df |>
    mutate(across(c(seed_weight, intrarow_weed_biomass, interrow_weed_biomass), as.numeric))
})

all_raw <- bind_rows(datasets_cleaned)

#Standardaze column names, convert to factors, check for outliers of variable**
all_clean <- clean_names(all_raw) |>  
  rename ('mowing'= treatment,'weeds'= microplot) |> 
  mutate(across(c(mowing, block, plot, weeds, location), as.factor)) 
  #mutate(is_outlier = bean_yield < (quantile(bean_yield, 0.25) - 1.5 * IQR(bean_yield)) |
                       #bean_yield > (quantile(bean_yield, 0.75) + 1.5 * IQR(bean_yield)))


#select and convert data for Yield analysis
  
all_yield_clean <-all_clean |>              
  #filter(is_outlier == FALSE) |>              # Keep rows where beanyd is not an outlier
  filter(weeds %in% c("SW", "M")) |>       # Keep rows where SW and M are microplots
  mutate(bean_yield_adj_bu_acre = (((bean_yield/454)/(16.4/43560))/60)* ((100-0.00001)/(100-14))) |> 
  mutate(bean_yield_adj_lbs_acre = ((bean_yield/454)/(16.4/43560))* ((100-0.00001)/(100-14))) |>
  mutate(bean_yield_adj_kg_ha = ((bean_yield/454)/(16.4/43560))* 1.12085 *((100-0.00001)/(100-14)))
kable(head(all_yield_clean)) 

```

<br>

# **Assumptions**
## **Levene's test**
```{r}
levene_test((beanyd_adj_kg_ha) ~ loc, data = all_yield_clean_2023)
```

# **Model Testing**

### **location random**
```{r}
all_yield_random  <- lmer(bean_yield_adj_kg_ha ~  mowing*weeds + (1|location) + (1|location:block)+  (1|location:block:mowing)  , data = all_yield_clean)

resid_panel(all_yield_random)
```


### **location fixed**
```{r}
all_yield_fixed <- lmer(bean_yield_adj_kg_ha ~ location*mowing*weeds + (1|location:block)+  (1|location:block:mowing), data = all_yield_clean)


resid_panel(all_yield_fixed)
```

The residuals apppear better with location as a fixed effect

# **ANOVA table**
```{r}
 all_yield_fixed |> 
  joint_tests() |> 
  kable()  
```

# **Means comparison of yield**

```{r message=FALSE}
all_yield_means <- 
 emmeans(all_yield_fixed, ~ location * mowing * weeds)
# Optional: Adjust for multiple comparisons (e.g., using Tukey's method)

pairwise_comparisons<- pairs(all_yield_means) 
kable(head(pairwise_comparisons))
```


### **Tukey method for comparing means**
```{r}
#Tukey method for comparing means
#mowing
cld_mowing_tukey <-cld(emmeans(all_yield_fixed, ~  mowing, type="response"), Letters = letters, sort = TRUE, reversed = TRUE)
cld_mowing_tukey

#weeds
cld_weeds_tukey <-cld(emmeans(all_yield_fixed_2023, ~  weeds, type = "response"), Letters = letters, sort = FALSE, reversed = FALSE)
cld_weeds_tukey

#mowing|weeds
cld_weeds_mowing_tukey <-cld(emmeans(all_yield_fixed_2023, ~  weeds|mowing, type = "response"), Letters = letters, sort = FALSE, reversed = FALSE)
cld_weeds_mowing_tukey

#loc|weeds
cld_weeds_loc_tukey <-cld(emmeans(all_yield_fixed, ~  weeds|location, type = "response"), Letters = letters, sort = TRUE, reversed = TRUE)
cld_weeds_loc_tukey

#loc|weeds
cld_mowing_loc_tukey <-cld(emmeans(all_yield_fixed, ~  mowing|location, type = "response"), Letters = letters, sort = TRUE, reversed = TRUE)
cld_mowing_loc_tukey

#loc|weeds|loc
cld_mowing_weeds_loc_tukey <-cld(emmeans(all_yield_fixed_2023, ~  mowing|weeds|loc, type = "response"), Letters = letters, sort = FALSE, reversed = FALSE)
cld_mowing_weeds_loc_tukey

```
<br>

### **Fisher's method for comparing means**
```{r}
#Fisher's method for comparing means

#mowing
cld_mowing_fisher <-cld(emmeans(all_yield_fixed_2023, ~  mowing, type = "response"), Letters = letters, sort = FALSE, adjust="none", reversed=FALSE)
cld_mowing_fisher

#weeds
cld_weeds_fisher <- cld(emmeans(all_yield_fixed_2023, ~  weeds, type = "response"), Letters = letters, sort = FALSE, adjust="none", reversed=FALSE)
cld_weeds_fisher

#mowing|weeds
cld_mowing_weeds_fisher <-cld(emmeans(all_yield_fixed_2023, ~  mowing|weeds, 
                              type = "response"), Letters = letters, 
                              sort = FALSE, adjust="none", reversed=FALSE)
cld_mowing_weeds_fisher

#mowing|weeds|loc
cld_mowing_weeds_loc_fisher <-cld(emmeans(all_yield_fixed_2023, ~  mowing|weeds|loc, type = "response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)
cld_mowing_weeds_loc_fisher

```

<br>

# **FIGURES**

## **Mowing**

```{r message=FALSE}
all_yield_clean |> 
  left_join(cld_mowing_tukey) |> 
  ggplot(aes(x = mowing, y = bean_yield_adj_kg_ha, fill = mowing)) +
  stat_summary(geom = "bar", fun = "mean", width = 0.7) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2) +
  stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5) +
  labs(
    x = "Timing of Mowing",
    y = expression("Dry bean yield" ~ (kg ~ ha^{-1})),
    title = str_c("The influence of interrow mowing on dry bean yield"),
    subtitle = expression(italic("P = 0.07"))) +
  
  scale_x_discrete(labels = c("As-needed\nmowing", "Early\nmowing", "Late\nmowing", "No\nmowing")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_viridis(discrete = TRUE, option = "D", direction = -1, end = 0.9, begin = 0.1) +
   theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 12)
  )
ggsave("yield_plot_mowing.png", width = 8, height = 6, dpi = 300)
```
<br>

## **weeds**
```{r message=FALSE}
all_yield_clean_2023 |> 
  left_join(cld_weeds_fisher) |> 
  ggplot(aes(x = weeds, y = beanyd_adj_kg_ha, fill = weeds)) +
  stat_summary(geom = "bar", fun = "mean", width = 0.7) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2) +
  stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5) +
  labs(
    x = "Weediness",
    y = expression("Dry bean yield" ~ (kg ~ ha^{-1})),
    title = str_c("The influence of weed level on dry bean yield"),
    subtitle = expression(italic("Not signficant"))) +
  scale_x_discrete(labels = c("Ambient weeds", "Ambient + Surrogate weeds")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_viridis(discrete = TRUE, option = "D", direction = -1, end = 0.9, begin = 0.1) +
   theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 12)
  )
ggsave("yield_plot_weeds.png", width = 8, height = 6, dpi = 300)
```
<br>

## **mowing|weeds**

```{r message=FALSE}
all_yield_clean |> 
  left_join(cld_mowing_loc_tukey) |> 
  ggplot(aes(x = mowing, y = bean_yield_adj_kg_ha, fill = mowing)) +
  facet_wrap(~location,  nrow = 1,  labeller = labeller(location = c("CU" = "Aurora, NY", "FH" = "Hurley, NY", "ME" = "Orono, ME", "VT" = "Alburgh, VT", "WI" = "Arlington, WI"))) +
  stat_summary(geom = "bar", fun = "mean", width = 0.7) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2) +
  stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5) +
  labs(
    x = "Timing of mowing",
    y = expression("Dry bean yield" ~ (kg ~ ha^{-1})),
    title = str_c("The influence of interrow mowing on dry bean yield across study lcoations"),
    subtitle = expression(italic("P =0.01"))) +
  scale_x_discrete(labels = c("As-needed\nmowing", "Early\nmowing", "Late\nmowing", "No\nmowing")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_viridis(discrete = TRUE, option = "D", direction = -1, end = 0.9, begin = 0.1) +
   theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 12)
  )
ggsave("yield_plot_mowing_location.png", width = 12, height = 6, dpi = 300)
```

<br>

## **mowing|weeds|loc**

```{r message=FALSE}
all_yield_clean_2023 |> 
  left_join(cld_mowing_weeds_loc_fisher) |> 
  ggplot(aes(x = mowing, y = beanyd_adj_kg_ha, fill = mowing)) +
  facet_grid(weeds ~ loc, labeller = labeller(
    loc = c("CU" = "Aurora, NY", "FH" = "Hurley, NY", "ME" = "Orono, ME", "VT" = "Alburgh, VT", "WI" = "Arlington, WI"),
    weeds = c("M" = "Ambient Weeds", "SW" = "Ambient + Surrogate Weeds")
  )) +
  stat_summary(geom = "bar", fun = "mean", width = 0.7) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2) +
  stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=4.5,vjust=-0.5) +
  labs(
    x = "Timing of mowing",
    y = expression("Dry bean yield" ~ (kg ~ ha^{-1})),
    title = str_c("The influence of mowing on dry bean yield across locations and weed levels"),
    subtitle = expression(italic("P = 0.049"))) +
  scale_x_discrete(labels = c("As-needed\nmowing", "Early\nmowing", "Late\nmowing", "No\nmowing")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_viridis(discrete = TRUE, option = "D", direction = -1, end = 0.9, begin = 0.1) +
   theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 12)
  )
ggsave("yield_plot_mowing_weeds_loc.png", width = 12, height = 6, dpi = 300)
```



