---
title: "IMT Bean yield"
output: github_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries

```{r message=FALSE, warning=FALSE}

#Set work directory
setwd("/Users/ey239/Github/IMT/rmarkdowns")

#Load packages 
library(tidyverse) ##install.packages("tidyverse")
library(knitr)
library(patchwork) ##install.packages("patchwork")
library(skimr)     ##install.packages("skimr")
library(readxl)
library(janitor) ##install.packages("janitor")

library(kableExtra) ##install.packages("kableExtra")
library(webshot) ##install.packages("webshot")
webshot::install_phantomjs()
library(viridis) ##install.packages("viridis")
library(lme4) ##install.packages("lme4")
library(lmerTest) ##install.packages("lmerTest")
library(emmeans) ##install.packages("emmeans")
library(rstatix) ##install.packages("rstatix")
#library(Matrix) ##install.packages("Matrix")
library(multcomp) ##install.packages("multcomp")
library(multcompView) ##install.packages("multcompView")
library(ggResidpanel) ##install.packages("ggResidpanel")
#library(car)
#library(TMB)  ##install.packages("TMB")
library(glmmTMB)  ##install.packages("glmmTMB")
library(DHARMa)  ##install.packages("DHARMa")
library(performance) ##install.packages("performance")
library(WrensBookshelf)##install.packages("WrensBookshelf")
#Load Functions
MeanPlusSe<-function(x) mean(x)+plotrix::std.error(x)

find_logw0=function(x){c=trunc(log(min(x[x>0],na.rm=T)))
d=exp(c)
return(d)}
```


<br>

# Load and clean data

## Load data

``` {r}
combined_raw <- read_excel("~/Github/IMT/raw-data/combined_raw.xlsx")
kable(head(combined_raw))

```




##Clean data
###ECOBEAN
```{r}
#Standardaze column names, convert to factors, check for outliers of variable**
clean_combined <- clean_names(combined_raw) |>  
  rename(mowing = treatment, weeds = microplot) |> 
  mutate(across(c(year, location, site_year, mowing, block, plot, weeds), as.factor),
         bean_yield = as.numeric(as.character(bean_yield))) |>  # Convert to numeric
  mutate(is_outlier = bean_yield < (quantile(bean_yield, 0.25, na.rm = TRUE) - 1.5 * IQR(bean_yield, na.rm = TRUE)) |
                     bean_yield > (quantile(bean_yield, 0.75, na.rm = TRUE) + 1.5 * IQR(bean_yield, na.rm = TRUE))) |> 
  mutate(is_outlier = replace_na(is_outlier, FALSE))  # Ensure logical values

bean_yield_clean <- clean_combined |>  
  filter(weeds %in% c("SW", "M")) |> # Keep only SW and M microplots
  filter(!is.na(bean_yield)) |>  # Remove NA values
  filter(is_outlier == FALSE) |>  # Remove outliers
  mutate(
    bean_yield_adj_bu_acre = (((bean_yield / 454) / (16.4 / 43560)) / 60) * ((100 - 0.00001) / (100 - 14)),
    bean_yield_adj_lbs_acre = ((bean_yield / 454) / (16.4 / 43560)) * ((100 - 0.00001) / (100 - 14)),
    bean_yield_adj_kg_ha = ((bean_yield / 454) / (16.4 / 43560)) * 1.12085 * ((100 - 0.00001) / (100 - 14))
  )
kable(bean_yield_clean)

```

###FARMHUB REPORT 
```{r}
#Standardaze column names, convert to factors, check for outliers of variable**
clean_combined <- clean_names(combined_raw) |>  
  rename(mowing = treatment, weeds = microplot) |> 
  mutate(across(c(year, location, site_year, mowing, block, plot, weeds), as.factor),
         bean_yield = as.numeric(as.character(bean_yield))) |>  # Convert to numeric
  mutate(is_outlier = bean_yield < (quantile(bean_yield, 0.25, na.rm = TRUE) - 1.5 * IQR(bean_yield, na.rm = TRUE)) |
                     bean_yield > (quantile(bean_yield, 0.75, na.rm = TRUE) + 1.5 * IQR(bean_yield, na.rm = TRUE))) |> 
  mutate(is_outlier = replace_na(is_outlier, FALSE))  # Ensure logical values

bean_yield_clean_fh <- clean_combined |>  
  filter(weeds %in% c("SW", "M")) |> # Keep only SW and M microplots
  filter(location %in% c("FH", "CU")) |>
  filter(!is.na(bean_yield)) |>  # Remove NA values
  filter(is_outlier == FALSE) |>  # Remove outliers
  mutate(
    bean_yield_adj_bu_acre = (((bean_yield / 454) / (16.4 / 43560)) / 60) * ((100 - 0.00001) / (100 - 14)),
    bean_yield_adj_lbs_acre = ((bean_yield / 454) / (16.4 / 43560)) * ((100 - 0.00001) / (100 - 14)),
    bean_yield_adj_kg_ha = ((bean_yield / 454) / (16.4 / 43560)) * 1.12085 * ((100 - 0.00001) / (100 - 14))
  )
kable(bean_yield_clean_fh)

```

# Model testing
##ECOBEAN
### Lmer
Block is random
Tyler is under the impression that block should always be random and that post-hoc comparisons should use TUKEY rather the Fischer. Fisher is bogus apparently. 

```{r}

# This is better for providing generalizatins and reccomendations. 

random <- lmer(bean_yield_adj_bu_acre ~ mowing*weeds + (1|site_year) + (1|site_year:block)+  (1|site_year:block:mowing), data = bean_yield_clean)


#tyler whats up with uri being random? location*year takes into accoutn if we are concerned about only these years and locations, everything is relative to the ten means from this experiment

#random_uri <- lmer(bean_yield_adj_kg_ha  ~ mowing*weeds + location*year + (1|site_year:block)+  (1|site_year:block:mowing)  , data =  bean_yield_clean)


resid_panel(random)

simulateResiduals(random,plot = TRUE) # Residuals and normality look good
check_model(random)
```

### Joint test (anova)
```{r}
 random |> 
  joint_tests() |> 
  kable()  
```
### Anova table
```{r}
options(contrasts = c("contr.sum", "contr.poly"))
Anova(random, type = 3)
```
### Fisher compact letter display
#### Weed-control (No significant)

```{r}
cld_mowing_fisher <-cld(emmeans(random, ~  mowing , type = "response"), Letters = letters, adjust = "none",sort = TRUE, reversed=TRUE)
cld_mowing_fisher
```

#### Weeds (significant)

```{r}
cld_weeds_fisher <-cld(emmeans(random, ~  weeds , type = "response"), Letters = letters, adjust = "none",sort = TRUE, reversed=TRUE)
cld_weeds_fisher
```

##FARMHUB REPORT
### Lmer
Block is random
Tyler is under the impression that block should always be random and that post-hoc comparisons should use TUKEY rather the Fischer. Fisher is bogus apparently. 

```{r}

# This is better for providing generalizatins and reccomendations. 

random_fh <- lmer(bean_yield_adj_bu_acre ~ mowing*weeds + (1|site_year) + (1|site_year:block)+  (1|site_year:block:mowing), data = bean_yield_clean_fh)


#tyler whats up with uri being random? location*year takes into accoutn if we are concerned about only these years and locations, everything is relative to the ten means from this experiment

#random_uri <- lmer(bean_yield_adj_kg_ha  ~ mowing*weeds + location*year + (1|site_year:block)+  (1|site_year:block:mowing)  , data =  bean_yield_clean)


resid_panel(random_fh)

simulateResiduals(random_fh,plot = TRUE) # Residuals and normality look good
check_model(random_fh)
```

### Joint test (anova)
```{r}
 random_fh |> 
  joint_tests() |> 
  kable()  
```
### Anova table
```{r}
options(contrasts = c("contr.sum", "contr.poly"))
Anova(random_fh, type = 3)
```
### Fisher compact letter display
#### Weed-control (No significant)

```{r}
cld_mowing_fisher_fh <-cld(emmeans(random_fh, ~  mowing , type = "response"), Letters = letters, adjust = "none",sort = TRUE, reversed=TRUE)
cld_mowing_fisher
```

#### Weeds (significant)

```{r}
cld_weeds_fisher_fh <-cld(emmeans(random_fh, ~  weeds , type = "response"), Letters = letters, adjust = "none",sort = TRUE, reversed=TRUE)
cld_weeds_fisher
```

#Figures
##ECOBEAN

### Mowing on yield (not significant)

```{r message=FALSE}
bean_yield_clean |> 
  left_join(cld_mowing_fisher) |> 
  ggplot(aes(x = factor(mowing, levels = c("NWC", "EWC", "LWC", "AWC")), y = bean_yield_adj_bu_acre, fill = mowing)) +
  stat_summary(geom = "bar", fun = "mean", width = 0.7) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2) +
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5) +
  #geom_bar(stat="identity", position=position_dodge()) + 
  #geom_errorbar(aes(ymin=response-SE, ymax=response+SE), width=.2,
                 #position=position_dodge(.9))+
#geom_text(aes(label = trimws(.group), y = response + (SE + 30)), size = 7) +
  labs(
    x = "",
       y = expression(paste("Dry bean yield (", bu~a^{-1}, " at 13% moisture)")),
    #title = str_c("Influence of interrow weed control on weed biomass"),
    subtitle = expression(italic("Not signficant"))) +
  
  scale_x_discrete(labels = c("No\nmowing", "Early\nmowing", "Late\nmowing", "As-needed\nmowing")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_WB_d(name = "BlueberriesForSal", direction = 1) +
   theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 12),
    axis.title = element_text(size = 24),  # Increase font size of axis titles
    axis.text = element_text(size = 24),   # Increase font size of axis labels
    plot.title = element_text(size = 24, face = "bold"),  # Increase font size of title
    plot.subtitle = element_text(size = 24, face = "italic")  # Increase font size of subtitle
  
  )
ggsave("bean_yield_mowing_kgha_eco.png", width = 10, height = 8, dpi = 300)
```
### Weed level of yield (significant)

```{r message=FALSE}
bean_yield_clean |> 
  left_join(cld_weeds_fisher) |> 
  ggplot(aes(x = weeds, y = bean_yield_adj_bu_acre, fill = weeds)) +  # Fill added
  stat_summary(geom = "bar", fun = "mean", width = 0.6, position = position_dodge(width = 0.7)) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2, position = position_dodge(width = 0.7)) +
  stat_summary(geom = "text", fun = "MeanPlusSe", aes(label = trimws(.group)), 
               size = 6.5, vjust = -0.5, position = position_dodge(width = 0.7)) +
  labs(
    x = "",
    y = expression(paste("Dry bean yield (", bu~a^{-1}, " at 13% moisture)")),
  subtitle = expression(italic("P < 0.005"))
  ) +
  scale_x_discrete(labels = c("Ambient weeds", "Surrogate + ambient weeds")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_WB_d(name = "BlueberriesForSal", direction = 1) +  # Ensure correct function use
  theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 20),
    axis.title = element_text(size = 24),
    axis.text = element_text(size = 20),
    plot.title = element_text(size = 24, face = "bold"),
    plot.subtitle = element_text(size = 24, face = "italic")
  )
ggsave("bean_yield_weeds_buac_eco.png", width = 10, height = 8, dpi = 300)
```
## FARMHUB REPORT
### Mowing on yield
```{r message=FALSE}
bean_yield_clean_fh |> 
  left_join(cld_mowing_fisher_fh) |> 
  ggplot(aes(x = factor(mowing, levels = c("NWC", "EWC", "LWC", "AWC")), 
             y = bean_yield_adj_bu_acre, fill = mowing)) + 
  stat_summary(geom = "bar", fun = "mean", width = 0.6) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2) +
  labs(
    x = "",
    y = expression(paste("Dry bean yield (", bu~a^{-1}, " at 13% moisture)")),
    subtitle = expression(italic("Not signficant"))) +
  scale_x_discrete(labels = c("No\nmowing", "Early\nmowing", "Late\nmowing", "As-needed\nmowing")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_WB_d(name = "BlueberriesForSal", direction = 1) +  
  theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 12),
    axis.title = element_text(size = 24),
    axis.text = element_text(size = 24),
    plot.title = element_text(size = 24, face = "bold"),
    plot.subtitle = element_text(size = 24, face = "italic")
  )

ggsave("bean_yield_mowing_kgha_fh.png", width = 10, height = 8, dpi = 300)
```
### Weed level of yield (significant)

```{r message=FALSE}
bean_yield_clean_fh |> 
  left_join(cld_weeds_fisher_fh) |> 
  ggplot(aes(x = weeds, y = bean_yield_adj_bu_acre, fill = weeds)) +  # Fill added
  stat_summary(geom = "bar", fun = "mean", width = 0.6, position = position_dodge(width = 0.7)) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2, position = position_dodge(width = 0.7)) +
  stat_summary(geom = "text", fun = "MeanPlusSe", aes(label = trimws(.group)), 
               size = 6.5, vjust = -0.5, position = position_dodge(width = 0.7)) +
  labs(
    x = "",
    y = expression(paste("Dry bean yield (", bu~a^{-1}, " at 13% moisture)")),
  subtitle = expression(italic("P < 0.005"))
  ) +
  scale_x_discrete(labels = c("Ambient weeds", "Surrogate + ambient weeds")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_WB_d(name = "BlueberriesForSal", direction = 1) +  # Ensure correct function use
  theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 20),
    axis.title = element_text(size = 24),
    axis.text = element_text(size = 20),
    plot.title = element_text(size = 24, face = "bold"),
    plot.subtitle = element_text(size = 24, face = "italic")
  )
ggsave("bean_yield_weeds_bhac_fh.png", width = 10, height = 8, dpi = 300)
```