---
title: "IMT Bean yield"
output: github_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries

```{r message=FALSE, warning=FALSE}

#Set work directory
setwd("/Users/ey239/Github/IMT/rmarkdowns")

#Load packages 
library(tidyverse) ##install.packages("tidyverse")
library(knitr)
library(patchwork) ##install.packages("patchwork")
library(skimr)     ##install.packages("skimr")
library(readxl)
library(janitor) ##install.packages("janitor")

library(kableExtra) ##install.packages("kableExtra")
library(webshot) ##install.packages("webshot")
webshot::install_phantomjs()
library(viridis) ##install.packages("viridis")
library(lme4) ##install.packages("lme4")
library(lmerTest) ##install.packages("lmerTest")
library(emmeans) ##install.packages("emmeans")
library(rstatix) ##install.packages("rstatix")
#library(Matrix) ##install.packages("Matrix")
library(multcomp) ##install.packages("multcomp")
library(multcompView) ##install.packages("multcompView")
library(ggResidpanel) ##install.packages("ggResidpanel")
#library(car)
#library(TMB)  ##install.packages("TMB")
library(glmmTMB)  ##install.packages("glmmTMB")
library(DHARMa)  ##install.packages("DHARMa")
library(performance) ##install.packages("performance")
library(WrensBookshelf)##install.packages("WrensBookshelf")
#Load Functions
MeanPlusSe<-function(x) mean(x)+plotrix::std.error(x)

find_logw0=function(x){c=trunc(log(min(x[x>0],na.rm=T)))
d=exp(c)
return(d)}
```


<br>

# Load and clean data

## Load data

``` {r}
combined_raw <- read_excel("~/Github/IMT/raw-data/combined_raw.xlsx")
kable(head(combined_raw))

```




##Clean data
###ECOBEAN (all sites)
```{r}
## Standardize column names and convert variables
clean_combined <- combined_raw |>  
  clean_names() |>  
  rename(mowing = treatment, weeds = microplot) |> 
  mutate(
    across(c(year, location, site_year, mowing, block, plot, weeds), as.factor),
    bean_yield = as.numeric(bean_yield)  # Convert to numeric safely
  )

# Define constants for yield conversion
moisture_correction <- (100 - 0.00001) / (100 - 14)
kg_to_lb <- 2.20462
sqft_per_acre <- 43560
sample_area_sqft <- 16.4
grams_per_lb <- 454

# Filter relevant data and compute adjusted yields
bean_yield_clean <- clean_combined |>  
  filter(
    weeds %in% c("SW", "M"), 
    !is.na(bean_yield)
  ) |>  
  mutate(
    bean_yield_adj_bu_acre = (((bean_yield / grams_per_lb) / (sample_area_sqft / sqft_per_acre)) / 60) * moisture_correction,
    bean_yield_adj_lbs_acre = ((bean_yield / grams_per_lb) / (sample_area_sqft / sqft_per_acre)) * moisture_correction,
    bean_yield_adj_kg_ha = bean_yield_adj_lbs_acre / kg_to_lb
  )

# Display cleaned dataset
kable(head(bean_yield_clean))

```

###FARMHUB 2024 REPORT (Musgrave and Farmhub)
```{r}
## Standardize column names, convert to factors, and check for outliers
clean_combined <- combined_raw |>  
  clean_names() |>  
  rename(mowing = treatment, weeds = microplot) |> 
  mutate(
    across(c(year, location, site_year, mowing, block, plot, weeds), as.factor),
    bean_yield = as.numeric(bean_yield) # Convert to numeric safely
  ) 

# Define constants for yield conversion
moisture_correction <- (100 - 0.00001) / (100 - 14)
kg_to_lb <- 2.20462
sqft_per_acre <- 43560
sample_area_sqft <- 16.4
grams_per_lb <- 454

# Filter relevant data and compute adjusted yields
bean_yield_clean_fh <- clean_combined |>  
  filter(
    weeds %in% c("SW", "M"), 
    location %in% c("FH", "CU"), 
    year == "2024", 
    !is.na(bean_yield)
  ) |>  
  mutate(
    bean_yield_adj_bu_acre_fh = (((bean_yield / grams_per_lb) / (sample_area_sqft / sqft_per_acre)) / 60) * moisture_correction,
    bean_yield_adj_lbs_acre_fh = ((bean_yield / grams_per_lb) / (sample_area_sqft / sqft_per_acre)) * moisture_correction,
    bean_yield_adj_kg_ha_fh = bean_yield_adj_lbs_acre_fh / kg_to_lb
  )

# Display cleaned dataset
kable(bean_yield_clean_fh)
```
###FARMHUB REPORT (Musgrave and Farm hub, NWC only)
```{r}
# Standardize column names and convert variables
clean_combined <- combined_raw |>  
  clean_names() |>  
  rename(mowing = treatment, weeds = microplot) |> 
  mutate(
    across(c(year, location, site_year, mowing, block, plot, weeds), as.factor),
    bean_yield = as.numeric(bean_yield)  # Convert to numeric safely
  )

# Define constants for yield conversion
moisture_correction <- (100 - 0.00001) / (100 - 14)
kg_to_lb <- 2.20462
sqft_per_acre <- 43560
sample_area_sqft <- 16.4
grams_per_lb <- 454

# Filter relevant data and compute adjusted yields
bean_yield_clean_fh_wf <- clean_combined |>  
  filter(
    location %in% c("FH", "CU"),
    year == "2024",
    mowing == "NWC",
    !is.na(bean_yield)
  ) |>  
  mutate(
    bean_yield_adj_bu_acre_fh_wf = (((bean_yield / grams_per_lb) / (sample_area_sqft / sqft_per_acre)) / 60) * moisture_correction,
    bean_yield_adj_lbs_acre_fh_wf = ((bean_yield / grams_per_lb) / (sample_area_sqft / sqft_per_acre)) * moisture_correction,
    bean_yield_adj_kg_ha_fh_wf = bean_yield_adj_lbs_acre_fh_wf / kg_to_lb
  )

# Display cleaned dataset
kable(bean_yield_clean_fh_wf)
```
# Model testing
##ECOBEAN
### Lmer

```{r}

# This is better for providing generalizations and recommendations. Location can be used as a random effect since we have 5 locations, (if need be, we can )

random_eco <- lmer(bean_yield_adj_bu_acre ~ mowing*weeds  + (1|location) + (1|location:block)+  (1|location:block:mowing), data = bean_yield_clean)


#tyler whats up with uri being random? location*year takes into accoutn if we are concerned about only these years and locations, everything is relative to the ten means from this experiment

#random_uri <- lmer(bean_yield_adj_kg_ha  ~ mowing*weeds + location*year + (1|site_year:block)+  (1|site_year:block:mowing)  , data =  bean_yield_clean)


resid_panel(random_eco)

simulateResiduals(random_eco,plot = TRUE) # Residuals and normality look good
check_model(random_eco)
```

### Joint test (anova)
```{r}
 random_eco |> 
  joint_tests() |> 
  kable()  
```
### Anova table
```{r}
options(contrasts = c("contr.sum", "contr.poly"))
Anova(random_eco, type = 3)
```
### Fisher compact letter display
#### Weed-control (No significant)

```{r}
tukey_mowing <- emmeans(random_eco, list(pairwise ~ mowing), adjust = "tukey")
tukey_mowing

cld_mowing_tukey <- cld(emmeans(random_eco, ~ mowing), adjust = "tukey", Letters = letters, sort = TRUE, reversed = TRUE)

cld_mowing_tukey
```



#### Weeds (significant)

```{r}


tukey_weeds <- emmeans(random_eco, list(pairwise ~ weeds), adjust = "tukey")
tukey_weeds

cld_weeds_tukey <- cld(emmeans(random_eco, ~ weeds), adjust = "tukey", Letters = letters, sort = TRUE, reversed = TRUE)

cld_weeds_tukey
```

##FARMHUB REPORT
### Lmer
Block is random
Tyler is under the impression that block should always be random and that post-hoc comparisons should use TUKEY rather the Fischer. Fisher is bogus apparently. 

```{r}

# This is better for providing generalizatins and reccomendations. 

random_fh <- lmer(bean_yield_adj_bu_acre_fh ~ mowing*weeds*location+ (1|location:block)+  (1|location:block:mowing), data = bean_yield_clean_fh)


#tyler whats up with uri being random? location*year takes into accoutn if we are concerned about only these years and locations, everything is relative to the ten means from this experiment

#random_uri <- lmer(bean_yield_adj_kg_ha  ~ mowing*weeds + location*year + (1|site_year:block)+  (1|site_year:block:mowing)  , data =  bean_yield_clean)


resid_panel(random_fh)

simulateResiduals(random_fh,plot = TRUE) # Residuals and normality look good
check_model(random_fh)
```

### Joint test (anova)
```{r}
 random_fh |> 
  joint_tests() |> 
  kable()  
```
### Anova table
```{r}
options(contrasts = c("contr.sum", "contr.poly"))
Anova(random_fh, type = 3)
```
### Fisher compact letter display
#### Weed-control (No significant)

```{r}
cld_mowing_fisher_fh <-cld(emmeans(random_fh, ~  mowing , type = "response"), Letters = letters, adjust = "none",sort = TRUE, reversed=TRUE)
cld_mowing_fisher_fh
```

#### Weeds (significant)

```{r}
cld_weeds_fisher_fh <-cld(emmeans(random_fh, ~  weeds , type = "response"), Letters = letters, adjust = "none",sort = TRUE, reversed=TRUE)
cld_weeds_fisher_fh
```
#### Weeds by location (significant)

```{r}
cld_location_fisher_fh <-cld(emmeans(random_fh, ~ location , type = "response"), Letters = letters, adjust = "none",sort = TRUE, reversed=TRUE)
cld_location_fisher_fh
```
#### Mowing by location (not significant)

```{r}
cld_mowing_weeds_location_fisher_fh <-cld(emmeans(random_fh, ~  mowing|weeds|location , type = "response"), Letters = letters, adjust = "none",sort = TRUE, reversed=TRUE)
cld_mowing_weeds_location_fisher_fh
```
##FARMHUB REPORT weed free
### Lmer

```{r}

# This is better for providing generalizatins and reccomendations. 

random_fh_wf <- lmer(bean_yield_adj_bu_acre_fh_wf ~ weeds*location+ (1|location:block)+  (1|location:block:mowing), data = bean_yield_clean_fh_wf)


#tyler whats up with uri being random? location*year takes into accoutn if we are concerned about only these years and locations, everything is relative to the ten means from this experiment

#random_uri <- lmer(bean_yield_adj_kg_ha  ~ mowing*weeds + location*year + (1|site_year:block)+  (1|site_year:block:mowing)  , data =  bean_yield_clean)


resid_panel(random_fh_wf)

simulateResiduals(random_fh_wf,plot = TRUE) # Residuals and normality look good
check_model(random_fh_wf)
```
### Joint test (anova)
```{r}
 random_fh_wf |> 
  joint_tests() |> 
  kable()  
```

#### Weeds (Significant)

```{r}
cld_weeds_fisher_fh_wf <-cld(emmeans(random_fh_wf, ~  weeds , type = "response"), Letters = letters, adjust = "none",sort = TRUE, reversed=TRUE)
cld_weeds_fisher_fh_wf
```
#### Weeds by location (not significant)

```{r}
cld_weeds_location_fisher_fh_wf <-cld(emmeans(random_fh_wf, ~  weeds|location , type = "response"), Letters = letters, adjust = "none",sort = TRUE, reversed=TRUE)
cld_weeds_location_fisher_fh_wf
```
#### Weeds by location (not significant)

```{r}
cld_location_weeds_fisher_fh_wf <-cld(emmeans(random_fh_wf, ~  location|weeds , type = "response"), Letters = letters, adjust = "none",sort = TRUE, reversed=TRUE)
cld_location_weeds_fisher_fh_wf
```
#Figures
##ECOBEAN

### Mowing on yield (not significant)

```{r message=FALSE}
bean_yield_clean |> 
  left_join(cld_mowing_tukey) |> 
  ggplot(aes(x = factor(mowing, levels = c("NWC", "EWC", "LWC", "AWC")), y = bean_yield_adj_bu_acre, fill = mowing)) +
  stat_summary(geom = "bar", fun = "mean", width = 0.7) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2) +
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5) +
  #geom_bar(stat="identity", position=position_dodge()) + 
  #geom_errorbar(aes(ymin=response-SE, ymax=response+SE), width=.2,
                 #position=position_dodge(.9))+
#geom_text(aes(label = trimws(.group), y = response + (SE + 30)), size = 7) +
  labs(
    x = "",
       y = expression(paste("Dry bean yield (", bu/a, " at 14% moisture)")),
    subtitle = expression(italic("Not significant"))) +
  
  scale_x_discrete(labels = c("No\nmowing", "Early\nmowing", "Late\nmowing", "As-needed\nmowing")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_WB_d(name = "BlueberriesForSal", direction = 1) +
   theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 12),
    axis.title = element_text(size = 24),  # Increase font size of axis titles
    axis.text = element_text(size = 24),   # Increase font size of axis labels
    plot.title = element_text(size = 24, face = "bold"),  # Increase font size of title
    plot.subtitle = element_text(size = 24, face = "italic")  # Increase font size of subtitle
  
  )
ggsave("bean_yield_mowing_buac_eco.png", width = 10, height = 8, dpi = 300)
```
### Weed level of yield (significant)

```{r message=FALSE}
bean_yield_clean |> 
  left_join(cld_weeds_tukey) |> 
  ggplot(aes(x = weeds, y = bean_yield_adj_bu_acre, fill = weeds)) +  # Fill added
  stat_summary(geom = "bar", fun = "mean", width = 0.6, position = position_dodge(width = 0.7)) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2, position = position_dodge(width = 0.7)) +
  stat_summary(geom = "text", fun = "MeanPlusSe", aes(label = trimws(.group)), 
               size = 6.5, vjust = -0.5, position = position_dodge(width = 0.7)) +
  labs(
    x = "",
    y = expression(paste("Dry bean yield (", bu/a, " at 14% moisture)")),
  subtitle = expression(italic("P < 0.001"))
  ) +
  scale_x_discrete(labels = c("Ambient weeds", "Surrogate + ambient weeds")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_WB_d(name = "BlueberriesForSal", direction = 1) +  # Ensure correct function use
  theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 20),
    axis.title = element_text(size = 24),
    axis.text = element_text(size = 20),
    plot.title = element_text(size = 24, face = "bold"),
    plot.subtitle = element_text(size = 24, face = "italic")
  )
ggsave("bean_yield_weeds_buac_eco.png", width = 10, height = 8, dpi = 300)
```


## FARMHUB REPORT
### Mowing on yield
```{r message=FALSE}
bean_yield_clean_fh |> 
  left_join(cld_mowing_fisher_fh) |> 
  ggplot(aes(x = factor(mowing, levels = c("NWC", "EWC", "LWC", "AWC")), 
             y = bean_yield_adj_bu_acre_fh, fill = mowing)) + 
  stat_summary(geom = "bar", fun = "mean", width = 0.6) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2) +
  labs(
    x = "",
    y = expression(paste("Dry bean yield (", "bu/a", " at 14% moisture)"))) +
  scale_x_discrete(labels = c("No\nmowing", "Early\nmowing", "Late\nmowing", "As-needed\nmowing")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_WB_d(name = "BlueberriesForSal", direction = 1) +  
  theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 12),
    axis.title = element_text(size = 24),
    axis.text = element_text(size = 24),
    plot.title = element_text(size = 24, face = "bold"),
    plot.subtitle = element_text(size = 24, face = "italic")
  )

ggsave("bean_yield_mowing_bua_fh.png", width = 10, height = 8, dpi = 300)
```
### Weed level on yield (significant)

```{r message=FALSE}
bean_yield_clean_fh_wf |> 
  left_join(cld_weeds_fisher_fh_wf) |> 
  ggplot(aes(x = factor(weeds, levels = c("WF", "M", "SW")), y = bean_yield_adj_bu_acre_fh_wf, fill = weeds)) +  # Fill added
  stat_summary(geom = "bar", fun = "mean", width = 0.6, position = position_dodge(width = 0.7)) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2, position = position_dodge(width = 0.7)) +
  stat_summary(geom = "text", fun = "MeanPlusSe", aes(label = trimws(.group)), 
               size = 6.5, vjust = -0.5, position = position_dodge(width = 0.7)) +
  labs(
    x = "",
   y = expression(paste("Dry bean yield (", "bu/a", " at 14% moisture)"))) +
  scale_x_discrete(labels = c("Weed free", "Ambient weeds", "Surrogate + ambient weeds")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_WB_d(name = "BlueberriesForSal", direction = 1) +  # Ensure correct function use
  theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 20),
    axis.title = element_text(size = 24),
    axis.text = element_text(size = 20),
    plot.title = element_text(size = 24, face = "bold"),
    plot.subtitle = element_text(size = 24, face = "italic")
  )
ggsave("bean_yield_weeds_bhac_fh.png", width = 10, height = 8, dpi = 300)
```

### Weed level and location (not significant)

```{r message=FALSE}
bean_yield_clean_fh_wf |> 
  left_join(cld_weeds_location_fisher_fh_wf) |> 
  ggplot(aes(x = factor(weeds, levels = c("WF", "M", "SW")), y = bean_yield_adj_bu_acre_fh_wf, fill = weeds)) + facet_wrap(~location, ncol= 2, labeller = labeller(location = c("CU" = "Cornell Musgrave Research Farm", "FH" = "Hudson Valley Farm Hub"))) + # Fill added
  stat_summary(geom = "bar", fun = "mean", width = 0.6, position = position_dodge(width = 0.7)) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2, position = position_dodge(width = 0.7)) +
  stat_summary(geom = "text", fun = "MeanPlusSe", aes(label = trimws(.group)), 
               size = 6.5, vjust = -0.5, position = position_dodge(width = 0.7)) +
  labs(
    x = "",
   y = expression(paste("Dry bean yield (", "bu/a", " at 14% moisture)")),
  subtitle = expression(italic("P < 0.005"))
  ) +
  scale_x_discrete(labels = c("Weed free", "Ambient \nweeds", "Surrogate + \nambient weeds")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_WB_d(name = "BlueberriesForSal", direction = 1) +  # Ensure correct function use
  theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 20),
    axis.title = element_text(size = 24),
    axis.text = element_text(size = 20),
    plot.title = element_text(size = 24, face = "bold"),
    plot.subtitle = element_text(size = 24, face = "italic")
  )
ggsave("bean_yield_weeds_location_bhac_fh.png", width = 10, height = 10, dpi = 300)
```