---
title: "IMT Weed biomass"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries

```{r message=FALSE, warning=FALSE}

#Set work directory
setwd("/Users/ey239/Github/IMT/rmarkdowns")

#Load packages 
library(tidyverse) ##install.packages("tidyverse")
library(knitr)
library(patchwork) ##install.packages("patchwork")
library(skimr)     ##install.packages("skimr")
library(readxl)
library(janitor) ##install.packages("janitor")

library(kableExtra) ##install.packages("kableExtra")
library(webshot) ##install.packages("webshot")
webshot::install_phantomjs()
library(viridis) ##install.packages("viridis")
library(lme4) ##install.packages("lme4")
library(lmerTest) ##install.packages("lmerTest")
library(emmeans) ##install.packages("emmeans")
library(rstatix) ##install.packages("rstatix")
#library(Matrix) ##install.packages("Matrix")
library(multcomp) ##install.packages("multcomp")
library(multcompView) ##install.packages("multcompView")
library(ggResidpanel) ##install.packages("ggResidpanel")
#library(car)
#library(TMB)  ##install.packages("TMB")
library(glmmTMB)  ##install.packages("glmmTMB")
library(DHARMa)  ##install.packages("DHARMa")
library(performance) ##install.packages("performance")
library(WrensBookshelf)##install.packages("WrensBookshelf")
#Load Functions
MeanPlusSe<-function(x) mean(x)+plotrix::std.error(x)

find_logw0=function(x){c=trunc(log(min(x[x>0],na.rm=T)))
d=exp(c)
return(d)}
```

<br>

# Load and clean data

## Load data

``` {r}
combined_raw <- read_excel("~/Github/IMT/raw-data/combined_raw.xlsx")
kable(head(combined_raw))

```

##Clean data
##ECOBEAN
```{r}
#Standardaze column names, convert to factors, check for outliers of variable**
clean_combined <- clean_names(combined_raw) |>  
  rename ('mowing'= treatment,'weeds'= microplot) |> 
  mutate(across(c(year, location, site_year, mowing, block, plot, weeds, ), as.factor)) 

#select and convert data for wbm analysis
weed_biomass_clean <-clean_combined |>             
  filter(weeds %in% c("SW", "M")) |>  # Keep rows where SW and M are microplots
  mutate(weed_biomass_grams_meter = (weed_biomass /0.5)) |> 
  mutate(weed_biomass_kg_ha = (weed_biomass_grams_meter *(10000))/(1000)) |>
  mutate(weed_biomass_lbs_ac = ((weed_biomass_grams_meter *(10000))/(1000))* 0.892179)
kable(head(weed_biomass_clean)) 
```
##FARMHUB REPORT
```{r}
#Standardaze column names, convert to factors, check for outliers of variable**
clean_combined <- clean_names(combined_raw) |>  
  rename ('mowing'= treatment,'weeds'= microplot) |> 
  mutate(across(c(year, location, site_year, mowing, block, plot, weeds, ), as.factor)) 

#select and convert data for wbm analysis
weed_biomass_clean_fh <-clean_combined |>             
  filter(weeds %in% c("SW", "M")) |>  # Keep rows where SW and M are microplots
   filter(location %in% c("FH", "CU")) |>
  mutate(weed_biomass_grams_meter = (weed_biomass /0.5)) |> 
  mutate(weed_biomass_kg_ha = (weed_biomass_grams_meter *(10000))/(1000)) |>
  mutate(weed_biomass_lbs_ac = ((weed_biomass_grams_meter *(10000))/(1000))* 0.892179)
kable(head(weed_biomass_clean_fh)) 
```

# Model testing
##ECOBEAN
### Glmm
```{r}

model_tweedie_log <- glmmTMB(weed_biomass_lbs_ac ~ mowing*weeds + (1|site_year) + (1|site_year:block)+ (1|site_year:block:mowing), 
  data = weed_biomass_clean, 
  family = tweedie(link = "log")

)

###It assumes that mowing effects may vary by block, in addition to site-year and block-level variation.
#This would be useful if you suspect that mowing impacts weed biomass differently in different blocks.
#The model accounts for hierarchical structure down to the mowing level within blocks.

### Two checks specifically for a generalize linear approach
simulateResiduals(model_tweedie_log,plot = TRUE) # Residuals and normality look good
check_model(model_tweedie_log) #Perfect, preditions match real data

summary(model_tweedie_log )
VarCorr(model_tweedie_log )


```

### Joint test (anova)
```{r}
model_tweedie_log |> 
  joint_tests() |> 
  kable()  
```
### Anova table
```{r}
options(contrasts = c("contr.sum", "contr.poly"))
Anova(model_tweedie_log, type = 3)
```
### Fisher compact letter display
#### Weed control (Significant)

```{r}
cld_mowing_fisher <-cld(emmeans(model_tweedie_log, ~  mowing, type = "response"), Letters = letters,adjust = "none", sort = TRUE, reversed=TRUE)
cld_mowing_fisher


```

#### Weed level (Significant)

```{r}
cld_weeds_fisher <-cld(emmeans(model_tweedie_log, ~  weeds, type = "response"), Letters = letters,adjust = "none", sort = TRUE, reversed=TRUE)
cld_weeds_fisher


```
##FARMHUB REPORT
### Glmm
```{r}

model_tweedie_log_fh <- glmmTMB(weed_biomass_lbs_ac ~ mowing*weeds + (1|site_year) + (1|site_year:block)+ (1|site_year:block:mowing), 
  data = weed_biomass_clean_fh, 
  family = tweedie(link = "log")



)
###It assumes that mowing effects may vary by block, in addition to site-year and block-level variation.
#This would be useful if you suspect that mowing impacts weed biomass differently in different blocks.
#The model accounts for hierarchical structure down to the mowing level within blocks.

### Two checks specifically for a generalize linear approach
simulateResiduals(model_tweedie_log_fh,plot = TRUE) # Residuals and normality look good
check_model(model_tweedie_log_fh) #Perfect, preditions match real data

summary(model_tweedie_log_fh )
VarCorr(model_tweedie_log_fh )


```

### Joint test (anova)
```{r}
model_tweedie_log_fh |> 
  joint_tests() |> 
  kable()  
```
### Anova table
```{r}
options(contrasts = c("contr.sum", "contr.poly"))
Anova(model_tweedie_log_fh, type = 3)
```
### Fisher compact letter display
#### Weed control (Significant)

```{r}
cld_mowing_fisher_fh <-cld(emmeans(model_tweedie_log_fh, ~  mowing, type = "response"), Letters = letters,adjust = "none", sort = TRUE, reversed=TRUE)
cld_mowing_fisher_fh


```
#### Weed level (Significant)

```{r}
cld_weeds_fisher_fh <-cld(emmeans(model_tweedie_log_fh, ~  weeds, type = "response"), Letters = letters,adjust = "none", sort = TRUE, reversed=TRUE)
cld_weeds_fisher_fh


```

#Figures
##ECOBEAN
### Mowing (Significant)


```{r message=FALSE}
weed_biomass_clean |> 
  left_join(cld_mowing_fisher) |> 
  ggplot(aes(x = factor(mowing, levels = c("NWC", "EWC", "LWC", "AWC")), y = response, fill = mowing)) +
  #stat_summary(geom = "bar", fun = "mean", width = 0.7) +
  #stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2) +
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5) +
  geom_bar(stat="identity", position=position_dodge()) + 
  geom_errorbar(aes(ymin=response-SE, ymax=response+SE), width=.2,
                 position=position_dodge(.9))+
geom_text(aes(label = trimws(.group), y = response + (SE + 35)), size = 7) +
  labs(
    x = "",
     y = expression("Weed biomass (lbs/a)"),
    #title = str_c("Influence of interrow weed control on weed biomass"),
    subtitle = expression(italic("P < 0.005"))) +
  
  scale_x_discrete(labels = c("No\nmowing", "Early\nmowing", "Late\nmowing", "As-needed\nmowing")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_WB_d(name = "BlueberriesForSal", direction = 1) +
   theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 12),
    axis.title = element_text(size = 24),  # Increase font size of axis titles
    axis.text = element_text(size = 24),   # Increase font size of axis labels
    plot.title = element_text(size = 24, face = "bold"),  # Increase font size of title
    plot.subtitle = element_text(size = 24, face = "italic")  # Increase font size of subtitle
  )
ggsave("weed_biomass_mowing_lbac_eco.png", width = 10, height = 8, dpi = 300)
```

### Weed level of weed biomass (significant)

```{r message=FALSE}
weed_biomass_clean |> 
  left_join(cld_weeds_fisher) |> 
  ggplot(aes(x = weeds, y = response, fill = weeds)) +  # Fill added
  #stat_summary(geom = "bar", fun = "mean", width = 0.6, position = position_dodge(width = 0.7)) +
  #stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2, position = position_dodge(width = 0.7)) +
  #stat_summary(geom = "text", fun = "MeanPlusSe", aes(label = trimws(.group)), 
               #size = 6.5, vjust = -0.5, position = position_dodge(width = 0.7)) +
  geom_bar(stat="identity", position=position_dodge()) + 
  geom_errorbar(aes(ymin=response-SE, ymax=response+SE), width=.2,
                 position=position_dodge(.9))+
geom_text(aes(label = trimws(.group), y = response + (SE + 40)), size = 7) +
  labs(
    x = "",
    y = expression("Weed biomass" ~ (kg~ha^{-1})),
  subtitle = expression(italic("P < 0.005"))
  ) +
  scale_x_discrete(labels = c("Ambient weeds", "Surrogate + ambient weeds")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_WB_d(name = "BlueberriesForSal", direction = 1) +  # Ensure correct function use
  theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 20),
    axis.title = element_text(size = 24),
    axis.text = element_text(size = 20),
    plot.title = element_text(size = 24, face = "bold"),
    plot.subtitle = element_text(size = 24, face = "italic")
  )
ggsave("weed_biomass_weeds_kgha_eco.png", width = 10, height = 8, dpi = 300)
```

#Figures
##FARMHUB REPORT
### Mowing (Significant)


```{r message=FALSE}
weed_biomass_clean_fh |> 
  left_join(cld_mowing_fisher_fh) |> 
  ggplot(aes(x = factor(mowing, levels = c("NWC", "EWC", "LWC", "AWC")), y = response, fill = mowing)) +
  #stat_summary(geom = "bar", fun = "mean", width = 0.7) +
  #stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2) +
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5) +
  geom_bar(stat="identity", position=position_dodge()) + 
  geom_errorbar(aes(ymin=response-SE, ymax=response+SE), width=.2,
                 position=position_dodge(.9))+
geom_text(aes(label = trimws(.group), y = response + (SE + 35)), size = 7) +
  labs(
    x = "",
     y = expression("Weed biomass (lbs/a)"),
    #title = str_c("Influence of interrow weed control on weed biomass"),
    subtitle = expression(italic("P < 0.005"))) +
  
  scale_x_discrete(labels = c("No\nmowing", "Early\nmowing", "Late\nmowing", "As-needed\nmowing")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_WB_d(name = "BlueberriesForSal", direction = 1) +
   theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 12),
    axis.title = element_text(size = 24),  # Increase font size of axis titles
    axis.text = element_text(size = 24),   # Increase font size of axis labels
    plot.title = element_text(size = 24, face = "bold"),  # Increase font size of title
    plot.subtitle = element_text(size = 24, face = "italic")  # Increase font size of subtitle
  )
ggsave("weed_biomass_mowing_lbac_fh.png", width = 10, height = 8, dpi = 300)
```

## Weed level on weed biomass (significant)

```{r message=FALSE}
weed_biomass_clean_fh |> 
  left_join(cld_weeds_fisher_fh) |> 
  ggplot(aes(x = weeds, y = response, fill = weeds)) +  # Fill added
  #stat_summary(geom = "bar", fun = "mean", width = 0.6, position = position_dodge(width = 0.7)) +
  #stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2, position = position_dodge(width = 0.7)) +
  #stat_summary(geom = "text", fun = "MeanPlusSe", aes(label = trimws(.group)), 
               #size = 6.5, vjust = -0.5, position = position_dodge(width = 0.7)) +
  geom_bar(stat="identity", position=position_dodge()) + 
  geom_errorbar(aes(ymin=response-SE, ymax=response+SE), width=.2,
                 position=position_dodge(.9))+
geom_text(aes(label = trimws(.group), y = response + (SE + 40)), size = 7) +
  labs(
    x = "",
    y = expression("Weed biomass" ~ (kg~ha^{-1})),
  subtitle = expression(italic("P < 0.005"))
  ) +
  scale_x_discrete(labels = c("Ambient weeds", "Surrogate + ambient weeds")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_WB_d(name = "BlueberriesForSal", direction = 1) +  # Ensure correct function use
  theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 20),
    axis.title = element_text(size = 24),
    axis.text = element_text(size = 20),
    plot.title = element_text(size = 24, face = "bold"),
    plot.subtitle = element_text(size = 24, face = "italic")
  )
ggsave("weed_biomass_weeds_kgha_fh.png", width = 10, height = 8, dpi = 300)
```
