---
title: "Weed biomass"

output:
  github_document:
    toc: true
always_allow_html: true


---
#Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = TRUE,
  message = FALSE,
  warning = FALSE

)
```
#Packages
```{r}
# Packages ------------------------------------------------------------
library(tidyverse)    # includes dplyr, ggplot2, readr, tibble, etc.
library(janitor)
library(readxl)
library(glmmTMB)
library(DHARMa)
library(emmeans)
library(multcomp)
library(car)
library(kableExtra)
library(here)
library(conflicted)
library(lme4)
library(purrr)
library(tibble)
library(stringr)
library(WrensBookshelf)

# Handle conflicts ----------------------------------------------------
conflicts_prefer(dplyr::select)
conflicts_prefer(dplyr::filter)
conflicts_prefer(dplyr::recode)

# Global theme --------------------------------------------------------
theme_set(theme_bw(base_size = 12))

# Treatment level order (use everywhere) ------------------------------
mow_levels <- c(
  "No mowing",
  "Early mowing",
  "Late mowing",
  "As-needed mowing"
)

# One consistent CVD-safe color palette for all figures ---------------
fill_cols <- WB_brewer(
  name = "LittleBlueHouseBesideTheSea1",
  n    = length(mow_levels),
  type = "discrete"
) |>
  setNames(mow_levels)

# x-axis label helpers ------------------------------------------------

# Break on spaces (if you ever want every word on its own line)
label_break_spaces <- function(x) {
  stringr::str_replace_all(x, " ", "\n")
}

# Break after the comma: "Rolled,\nno control", etc.
label_break_comma <- function(x) {
  stringr::str_replace_all(x, ", ", ",\n")
}

# Break after comma AND split "high-residue cultivation"
# -> "Rolled,\nhigh-residue\ncultivation"
label_break_comma_cult <- function(x) {
  x |>
    stringr::str_replace("high-residue cultivation",
                         "high-residue\ncultivation") |>
    stringr::str_replace_all(", ", ",\n")
}

# Helper: tidy emmeans output regardless of CI column names -----------
# (works directly on an emmeans object)
# trt_var = name of treatment column to relevel (e.g., "weed_trt", "treatment")

tidy_emm <- function(emm, trt_var = NULL, ref_levels = NULL) {
  emm_df <- as.data.frame(emm)

  lcl_col <- intersect(c("lower.CL", "asymp.LCL"), names(emm_df))[1]
  ucl_col <- intersect(c("upper.CL", "asymp.UCL"), names(emm_df))[1]

  if (is.na(lcl_col) || is.na(ucl_col)) {
    stop("Could not find CI columns in emmeans output.")
  }

  out <- emm_df |>
    dplyr::mutate(
      ci_low  = .data[[lcl_col]],
      ci_high = .data[[ucl_col]]
    )

  if (!is.null(trt_var) && !is.null(ref_levels) && trt_var %in% names(out)) {
    out <- out |>
      dplyr::mutate(
        !!trt_var := factor(.data[[trt_var]], levels = ref_levels)
      )
  }

  out
}


```



# Data import & prep

```{r}
# IMT weed biomass data import & cleaning (2023–2025) ------------------

# 1) List of raw files (comment out any you don't have yet) -------------
weed_files <- c(
  here("..", "data", "raw", "cornell_raw_2023.xlsx"),
  here("..", "data", "raw", "cornell_raw_2024.xlsx"),
  here("..", "data", "raw", "cornell_raw_2025.xlsx"),
  
  here("..", "data", "raw", "farmhub_raw_2023.xlsx"),
  here("..", "data", "raw", "farmhub_raw_2024.xlsx"),
  here("..", "data", "raw", "farmhub_raw_2025.xlsx"),
  
  here("..", "data", "raw", "maine_raw_2023.xlsx"),
  here("..", "data", "raw", "maine_raw_2024.xlsx"),
  here("..", "data", "raw", "maine_raw_2025.xlsx"),
  
  here("..", "data", "raw", "vermont_raw_2023.xlsx"),
  here("..", "data", "raw", "vermont_raw_2024.xlsx"),
  here("..", "data", "raw", "vermont_raw_2025.xlsx"),
  
  here("..", "data", "raw", "wisconsin_raw_2023.xlsx"),
  here("..", "data", "raw", "wisconsin_raw_2024.xlsx"),
  here("..", "data", "raw", "wisconsin_raw_2025.xlsx")
)

# Quick sanity check
weed_files
file.exists(weed_files)

# 2) Robust helper to read + standardize a single file ------------------
read_weed_file <- function(path) {
  dat <- read_excel(path, na = c("na", "Na", "NA")) |>
    clean_names()
  
  fname <- basename(path)
  
  # Derive location label from filename (used if column is missing)
  loc_label <- dplyr::case_when(
    stringr::str_detect(fname, "cornell")   ~ "Cornell",
    stringr::str_detect(fname, "farmhub")   ~ "FarmHub",
    stringr::str_detect(fname, "maine")     ~ "Maine",
    stringr::str_detect(fname, "vermont")   ~ "Vermont",
    stringr::str_detect(fname, "wisconsin") ~ "Wisconsin",
    TRUE                                    ~ "Unknown"
  )
  
  # Derive year from filename (used if column is missing)
  year_val <- stringr::str_extract(fname, "20[0-9]{2}")
  
  # If location / year columns are missing, create them -----------------
  if (!"location" %in% names(dat)) {
    dat$location <- loc_label
  }
  if (!"year" %in% names(dat)) {
    dat$year <- year_val
  }
  # If site_year is missing, create it from location + year -------------
  if (!"site_year" %in% names(dat)) {
    dat$site_year <- paste(dat$location, dat$year, sep = "_")
  }
  
  dat |>
    mutate(
      location  = factor(location),
      year      = factor(year),
      site_year = factor(site_year),
      block     = factor(block),
      microplot = stringr::str_trim(microplot),
      # match your old rename(weed_trt = treatment) + recode
      weed_trt  = dplyr::recode(
        treatment,
        "NWC" = "No mowing",
        "EWC" = "Early mowing",
        "LWC" = "Late mowing",
        "AWC" = "As-needed mowing"
      ),
      weed_trt  = factor(weed_trt, levels = mow_levels)
    )
}

# 3) Read all files, stack, and compute per-area biomass ----------------
weed_biomass_clean <- purrr::map_df(weed_files, read_weed_file) |>
  filter(!is.na(weed_biomass)) |>
  mutate(
    # all biomass originally in g per 0.5 m^2 quadrat
    weed_biomass_g_m2           = weed_biomass          * 2,
    weed_biomass_kg_ha          = weed_biomass          * 20,
    inrow_weed_biomass_g_m2     = intrarow_weed_biomass * 2,
    inrow_weed_biomass_kg_ha    = intrarow_weed_biomass * 20,
    interrow_weed_biomass_g_m2  = interrow_weed_biomass * 2,
    interrow_weed_biomass_kg_ha = interrow_weed_biomass * 20
  )

# 4) Quick checks -------------------------------------------------------
kable(
  head(weed_biomass_clean),
  caption = "All IMT site-years (2023–2025), cleaned weed biomass"
)

weed_biomass_clean |>
  count(site_year, weed_trt) |>
  arrange(site_year, weed_trt)



```


## Subsets
```{r}

# Subset for weed biomass models: ambient vs surrogate only ---------

weed_biomass_bi <- weed_biomass_clean |>
  mutate(
    weeds = dplyr::recode(
      microplot,
      "M"  = "Ambient weeds",
      "SW" = "Surrogate weeds",
      .default = NA_character_
    ),
    weeds = factor(weeds, levels = c("Ambient weeds", "Surrogate weeds"))
  ) |>
  filter(!is.na(weeds))    # drop WF for biomass analysis only

# Quick check: which locations are present? -----------------------------

weed_biomass_bi |>
  count(location) |>
  kable(
    caption = "Number of ambient/surrogate weed microplots by location"
  ) |>
  kable_styling(full_width = FALSE)

# 3) Define Ecobean (all sites) and NY-only subsets --------------------

# Ecobean = all five locations in the IMT network
weed_biomass_eco <- weed_biomass_bi |>
  filter(location %in% c("CU", "FH", "ME", "VT", "WI")) |>
  droplevels()

# New York only = Cornell + Farm Hub
weed_biomass_ny <- weed_biomass_bi |>
  filter(location %in% c("CU", "FH")) |>
  droplevels()

# Optional: quick sanity check of site-years in each subset ------------

weed_biomass_eco |>
  count(site_year) |>
  kable(
    caption = "Ecobean subset: ambient/surrogate weed microplots by site-year"
  ) |>
  kable_styling(full_width = FALSE)

weed_biomass_ny |>
  count(site_year) |>
  kable(
    caption = "NY-only subset: ambient/surrogate weed microplots by site-year"
  ) |>
  kable_styling(full_width = FALSE)

```

# Model testing
## Exploratory 
###Total weed biomass (kg ha⁻¹)
```{r}
## 1a) Ecobean (all five locations, 2023–2025) -------------------------

# Summary table by site-year × mowing
weed_biomass_eco |>
  group_by(site_year, weed_trt) |>
  summarise(
    n       = n(),
    mean    = mean(weed_biomass_kg_ha, na.rm = TRUE),
    median  = median(weed_biomass_kg_ha, na.rm = TRUE),
    sd      = sd(weed_biomass_kg_ha, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(site_year, weed_trt) |>
  kable(
    digits  = 1,
    caption = "Ecobean (all locations): weed biomass (kg ha⁻¹) by site-year × mowing treatment"
  ) |>
  kable_styling(
    full_width        = FALSE,
    bootstrap_options = c("striped", "hover")
  )

# Boxplot: rows = year (2023–2025), columns = location ------------------
wbm_box_eco <- weed_biomass_eco |>
  mutate(
    year     = factor(year, levels = c(2023, 2024, 2025)),          # 2023 on top
    location = factor(location, levels = c("CU", "FH", "ME", "VT", "WI"))
  ) |>
  ggplot(aes(x = weed_trt, y = weed_biomass_kg_ha, fill = weed_trt)) +
  geom_boxplot(
    outlier.shape = NA,
    width         = 0.55,
    color         = "black"
  ) +
  geom_jitter(
    width  = 0.12,
    height = 0,
    alpha  = 0.4,
    size   = 1.8,
    color  = "grey30"
  ) +
  facet_grid(year ~ location) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_spaces) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x     = NULL,
    y     = expression(Weed~biomass~"(kg"~ha^{-1}*")"),
    title = "Ecobean: weed biomass by mowing treatment"
  ) +
  theme(
    axis.text.x = element_text(size = 9),
    strip.text  = element_text(face = "bold")
  )

wbm_box_eco  # print in the Rmd


## 1b) New York only (Cornell + Farm Hub) ------------------------------

# Summary table by site-year × mowing
weed_biomass_ny |>
  group_by(site_year, weed_trt) |>
  summarise(
    n       = n(),
    mean    = mean(weed_biomass_kg_ha, na.rm = TRUE),
    median  = median(weed_biomass_kg_ha, na.rm = TRUE),
    sd      = sd(weed_biomass_kg_ha, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(site_year, weed_trt) |>
  kable(
    digits  = 1,
    caption = "New York only (Cornell + Farm Hub): weed biomass (kg ha⁻¹) by site-year × mowing treatment"
  ) |>
  kable_styling(
    full_width        = FALSE,
    bootstrap_options = c("striped", "hover")
  )

# Boxplot for NY only, same layout: rows = year, columns = location ----
wbm_box_ny <- weed_biomass_ny |>
  mutate(
    year     = factor(year, levels = c(2023, 2024, 2025)),
    location = factor(location, levels = c("CU", "FH"))
  ) |>
  ggplot(aes(x = weed_trt, y = weed_biomass_kg_ha, fill = weed_trt)) +
  geom_boxplot(
    outlier.shape = NA,
    width         = 0.55,
    color         = "black"
  ) +
  geom_jitter(
    width  = 0.12,
    height = 0,
    alpha  = 0.4,
    size   = 1.8,
    color  = "grey30"
  ) +
  facet_grid(year ~ location) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_spaces) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x     = NULL,
    y     = expression(Weed~biomass~"(kg"~ha^{-1}*")"),
    title = "New York (Cornell + Farm Hub): weed biomass by mowing treatment"
  ) +
  theme(
    axis.text.x = element_text(size = 9),
    strip.text  = element_text(face = "bold")
  )

wbm_box_ny  # print in the Rmd

# Figure directories ---------------------------------------------------
fig_dir_eco <- here("analysis", "figs", "weed-biomass", "ecobean")
fig_dir_ny  <- here("analysis", "figs", "weed-biomass", "ny-only")

dir.create(fig_dir_eco, showWarnings = FALSE, recursive = TRUE)
dir.create(fig_dir_ny,  showWarnings = FALSE, recursive = TRUE)

# Save Ecobean figure --------------------------------------------------
ggsave(
  filename = file.path(
    fig_dir_eco,
    "fig_weed_biomass_box_ecobean_kg_ha.png"
  ),
  plot   = wbm_box_eco,
  width  = 12,
  height = 6,
  dpi    = 300
)

# Save NY-only figure --------------------------------------------------
ggsave(
  filename = file.path(
    fig_dir_ny,
    "fig_weed_biomass_box_ny_kg_ha.png"
  ),
  plot   = wbm_box_ny,
  width  = 12,
  height = 6,
  dpi    = 300
)


```
### In-row weed biomass (kg ha⁻¹) 
```{r}
## 1a) Ecobean (all five locations, 2023–2025) -------------------------

# Summary table by site-year × mowing (in-row only)
weed_biomass_eco |>
  filter(!is.na(inrow_weed_biomass_kg_ha)) |>
  group_by(site_year, weed_trt) |>
  summarise(
    n       = n(),
    mean    = mean(inrow_weed_biomass_kg_ha, na.rm = TRUE),
    median  = median(inrow_weed_biomass_kg_ha, na.rm = TRUE),
    sd      = sd(inrow_weed_biomass_kg_ha, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(site_year, weed_trt) |>
  kable(
    digits  = 1,
    caption = "Ecobean (all locations): in-row weed biomass (kg ha⁻¹) by site-year × mowing treatment"
  ) |>
  kable_styling(
    full_width        = FALSE,
    bootstrap_options = c("striped", "hover")
  )

# Boxplot: in-row biomass, rows = year, columns = location -------------
wbm_inrow_eco <- weed_biomass_eco |>
  filter(!is.na(inrow_weed_biomass_kg_ha)) |>
  mutate(
    year     = factor(year, levels = c(2023, 2024, 2025)),
    location = factor(location, levels = c("CU", "FH", "ME", "VT", "WI"))
  ) |>
  ggplot(aes(x = weed_trt, y = inrow_weed_biomass_kg_ha, fill = weed_trt)) +
  geom_boxplot(
    outlier.shape = NA,
    width         = 0.55,
    color         = "black"
  ) +
  geom_jitter(
    width  = 0.12,
    height = 0,
    alpha  = 0.4,
    size   = 1.8,
    color  = "grey30"
  ) +
  facet_grid(year ~ location) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_spaces) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x     = NULL,
    y     = expression(Inrow~weed~biomass~"(kg"~ha^{-1}*")"),
    title = "Ecobean: in-row weed biomass by mowing treatment"
  ) +
  theme(
    axis.text.x = element_text(size = 9),
    strip.text  = element_text(face = "bold")
  )

wbm_inrow_eco  # print in the Rmd


## 1b) New York only (Cornell + Farm Hub) ------------------------------

# Summary table by site-year × mowing (in-row only)
weed_biomass_ny |>
  filter(!is.na(inrow_weed_biomass_kg_ha)) |>
  group_by(site_year, weed_trt) |>
  summarise(
    n       = n(),
    mean    = mean(inrow_weed_biomass_kg_ha, na.rm = TRUE),
    median  = median(inrow_weed_biomass_kg_ha, na.rm = TRUE),
    sd      = sd(inrow_weed_biomass_kg_ha, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(site_year, weed_trt) |>
  kable(
    digits  = 1,
    caption = "New York only (Cornell + Farm Hub): in-row weed biomass (kg ha⁻¹) by site-year × mowing treatment"
  ) |>
  kable_styling(
    full_width        = FALSE,
    bootstrap_options = c("striped", "hover")
  )

# Boxplot: in-row biomass, rows = year, columns = location -------------
wbm_inrow_ny <- weed_biomass_ny |>
  filter(!is.na(inrow_weed_biomass_kg_ha)) |>
  mutate(
    year     = factor(year, levels = c(2023, 2024, 2025)),
    location = factor(location, levels = c("CU", "FH"))
  ) |>
  ggplot(aes(x = weed_trt, y = inrow_weed_biomass_kg_ha, fill = weed_trt)) +
  geom_boxplot(
    outlier.shape = NA,
    width         = 0.55,
    color         = "black"
  ) +
  geom_jitter(
    width  = 0.12,
    height = 0,
    alpha  = 0.4,
    size   = 1.8,
    color  = "grey30"
  ) +
  facet_grid(year ~ location) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_spaces) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x     = NULL,
    y     = expression(Inrow~weed~biomass~"(kg"~ha^{-1}*")"),
    title = "New York (Cornell + Farm Hub): in-row weed biomass by mowing treatment"
  ) +
  theme(
    axis.text.x = element_text(size = 9),
    strip.text  = element_text(face = "bold")
  )

wbm_inrow_ny  # print in the Rmd

# Directories for in-row weed biomass figs -----------------------------
fig_dir_eco_inrow <- here("analysis", "figs", "weed-biomass", "inrow", "ecobean")
fig_dir_ny_inrow  <- here("analysis", "figs", "weed-biomass", "inrow", "ny-only")

dir.create(fig_dir_eco_inrow, showWarnings = FALSE, recursive = TRUE)
dir.create(fig_dir_ny_inrow,  showWarnings = FALSE, recursive = TRUE)

# Save Ecobean in-row figure -------------------------------------------
ggsave(
  filename = file.path(
    fig_dir_eco_inrow,
    "fig_inrow_weed_biomass_box_ecobean_kg_ha.png"
  ),
  plot   = wbm_inrow_eco,
  width  = 12,
  height = 6,
  dpi    = 300
)

# Save NY-only in-row figure -------------------------------------------
ggsave(
  filename = file.path(
    fig_dir_ny_inrow,
    "fig_inrow_weed_biomass_box_ny_kg_ha.png"
  ),
  plot   = wbm_inrow_ny,
  width  = 12,
  height = 6,
  dpi    = 300
)



```

### Inter-row weed biomass (kg ha⁻¹) 
```{r}
### Inter-row weed biomass (kg ha⁻¹) by site-year × mowing ---------------
## Ecobean (all sites) + NY-only, with tables, plots, and saving

# 1) Ecobean summary table: inter-row biomass ---------------------------
inter_summary_eco <- weed_biomass_eco |>
  filter(!is.na(interrow_weed_biomass_kg_ha)) |>
  group_by(site_year, weed_trt) |>
  summarise(
    n       = n(),
    mean    = mean(interrow_weed_biomass_kg_ha, na.rm = TRUE),
    median  = median(interrow_weed_biomass_kg_ha, na.rm = TRUE),
    sd      = sd(interrow_weed_biomass_kg_ha, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(site_year, weed_trt)

inter_summary_eco |>
  kable(
    digits  = 1,
    caption = "Ecobean (all sites): inter-row weed biomass (kg ha⁻¹) by site-year × mowing treatment"
  ) |>
  kable_styling(
    full_width        = FALSE,
    bootstrap_options = c("striped", "hover")
  )

# 2) NY-only summary table: inter-row biomass ---------------------------
inter_summary_ny <- weed_biomass_ny |>
  filter(!is.na(interrow_weed_biomass_kg_ha)) |>
  group_by(site_year, weed_trt) |>
  summarise(
    n       = n(),
    mean    = mean(interrow_weed_biomass_kg_ha, na.rm = TRUE),
    median  = median(interrow_weed_biomass_kg_ha, na.rm = TRUE),
    sd      = sd(interrow_weed_biomass_kg_ha, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(site_year, weed_trt)

inter_summary_ny |>
  kable(
    digits  = 1,
    caption = "New York only (Cornell + Farm Hub): inter-row weed biomass (kg ha⁻¹) by site-year × mowing treatment"
  ) |>
  kable_styling(
    full_width        = FALSE,
    bootstrap_options = c("striped", "hover")
  )

# 3) Ecobean plot: inter-row biomass -----------------------------------
wbm_inter_eco <- weed_biomass_eco |>
  filter(!is.na(interrow_weed_biomass_kg_ha)) |>
  mutate(
    year_f     = factor(year,     levels = c(2023, 2024, 2025)),
    location_f = factor(location, levels = c("CU", "FH", "ME", "VT", "WI"))
  ) |>
  ggplot(aes(x = weed_trt,
             y = interrow_weed_biomass_kg_ha,
             fill = weed_trt)) +
  geom_boxplot(
    outlier.shape = NA,
    width         = 0.55,
    color         = "black"
  ) +
  geom_jitter(
    width  = 0.12,
    height = 0,
    alpha  = 0.4,
    size   = 1.8,
    color  = "grey30"
  ) +
  facet_grid(year_f ~ location_f) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_spaces) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x     = NULL,
    y     = expression(Interrow~weed~biomass~"(kg"~ha^{-1}*")"),
    title = "Ecobean: inter-row weed biomass by mowing treatment"
  ) +
  theme(
    axis.text.x = element_text(size = 9),
    strip.text  = element_text(face = "bold")
  )

# 4) NY-only plot: inter-row biomass -----------------------------------
wbm_inter_ny <- weed_biomass_ny |>
  filter(!is.na(interrow_weed_biomass_kg_ha)) |>
  ggplot(aes(x = weed_trt,
             y = interrow_weed_biomass_kg_ha,
             fill = weed_trt)) +
  geom_boxplot(
    outlier.shape = NA,
    width         = 0.55,
    color         = "black"
  ) +
  geom_jitter(
    width  = 0.12,
    height = 0,
    alpha  = 0.4,
    size   = 1.8,
    color  = "grey30"
  ) +
  facet_wrap(~ site_year, nrow = 2) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_spaces) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x     = NULL,
    y     = expression(Interrow~weed~biomass~"(kg"~ha^{-1}*")"),
    title = "New York only (Cornell + Farm Hub): inter-row weed biomass"
  ) +
  theme(
    axis.text.x = element_text(size = 10),
    strip.text  = element_text(face = "bold")
  )

# 5) Print plots in the Rmd --------------------------------------------
wbm_inter_eco
wbm_inter_ny

# 6) Directories for saving --------------------------------------------
fig_dir_eco_inter <- here("analysis", "figs", "weed-biomass", "interrow", "ecobean")
fig_dir_ny_inter  <- here("analysis", "figs", "weed-biomass", "interrow", "ny-only")

dir.create(fig_dir_eco_inter, showWarnings = FALSE, recursive = TRUE)
dir.create(fig_dir_ny_inter,  showWarnings = FALSE, recursive = TRUE)

# 7) Save figures -------------------------------------------------------
ggsave(
  filename = file.path(
    fig_dir_eco_inter,
    "fig_interrow_weed_biomass_box_ecobean_kg_ha.png"
  ),
  plot   = wbm_inter_eco,
  width  = 12,
  height = 6,
  dpi    = 300
)

ggsave(
  filename = file.path(
    fig_dir_ny_inter,
    "fig_interrow_weed_biomass_box_ny_kg_ha.png"
  ),
  plot   = wbm_inter_ny,
  width  = 12,
  height = 6,
  dpi    = 300
)


```


## Selection
### Total weed biomass
#### Ecobean 
```{r}
## Model testing / selection for Ecobean weed biomass (kg ha^-1) --------
## Goal:
##   1) Keep interactive mean structure: weed_trt * weeds
##   2) Drop site_year as fixed effect
##   3) Use simpler split-plot random structure:
##        (1 | site_year) + (1 | site_year:block)
##   4) Use Tweedie family, then optimize dispersion structure
##      and select best *valid* model by AIC (finite logLik + pdHess)
##   5) Inference via car::Anova(type = 3)

options(contrasts = c("contr.sum", "contr.poly"))

# 0) Helpers ------------------------------------------------------------

safe_aic <- function(mod) {
  out <- try(AIC(mod), silent = TRUE)
  if (inherits(out, "try-error")) return(NA_real_)
  out
}

is_valid_glmmTMB <- function(mod) {
  ll <- try(as.numeric(logLik(mod)), silent = TRUE)
  if (inherits(ll, "try-error")) return(FALSE)
  isTRUE(mod$sdr$pdHess) && is.finite(ll) && is.finite(safe_aic(mod))
}

aic_tbl <- function(mod_list) {
  tibble::tibble(
    model  = names(mod_list),
    df     = purrr::map_dbl(mod_list, ~ tryCatch(attr(logLik(.x), "df"), error = function(e) NA_real_)),
    AIC    = purrr::map_dbl(mod_list, safe_aic),
    pdHess = purrr::map_lgl(mod_list, ~ isTRUE(.x$sdr$pdHess)),
    valid  = purrr::map_lgl(mod_list, is_valid_glmmTMB)
  ) |>
    dplyr::mutate(
      deltaAIC = AIC - min(AIC[is.finite(AIC)], na.rm = TRUE)
    ) |>
    dplyr::arrange(dplyr::desc(valid), AIC)
}

# 1) Mean + random structure (SIMPLER RE) -------------------------------

form_eco_full <- weed_biomass_kg_ha ~ weed_trt * weeds +
  (1 | site_year) +
  (1 | site_year:block)

# 2) Fit Tweedie baseline (optionally with ZI for comparison) -----------

wbm_eco_tw <- glmmTMB(
  formula = form_eco_full,
  family  = tweedie(link = "log"),
  data    = weed_biomass_eco
)

# Optional: compare ZI as a starting point only
wbm_eco_tw_zi <- glmmTMB(
  formula   = form_eco_full,
  family    = tweedie(link = "log"),
  ziformula = ~ 1,
  data      = weed_biomass_eco
)

tweedie_cands <- list(
  "Tweedie: base"      = wbm_eco_tw,
  "Tweedie: + ZI(~1)"  = wbm_eco_tw_zi
)

aic_tw <- aic_tbl(tweedie_cands)

kable(
  aic_tw,
  digits  = 2,
  caption = "Ecobean weed biomass (kg ha⁻¹): Tweedie candidates (mean model fixed as weed_trt * weeds; simpler RE)"
) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

best_tw_row <- aic_tw |>
  dplyr::filter(valid) |>
  dplyr::slice_min(AIC, n = 1)

if (nrow(best_tw_row) == 0) {
  stop("No valid Tweedie models (finite logLik + pdHess) for Ecobean biomass.")
}

best_tw_name <- best_tw_row$model
best_tw_mod  <- tweedie_cands[[best_tw_name]]

cat("Selected Tweedie starting point:", best_tw_name, "\n")

# 3) Dispersion structure search (no ZI) --------------------------------
# IMPORTANT: force ziformula = ~0 for dispersion models

base_nozi <- update(best_tw_mod, ziformula = ~ 0)

m0 <- base_nozi

m_disp_sy_nozi <- update(
  base_nozi,
  dispformula = ~ site_year
)

m_disp_sy_weeds_nozi <- update(
  base_nozi,
  dispformula = ~ site_year + weeds
)

m_disp_sy_weeds_int_nozi <- update(
  base_nozi,
  dispformula = ~ site_year * weeds
)

disp_cands <- list(
  "m0 (no disp)"            = m0,
  "disp: site_year"         = m_disp_sy_nozi,
  "disp: site_year + weeds" = m_disp_sy_weeds_nozi,
  "disp: site_year * weeds" = m_disp_sy_weeds_int_nozi
)

aic_disp <- aic_tbl(disp_cands)

kable(
  aic_disp,
  digits  = 2,
  caption = "Ecobean weed biomass (kg ha⁻¹): dispersion-structure candidates (Tweedie; simpler RE; no ZI)"
) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

best_disp_row <- aic_disp |>
  dplyr::filter(valid) |>
  dplyr::slice_min(AIC, n = 1)

if (nrow(best_disp_row) == 0) {
  stop("No valid dispersion models (finite logLik + pdHess).")
}

best_disp_name <- best_disp_row$model
weed_glmm_eco  <- disp_cands[[best_disp_name]]

cat("Selected primary Ecobean model: Tweedie (log) +", best_disp_name, "\n")

# 4) Diagnostics + Type-III tests for chosen Ecobean model --------------

set.seed(123)
res_eco <- DHARMa::simulateResiduals(weed_glmm_eco)
plot(res_eco)

DHARMa::testDispersion(res_eco)
DHARMa::testZeroInflation(res_eco)

car::Anova(weed_glmm_eco, type = 3)


```

```{r}
## Model testing / selection for Ecobean weed biomass (kg ha^-1) --------
## (Simpler random-effects structure)
## Goal:
##   1) Keep interactive mean structure: weed_trt * weeds
##   2) Drop site_year as fixed effect
##   3) Use *simpler* split-plot random structure:
##        (1 | site_year) + (1 | site_year:block)
##      (drop (1 | site_year:block:weed_trt))
##   4) Use Tweedie(log), no ZI, and select best *valid* dispersion model by AIC
##      among: none, site_year, site_year + weeds, site_year * weeds

options(contrasts = c("contr.sum", "contr.poly"))

# 0) Helpers ------------------------------------------------------------

safe_aic <- function(mod) {
  out <- try(AIC(mod), silent = TRUE)
  if (inherits(out, "try-error")) return(NA_real_)
  out
}

is_valid_glmmTMB <- function(mod) {
  ll <- try(as.numeric(logLik(mod)), silent = TRUE)
  if (inherits(ll, "try-error")) return(FALSE)
  isTRUE(mod$sdr$pdHess) && is.finite(ll) && is.finite(safe_aic(mod))
}

aic_tbl <- function(mod_list) {
  tibble::tibble(
    model  = names(mod_list),
    df     = purrr::map_dbl(mod_list, ~ tryCatch(attr(logLik(.x), "df"), error = function(e) NA_real_)),
    AIC    = purrr::map_dbl(mod_list, safe_aic),
    pdHess = purrr::map_lgl(mod_list, ~ isTRUE(.x$sdr$pdHess)),
    valid  = purrr::map_lgl(mod_list, is_valid_glmmTMB)
  ) |>
    dplyr::mutate(
      deltaAIC = AIC - min(AIC[is.finite(AIC)], na.rm = TRUE)
    ) |>
    dplyr::arrange(dplyr::desc(valid), AIC)
}

# 1) Mean + (simplified) random structure ------------------------------

form_eco_full_simpleRE <- weed_biomass_kg_ha ~ weed_trt * weeds +
  (1 | site_year) +
  (1 | site_year:block)

# 2) Fit Tweedie baseline (no ZI) --------------------------------------

m0 <- glmmTMB(
  formula   = form_eco_full_simpleRE,
  family    = tweedie(link = "log"),
  ziformula = ~ 0,
  data      = weed_biomass_eco
)

# 3) Dispersion structure search (no ZI) --------------------------------
#   ladder: none -> site_year -> site_year + weeds -> site_year * weeds

m_disp_sy_nozi <- update(
  m0,
  dispformula = ~ site_year
)

m_disp_sy_weeds_nozi <- update(
  m0,
  dispformula = ~ site_year + weeds
)

m_disp_sy_weeds_int_nozi <- update(
  m0,
  dispformula = ~ site_year * weeds
)

disp_cands <- list(
  "m0 (no disp)"            = m0,
  "disp: site_year"         = m_disp_sy_nozi,
  "disp: site_year + weeds" = m_disp_sy_weeds_nozi,
  "disp: site_year * weeds" = m_disp_sy_weeds_int_nozi
)

aic_disp <- aic_tbl(disp_cands)

kable(
  aic_disp,
  digits  = 2,
  caption = "Ecobean weed biomass (kg ha⁻¹): dispersion-structure candidates (Tweedie; simpler RE; no ZI)"
) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

best_disp_row <- aic_disp |>
  dplyr::filter(valid) |>
  dplyr::slice_min(AIC, n = 1)

if (nrow(best_disp_row) == 0) {
  stop("No valid dispersion models (finite logLik + pdHess).")
}

best_disp_name <- best_disp_row$model
weed_glmm_eco  <- disp_cands[[best_disp_name]]

cat("Selected primary Ecobean model: Tweedie (log), simpler RE +", best_disp_name, "\n")

# 4) Diagnostics --------------------------------------------------------

set.seed(123)
res_eco <- DHARMa::simulateResiduals(weed_glmm_eco)
plot(res_eco)

DHARMa::testDispersion(res_eco)
DHARMa::testZeroInflation(res_eco)

# Residuals vs fitted (sensitive check you’ve been watching)
DHARMa::plotResiduals(
  res_eco,
  form = predict(weed_glmm_eco, type = "response")
)

# 5) Inference: prefer LRT / drop1 over Wald Type III -------------------

# LRT for interaction (recommended vs Wald when diagnose() flags issues)
m_add <- update(weed_glmm_eco, . ~ . - weed_trt:weeds)
anova(m_add, weed_glmm_eco)

# Optional: LRT-style tests for all fixed terms
drop1(weed_glmm_eco, test = "Chisq")

```

#### New York only
```{r}
## Model testing / selection for New York weed biomass (kg ha^-1) -------
## Match Ecobean workflow:
##   1) Always use interaction: weed_trt * weeds
##   2) Drop site_year as fixed effect
##   3) Use simpler random structure: (1|site_year) + (1|site_year:block)
##   4) Tweedie(log) only; allow ZI only as a *starting point* if base fails
##   5) Dispersion ladder (no ZI): none -> site_year -> site_year + weeds -> site_year * weeds
##   6) Final inference via car::Anova(type = 3)

options(contrasts = c("contr.sum", "contr.poly"))

# 0) Helpers ------------------------------------------------------------

safe_aic <- function(mod) {
  out <- try(AIC(mod), silent = TRUE)
  if (inherits(out, "try-error")) return(NA_real_)
  out
}

is_valid_glmmTMB <- function(mod) {
  ll <- try(as.numeric(logLik(mod)), silent = TRUE)
  if (inherits(ll, "try-error")) return(FALSE)
  isTRUE(mod$sdr$pdHess) && is.finite(ll) && is.finite(safe_aic(mod))
}

aic_tbl <- function(mod_list) {
  tibble::tibble(
    model  = names(mod_list),
    df     = purrr::map_dbl(mod_list, ~ tryCatch(attr(logLik(.x), "df"), error = function(e) NA_real_)),
    AIC    = purrr::map_dbl(mod_list, safe_aic),
    pdHess = purrr::map_lgl(mod_list, ~ isTRUE(.x$sdr$pdHess)),
    valid  = purrr::map_lgl(mod_list, is_valid_glmmTMB)
  ) |>
    dplyr::mutate(
      deltaAIC = AIC - min(AIC[is.finite(AIC)], na.rm = TRUE)
    ) |>
    dplyr::arrange(dplyr::desc(valid), AIC)
}

# 1) Mean + random structure (SIMPLER RE; always interaction) -----------

form_ny_full <- weed_biomass_kg_ha ~ weed_trt * weeds +
  (1 | site_year) +
  (1 | site_year:block)

# 2) Tweedie starting point (base + optional ZI) ------------------------

wbm_ny_tw <- glmmTMB(
  formula = form_ny_full,
  family  = tweedie(link = "log"),
  data    = weed_biomass_ny
)

# Optional: ZI as fallback starter only (we do NOT carry ZI into disp search)
wbm_ny_tw_zi <- glmmTMB(
  formula   = form_ny_full,
  family    = tweedie(link = "log"),
  ziformula = ~ 1,
  data      = weed_biomass_ny
)

tweedie_cands_ny <- list(
  "NY: Tweedie base"     = wbm_ny_tw,
  "NY: Tweedie + ZI(~1)" = wbm_ny_tw_zi
)

aic_tw_ny <- aic_tbl(tweedie_cands_ny)

kable(
  aic_tw_ny,
  digits  = 2,
  caption = "New York weed biomass (kg ha⁻¹): Tweedie candidates (weed_trt * weeds; simpler RE)"
) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

best_tw_row_ny <- aic_tw_ny |>
  dplyr::filter(valid) |>
  dplyr::slice_min(AIC, n = 1)

if (nrow(best_tw_row_ny) == 0) {
  stop("No valid Tweedie models (finite logLik + pdHess) for New York biomass.")
}

best_tw_name_ny <- best_tw_row_ny$model
best_tw_mod_ny  <- tweedie_cands_ny[[best_tw_name_ny]]

cat("Selected Tweedie starting point (NY):", best_tw_name_ny, "\n")

# 3) Dispersion structure search (NO ZI) --------------------------------
# IMPORTANT: force ziformula = ~0 for dispersion models

base_nozi_ny <- update(best_tw_mod_ny, ziformula = ~ 0)

m0_ny <- base_nozi_ny

m_disp_sy_nozi_ny <- update(
  base_nozi_ny,
  dispformula = ~ site_year
)

m_disp_sy_weeds_nozi_ny <- update(
  base_nozi_ny,
  dispformula = ~ site_year + weeds
)

m_disp_sy_weeds_int_nozi_ny <- update(
  base_nozi_ny,
  dispformula = ~ site_year * weeds
)

disp_cands_ny <- list(
  "NY: m0 (no disp)"            = m0_ny,
  "NY: disp site_year"          = m_disp_sy_nozi_ny,
  "NY: disp site_year + weeds"  = m_disp_sy_weeds_nozi_ny,
  "NY: disp site_year * weeds"  = m_disp_sy_weeds_int_nozi_ny
)

aic_disp_ny <- aic_tbl(disp_cands_ny)

kable(
  aic_disp_ny,
  digits  = 2,
  caption = "New York weed biomass (kg ha⁻¹): dispersion-structure candidates (Tweedie; simpler RE; no ZI)"
) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

best_disp_row_ny <- aic_disp_ny |>
  dplyr::filter(valid) |>
  dplyr::slice_min(AIC, n = 1)

if (nrow(best_disp_row_ny) == 0) {
  stop("No valid dispersion models (finite logLik + pdHess) for New York biomass.")
}

best_disp_name_ny <- best_disp_row_ny$model
weed_glmm_ny      <- disp_cands_ny[[best_disp_name_ny]]

cat("Selected primary New York model: Tweedie (log) +", best_disp_name_ny, "\n")

# 4) Diagnostics + Type-III tests for chosen New York model -------------

set.seed(123)
res_ny <- DHARMa::simulateResiduals(weed_glmm_ny)
plot(res_ny)

DHARMa::testDispersion(res_ny)
DHARMa::testZeroInflation(res_ny)

car::Anova(weed_glmm_ny, type = 3)


```

### In-row weed biomass (kg ha⁻¹) 
#### Ecobean
```{r}
## Model testing / selection for Ecobean IN-ROW weed biomass (kg ha^-1) ----

options(contrasts = c("contr.sum", "contr.poly"))

# Subset: Ecobean only, ambient + surrogate weeds, non-missing in-row biomass
# Assumes weed_biomass_eco already exists from weed_biomass_bi
eco_inrow <- weed_biomass_eco |>
  dplyr::filter(!is.na(inrow_weed_biomass_kg_ha))

# Safe AIC helper (OK to redefine; same as above) -----------------------
safe_aic <- function(mod) {
  out <- try(AIC(mod), silent = TRUE)
  if (inherits(out, "try-error")) return(NA_real_)
  out
}

# 1) Full fixed/random structure used for family selection -------------
#   - weed_trt × weeds (mowing × weed treatment)
#   - site_year additive (overall site-year differences)
#   - split-plot random structure:
#       (1 | site_year) + (1 | site_year:block) + (1 | site_year:block:weed_trt)

form_eco_in <- inrow_weed_biomass_kg_ha ~ weed_trt * weeds + site_year +
  (1 | site_year) +
  (1 | site_year:block) +
  (1 | site_year:block:weed_trt)

## 2) Candidate families / structures (all with same fixed/random) ------

wbm_eco_in_tw <- glmmTMB(
  formula = form_eco_in,
  family  = tweedie(link = "log"),
  data    = eco_inrow
)

wbm_eco_in_nb <- glmmTMB(
  formula = form_eco_in,
  family  = nbinom2(link = "log"),
  data    = eco_inrow
)

wbm_eco_in_tw_zi <- glmmTMB(
  formula   = form_eco_in,
  family    = tweedie(link = "log"),
  ziformula = ~ 1,
  data      = eco_inrow
)

wbm_eco_in_tw_disp <- glmmTMB(
  formula     = form_eco_in,
  family      = tweedie(link = "log"),
  ziformula   = ~ 1,
  dispformula = ~ site_year,
  data        = eco_inrow
)

# AIC table for reporting -----------------------------------------------
aic_eco_in <- tibble::tibble(
  model = c(
    "ECO-IN: Tweedie",
    "ECO-IN: NB2",
    "ECO-IN: Tweedie + ZI(~1)",
    "ECO-IN: Tweedie + ZI(~1) + disp(site_year)"
  ),
  AIC = c(
    safe_aic(wbm_eco_in_tw),
    safe_aic(wbm_eco_in_nb),
    safe_aic(wbm_eco_in_tw_zi),
    safe_aic(wbm_eco_in_tw_disp)
  )
)

kable(
  aic_eco_in,
  digits  = 1,
  caption = "Ecobean IN-ROW weed biomass (kg ha\u207b\u00b9): candidate distributional families"
) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

## 3) Choose best family (NA-safe, require > 2 AIC units better) --------

eco_in_best   <- wbm_eco_in_tw
eco_in_best_n <- "ECO-IN: Tweedie"
eco_in_best_a <- safe_aic(wbm_eco_in_tw)

eco_in_cands <- list(
  "ECO-IN: NB2"                          = wbm_eco_in_nb,
  "ECO-IN: Tweedie + ZI(~1)"             = wbm_eco_in_tw_zi,
  "ECO-IN: Tweedie + ZI(~1) + disp(site_year)" = wbm_eco_in_tw_disp
)

for (nm in names(eco_in_cands)) {
  this_aic <- safe_aic(eco_in_cands[[nm]])
  
  # Skip if this candidate failed (NA AIC)
  if (!is.finite(this_aic)) next
  
  # If current "best" is NA, accept first finite candidate outright
  # Otherwise require > 2 AIC units improvement
  if (!is.finite(eco_in_best_a) || (this_aic + 2 < eco_in_best_a)) {
    eco_in_best   <- eco_in_cands[[nm]]
    eco_in_best_n <- nm
    eco_in_best_a <- this_aic
  }
}

if (!is.finite(eco_in_best_a)) {
  stop("All Ecobean IN-ROW candidate models failed (AIC is NA). Check glmmTMB fits.")
}

cat("Selected family/structure for Ecobean IN-ROW weed biomass:",
    eco_in_best_n, "\n")

## 4) Within chosen family: additive vs interaction ---------------------

# Interaction model in chosen family
wbm_eco_in_int <- eco_in_best

# Additive model: same family/ZI/dispersion, simpler fixed effects
wbm_eco_in_add <- update(
  eco_in_best,
  . ~ weed_trt + weeds + site_year   # random/Zi/disp carried over
)

# LRT to test interaction (weed_trt × weeds)
lrt_eco_in   <- anova(wbm_eco_in_add, wbm_eco_in_int)
p_int_eco_in <- lrt_eco_in$`Pr(>Chisq)`[2]

AIC_add_eco_in  <- AIC(wbm_eco_in_add)
AIC_int_eco_in  <- AIC(wbm_eco_in_int)
deltaAIC_eco_in <- AIC_add_eco_in - AIC_int_eco_in   # > 0 → interaction has lower AIC

# Thresholds (same gray-zone logic as total biomass)
p_strong    <- 0.01
p_none      <- 0.20
dAIC_strong <- 4

interaction_class_eco_in <- dplyr::case_when(
  p_int_eco_in < p_strong | deltaAIC_eco_in >= dAIC_strong ~ "interaction",
  p_int_eco_in > p_none  & abs(deltaAIC_eco_in) < 2        ~ "additive",
  TRUE                                                     ~ "gray_zone"
)

primary_model_name_eco_in <- dplyr::case_when(
  interaction_class_eco_in == "interaction" ~ "Interaction: weed_trt * weeds + site_year",
  interaction_class_eco_in == "additive"    ~ "Additive: weed_trt + weeds + site_year",
  TRUE                                      ~ "Additive (gray zone): weed_trt + weeds + site_year"
)

# For gray zone: still default to additive, but note it in text/tables
wbm_inrow_glmm_eco <- if (interaction_class_eco_in == "interaction") {
  wbm_eco_in_int
} else {
  wbm_eco_in_add
}

# AIC table for reporting -----------------------------------------------
aic_eco_in_out <- tibble::tibble(
  model = c(
    "Additive: weed_trt + weeds + site_year",
    "Interaction: weed_trt * weeds + site_year"
  ),
  AIC = c(AIC_add_eco_in, AIC_int_eco_in)
) |>
  dplyr::mutate(
    deltaAIC                 = AIC - min(AIC),
    Selected                 = dplyr::if_else(
      model == stringr::str_remove(primary_model_name_eco_in, "^Additive \\(gray zone\\): "),
      "Yes", ""
    ),
    Interaction_evidence     = interaction_class_eco_in
  )

kable(
  aic_eco_in_out,
  digits  = 2,
  caption = "Ecobean IN-ROW weed biomass (kg ha\u207b\u00b9): additive vs interaction (within chosen family)"
) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

cat(
  "\nSelected primary Ecobean model for IN-ROW weed biomass (used in emmeans/plots):\n  ",
  primary_model_name_eco_in,
  sprintf(
    "  [LRT p = %.3f; \u0394AIC (add - int) = %.2f; class = %s; family = %s]\n",
    p_int_eco_in, deltaAIC_eco_in, interaction_class_eco_in, eco_in_best_n
  )
)

## 5) Diagnostics + Type-III tests for chosen Ecobean IN-ROW model ------

set.seed(123)
res_eco_in <- DHARMa::simulateResiduals(wbm_inrow_glmm_eco)
plot(res_eco_in)
DHARMa::testDispersion(wbm_inrow_glmm_eco)
DHARMa::testZeroInflation(wbm_inrow_glmm_eco)

car::Anova(wbm_inrow_glmm_eco, type = 3)

```

#### New York only
```{r}
## Model testing / selection for NY-only IN-ROW weed biomass (kg ha^-1) ----

options(contrasts = c("contr.sum", "contr.poly"))

# Subset: New York only (CU + FH), ambient + surrogate weeds,
#         non-missing in-row biomass
ny_inrow <- weed_biomass_ny |>
  dplyr::filter(!is.na(inrow_weed_biomass_kg_ha))

# Safe AIC helper (same as above; OK to redefine) -----------------------
safe_aic <- function(mod) {
  out <- try(AIC(mod), silent = TRUE)
  if (inherits(out, "try-error")) return(NA_real_)
  out
}

# 1) Full fixed/random structure used for family selection -------------
#   - weed_trt × weeds (mowing × weed treatment)
#   - site_year additive (CU_2023, FH_2024, etc.)
#   - split-plot random structure within NY:
#       (1 | site_year) + (1 | site_year:block) + (1 | site_year:block:weed_trt)

form_ny_in <- inrow_weed_biomass_kg_ha ~ weed_trt * weeds + site_year +
  (1 | site_year) +
  (1 | site_year:block) +
  (1 | site_year:block:weed_trt)

## 2) Candidate families / structures (all with same fixed/random) ------

wbm_ny_in_tw <- glmmTMB(
  formula = form_ny_in,
  family  = tweedie(link = "log"),
  data    = ny_inrow
)

wbm_ny_in_nb <- glmmTMB(
  formula = form_ny_in,
  family  = nbinom2(link = "log"),
  data    = ny_inrow
)

wbm_ny_in_tw_zi <- glmmTMB(
  formula   = form_ny_in,
  family    = tweedie(link = "log"),
  ziformula = ~ 1,
  data      = ny_inrow
)

wbm_ny_in_tw_disp <- glmmTMB(
  formula     = form_ny_in,
  family      = tweedie(link = "log"),
  ziformula   = ~ 1,
  dispformula = ~ site_year,
  data        = ny_inrow
)

# AIC table for reporting -----------------------------------------------
aic_ny_in <- tibble::tibble(
  model = c(
    "NY-IN: Tweedie",
    "NY-IN: NB2",
    "NY-IN: Tweedie + ZI(~1)",
    "NY-IN: Tweedie + ZI(~1) + disp(site_year)"
  ),
  AIC = c(
    safe_aic(wbm_ny_in_tw),
    safe_aic(wbm_ny_in_nb),
    safe_aic(wbm_ny_in_tw_zi),
    safe_aic(wbm_ny_in_tw_disp)
  )
)

kable(
  aic_ny_in,
  digits  = 1,
  caption = "NY-only IN-ROW weed biomass (kg ha\u207b\u00b9): candidate distributional families"
) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

## 3) Choose best family (NA-safe, require > 2 AIC units better) --------

ny_in_best   <- wbm_ny_in_tw
ny_in_best_n <- "NY-IN: Tweedie"
ny_in_best_a <- safe_aic(wbm_ny_in_tw)

ny_in_cands <- list(
  "NY-IN: NB2"                           = wbm_ny_in_nb,
  "NY-IN: Tweedie + ZI(~1)"              = wbm_ny_in_tw_zi,
  "NY-IN: Tweedie + ZI(~1) + disp(site_year)" = wbm_ny_in_tw_disp
)

for (nm in names(ny_in_cands)) {
  this_aic <- safe_aic(ny_in_cands[[nm]])
  
  if (!is.finite(this_aic)) next
  
  if (!is.finite(ny_in_best_a) || (this_aic + 2 < ny_in_best_a)) {
    ny_in_best   <- ny_in_cands[[nm]]
    ny_in_best_n <- nm
    ny_in_best_a <- this_aic
  }
}

if (!is.finite(ny_in_best_a)) {
  stop("All NY-only IN-ROW candidate models failed (AIC is NA). Check glmmTMB fits.")
}

cat("Selected family/structure for NY-only IN-ROW weed biomass:",
    ny_in_best_n, "\n")

## 4) Within chosen family: additive vs interaction ---------------------

wbm_ny_in_int <- ny_in_best

wbm_ny_in_add <- update(
  ny_in_best,
  . ~ weed_trt + weeds + site_year
)

lrt_ny_in   <- anova(wbm_ny_in_add, wbm_ny_in_int)
p_int_ny_in <- lrt_ny_in$`Pr(>Chisq)`[2]

AIC_add_ny_in  <- AIC(wbm_ny_in_add)
AIC_int_ny_in  <- AIC(wbm_ny_in_int)
deltaAIC_ny_in <- AIC_add_ny_in - AIC_int_ny_in

p_strong    <- 0.01
p_none      <- 0.20
dAIC_strong <- 4

interaction_class_ny_in <- dplyr::case_when(
  p_int_ny_in < p_strong | deltaAIC_ny_in >= dAIC_strong ~ "interaction",
  p_int_ny_in > p_none  & abs(deltaAIC_ny_in) < 2        ~ "additive",
  TRUE                                                   ~ "gray_zone"
)

primary_model_name_ny_in <- dplyr::case_when(
  interaction_class_ny_in == "interaction" ~ "Interaction: weed_trt * weeds + site_year",
  interaction_class_ny_in == "additive"    ~ "Additive: weed_trt + weeds + site_year",
  TRUE                                     ~ "Additive (gray zone): weed_trt + weeds + site_year"
)

wbm_inrow_glmm_ny <- if (interaction_class_ny_in == "interaction") {
  wbm_ny_in_int
} else {
  wbm_ny_in_add
}

aic_ny_in_out <- tibble::tibble(
  model = c(
    "Additive: weed_trt + weeds + site_year",
    "Interaction: weed_trt * weeds + site_year"
  ),
  AIC = c(AIC_add_ny_in, AIC_int_ny_in)
) |>
  dplyr::mutate(
    deltaAIC                 = AIC - min(AIC),
    Selected                 = dplyr::if_else(
      model == stringr::str_remove(primary_model_name_ny_in, "^Additive \\(gray zone\\): "),
      "Yes", ""
    ),
    Interaction_evidence     = interaction_class_ny_in
  )

kable(
  aic_ny_in_out,
  digits  = 2,
  caption = "NY-only IN-ROW weed biomass (kg ha\u207b\u00b9): additive vs interaction (within chosen family)"
) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

cat(
  "\nSelected primary NY-only model for IN-ROW weed biomass (used in emmeans/plots):\n  ",
  primary_model_name_ny_in,
  sprintf(
    "  [LRT p = %.3f; \u0394AIC (add - int) = %.2f; class = %s; family = %s]\n",
    p_int_ny_in, deltaAIC_ny_in, interaction_class_ny_in, ny_in_best_n
  )
)

## 5) Diagnostics + Type-III tests for chosen NY-only IN-ROW model ------

set.seed(123)
res_ny_in <- DHARMa::simulateResiduals(wbm_inrow_glmm_ny)
plot(res_ny_in)
DHARMa::testDispersion(wbm_inrow_glmm_ny)
DHARMa::testZeroInflation(wbm_inrow_glmm_ny)

car::Anova(wbm_inrow_glmm_ny, type = 3)

```
### Inter-row weed biomass (kg ha⁻¹) 
#### Ecobean
```{r}
## Model testing / selection for Ecobean INTER-ROW weed biomass (kg ha^-1) ----

options(contrasts = c("contr.sum", "contr.poly"))

# Subset: Ecobean only (all 5 locations), ambient + surrogate weeds,
#         non-missing inter-row biomass
eco_inter <- weed_biomass_eco |>
  dplyr::filter(!is.na(interrow_weed_biomass_kg_ha))

# Safe AIC helper (OK if already defined; re-defining is harmless) ------
safe_aic <- function(mod) {
  out <- try(AIC(mod), silent = TRUE)
  if (inherits(out, "try-error")) return(NA_real_)
  out
}

# 1) Full fixed/random structure used for family selection -------------
#   - Fixed: weed_trt × weeds + site_year
#   - Random: full split-plot structure
#       (1 | site_year) + (1 | site_year:block) + (1 | site_year:block:weed_trt)

form_eco_inter <- interrow_weed_biomass_kg_ha ~ weed_trt * weeds + site_year +
  (1 | site_year) +
  (1 | site_year:block) +
  (1 | site_year:block:weed_trt)

## 2) Candidate families / structures (all with same fixed/random) ------

wbm_eco_inter_tw <- glmmTMB(
  formula = form_eco_inter,
  family  = tweedie(link = "log"),
  data    = eco_inter
)

wbm_eco_inter_nb <- glmmTMB(
  formula = form_eco_inter,
  family  = nbinom2(link = "log"),
  data    = eco_inter
)

wbm_eco_inter_tw_zi <- glmmTMB(
  formula   = form_eco_inter,
  family    = tweedie(link = "log"),
  ziformula = ~ 1,
  data      = eco_inter
)

wbm_eco_inter_tw_disp <- glmmTMB(
  formula     = form_eco_inter,
  family      = tweedie(link = "log"),
  ziformula   = ~ 1,
  dispformula = ~ site_year,
  data        = eco_inter
)

# AIC table for reporting -----------------------------------------------
aic_eco_inter <- tibble::tibble(
  model = c(
    "ECO-INTER: Tweedie",
    "ECO-INTER: NB2",
    "ECO-INTER: Tweedie + ZI(~1)",
    "ECO-INTER: Tweedie + ZI(~1) + disp(site_year)"
  ),
  AIC = c(
    safe_aic(wbm_eco_inter_tw),
    safe_aic(wbm_eco_inter_nb),
    safe_aic(wbm_eco_inter_tw_zi),
    safe_aic(wbm_eco_inter_tw_disp)
  )
)

kable(
  aic_eco_inter,
  digits  = 1,
  caption = "Ecobean INTER-ROW weed biomass (kg ha\u207b\u00b9): candidate distributional families"
) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

## 3) Choose best family (NA-safe, require > 2 AIC units better) --------

eco_inter_best   <- wbm_eco_inter_tw
eco_inter_best_n <- "ECO-INTER: Tweedie"
eco_inter_best_a <- safe_aic(wbm_eco_inter_tw)

eco_inter_cands <- list(
  "ECO-INTER: NB2"                          = wbm_eco_inter_nb,
  "ECO-INTER: Tweedie + ZI(~1)"             = wbm_eco_inter_tw_zi,
  "ECO-INTER: Tweedie + ZI(~1) + disp(site_year)" = wbm_eco_inter_tw_disp
)

for (nm in names(eco_inter_cands)) {
  this_aic <- safe_aic(eco_inter_cands[[nm]])
  
  # Skip if candidate failed
  if (!is.finite(this_aic)) next
  
  # If current "best" is NA, take first finite; otherwise require > 2 AIC units improvement
  if (!is.finite(eco_inter_best_a) || (this_aic + 2 < eco_inter_best_a)) {
    eco_inter_best   <- eco_inter_cands[[nm]]
    eco_inter_best_n <- nm
    eco_inter_best_a <- this_aic
  }
}

if (!is.finite(eco_inter_best_a)) {
  stop("All Ecobean INTER-ROW candidate models failed (AIC is NA). Check glmmTMB fits.")
}

cat("Selected family/structure for Ecobean INTER-ROW weed biomass:",
    eco_inter_best_n, "\n")

## 4) Within chosen family: additive vs interaction ---------------------

# Full interaction (weed_trt × weeds) in chosen family
wbm_eco_inter_int <- eco_inter_best

# Additive version: same family/ZI/dispersion, simpler fixed effects
wbm_eco_inter_add <- update(
  eco_inter_best,
  . ~ weed_trt + weeds + site_year
)

# LRT: does the interaction help?
lrt_eco_inter   <- anova(wbm_eco_inter_add, wbm_eco_inter_int)
p_int_eco_inter <- lrt_eco_inter$`Pr(>Chisq)`[2]

AIC_add_eco_inter  <- AIC(wbm_eco_inter_add)
AIC_int_eco_inter  <- AIC(wbm_eco_inter_int)
deltaAIC_eco_inter <- AIC_add_eco_inter - AIC_int_eco_inter

# Thresholds
p_strong    <- 0.01
p_none      <- 0.20
dAIC_strong <- 4

interaction_class_eco_inter <- dplyr::case_when(
  p_int_eco_inter < p_strong | deltaAIC_eco_inter >= dAIC_strong ~ "interaction",
  p_int_eco_inter > p_none  & abs(deltaAIC_eco_inter) < 2        ~ "additive",
  TRUE                                                           ~ "gray_zone"
)

primary_model_name_eco_inter <- dplyr::case_when(
  interaction_class_eco_inter == "interaction" ~ "Interaction: weed_trt * weeds + site_year",
  interaction_class_eco_inter == "additive"    ~ "Additive: weed_trt + weeds + site_year",
  TRUE                                         ~ "Additive (gray zone): weed_trt + weeds + site_year"
)

# For gray zone, default to additive but note it in the text
wbm_inter_glmm_eco <- if (interaction_class_eco_inter == "interaction") {
  wbm_eco_inter_int
} else {
  wbm_eco_inter_add
}

# AIC table for reporting -----------------------------------------------
aic_eco_inter_out <- tibble::tibble(
  model = c(
    "Additive: weed_trt + weeds + site_year",
    "Interaction: weed_trt * weeds + site_year"
  ),
  AIC = c(AIC_add_eco_inter, AIC_int_eco_inter)
) |>
  dplyr::mutate(
    deltaAIC             = AIC - min(AIC),
    Selected             = dplyr::if_else(
      model == stringr::str_remove(primary_model_name_eco_inter,
                                   "^Additive \\(gray zone\\): "),
      "Yes", ""
    ),
    Interaction_evidence = interaction_class_eco_inter
  )

kable(
  aic_eco_inter_out,
  digits  = 2,
  caption = "Ecobean INTER-ROW weed biomass (kg ha\u207b\u00b9): additive vs interaction (within chosen family)"
) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

cat(
  "\nSelected primary Ecobean model for INTER-ROW weed biomass (used in emmeans/plots):\n  ",
  primary_model_name_eco_inter,
  sprintf(
    "  [LRT p = %.3f; \u0394AIC (add - int) = %.2f; class = %s; family = %s]\n",
    p_int_eco_inter, deltaAIC_eco_inter, interaction_class_eco_inter, eco_inter_best_n
  )
)

## 5) Diagnostics + Type-III tests for chosen Ecobean INTER-ROW model ---

set.seed(123)
res_eco_inter <- DHARMa::simulateResiduals(wbm_inter_glmm_eco)
plot(res_eco_inter)
DHARMa::testDispersion(wbm_inter_glmm_eco)
DHARMa::testZeroInflation(wbm_inter_glmm_eco)

car::Anova(wbm_inter_glmm_eco, type = 3)

```
#### New York only
```{r}
## Model testing / selection for NY-only INTER-ROW weed biomass (kg ha^-1) ----

options(contrasts = c("contr.sum", "contr.poly"))

# Subset: NY only (Cornell + Farm Hub), ambient + surrogate weeds,
#         non-missing inter-row biomass
ny_inter <- weed_biomass_ny |>
  dplyr::filter(!is.na(interrow_weed_biomass_kg_ha))

# Safe AIC helper (re-use or re-define) ---------------------------------
safe_aic <- function(mod) {
  out <- try(AIC(mod), silent = TRUE)
  if (inherits(out, "try-error")) return(NA_real_)
  out
}

# 1) Full fixed/random structure used for family selection -------------
form_ny_inter <- interrow_weed_biomass_kg_ha ~ weed_trt * weeds + site_year +
  (1 | site_year) +
  (1 | site_year:block) +
  (1 | site_year:block:weed_trt)

## 2) Candidate families / structures (all with same fixed/random) ------

wbm_ny_inter_tw <- glmmTMB(
  formula = form_ny_inter,
  family  = tweedie(link = "log"),
  data    = ny_inter
)

wbm_ny_inter_nb <- glmmTMB(
  formula = form_ny_inter,
  family  = nbinom2(link = "log"),
  data    = ny_inter
)

wbm_ny_inter_tw_zi <- glmmTMB(
  formula   = form_ny_inter,
  family    = tweedie(link = "log"),
  ziformula = ~ 1,
  data      = ny_inter
)

wbm_ny_inter_tw_disp <- glmmTMB(
  formula     = form_ny_inter,
  family      = tweedie(link = "log"),
  ziformula   = ~ 1,
  dispformula = ~ site_year,
  data        = ny_inter
)

# AIC table for reporting -----------------------------------------------
aic_ny_inter <- tibble::tibble(
  model = c(
    "NY-INTER: Tweedie",
    "NY-INTER: NB2",
    "NY-INTER: Tweedie + ZI(~1)",
    "NY-INTER: Tweedie + ZI(~1) + disp(site_year)"
  ),
  AIC = c(
    safe_aic(wbm_ny_inter_tw),
    safe_aic(wbm_ny_inter_nb),
    safe_aic(wbm_ny_inter_tw_zi),
    safe_aic(wbm_ny_inter_tw_disp)
  )
)

kable(
  aic_ny_inter,
  digits  = 1,
  caption = "NY-only INTER-ROW weed biomass (kg ha\u207b\u00b9): candidate distributional families"
) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

## 3) Choose best family (NA-safe, require > 2 AIC units better) --------

ny_inter_best   <- wbm_ny_inter_tw
ny_inter_best_n <- "NY-INTER: Tweedie"
ny_inter_best_a <- safe_aic(wbm_ny_inter_tw)

ny_inter_cands <- list(
  "NY-INTER: NB2"                          = wbm_ny_inter_nb,
  "NY-INTER: Tweedie + ZI(~1)"             = wbm_ny_inter_tw_zi,
  "NY-INTER: Tweedie + ZI(~1) + disp(site_year)" = wbm_ny_inter_tw_disp
)

for (nm in names(ny_inter_cands)) {
  this_aic <- safe_aic(ny_inter_cands[[nm]])
  
  if (!is.finite(this_aic)) next
  
  if (!is.finite(ny_inter_best_a) || (this_aic + 2 < ny_inter_best_a)) {
    ny_inter_best   <- ny_inter_cands[[nm]]
    ny_inter_best_n <- nm
    ny_inter_best_a <- this_aic
  }
}

if (!is.finite(ny_inter_best_a)) {
  stop("All NY-only INTER-ROW candidate models failed (AIC is NA). Check glmmTMB fits.")
}

cat("Selected family/structure for NY-only INTER-ROW weed biomass:",
    ny_inter_best_n, "\n")

## 4) Within chosen family: additive vs interaction ---------------------

wbm_ny_inter_int <- ny_inter_best

wbm_ny_inter_add <- update(
  ny_inter_best,
  . ~ weed_trt + weeds + site_year
)

lrt_ny_inter   <- anova(wbm_ny_inter_add, wbm_ny_inter_int)
p_int_ny_inter <- lrt_ny_inter$`Pr(>Chisq)`[2]

AIC_add_ny_inter  <- AIC(wbm_ny_inter_add)
AIC_int_ny_inter  <- AIC(wbm_ny_inter_int)
deltaAIC_ny_inter <- AIC_add_ny_inter - AIC_int_ny_inter

p_strong    <- 0.01
p_none      <- 0.20
dAIC_strong <- 4

interaction_class_ny_inter <- dplyr::case_when(
  p_int_ny_inter < p_strong | deltaAIC_ny_inter >= dAIC_strong ~ "interaction",
  p_int_ny_inter > p_none  & abs(deltaAIC_ny_inter) < 2        ~ "additive",
  TRUE                                                         ~ "gray_zone"
)

primary_model_name_ny_inter <- dplyr::case_when(
  interaction_class_ny_inter == "interaction" ~ "Interaction: weed_trt * weeds + site_year",
  interaction_class_ny_inter == "additive"    ~ "Additive: weed_trt + weeds + site_year",
  TRUE                                        ~ "Additive (gray zone): weed_trt + weeds + site_year"
)

wbm_inter_glmm_ny <- if (interaction_class_ny_inter == "interaction") {
  wbm_ny_inter_int
} else {
  wbm_ny_inter_add
}

aic_ny_inter_out <- tibble::tibble(
  model = c(
    "Additive: weed_trt + weeds + site_year",
    "Interaction: weed_trt * weeds + site_year"
  ),
  AIC = c(AIC_add_ny_inter, AIC_int_ny_inter)
) |>
  dplyr::mutate(
    deltaAIC             = AIC - min(AIC),
    Selected             = dplyr::if_else(
      model == stringr::str_remove(primary_model_name_ny_inter,
                                   "^Additive \\(gray zone\\): "),
      "Yes", ""
    ),
    Interaction_evidence = interaction_class_ny_inter
  )

kable(
  aic_ny_inter_out,
  digits  = 2,
  caption = "NY-only INTER-ROW weed biomass (kg ha\u207b\u00b9): additive vs interaction (within chosen family)"
) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

cat(
  "\nSelected primary NY-only model for INTER-ROW weed biomass (used in emmeans/plots):\n  ",
  primary_model_name_ny_inter,
  sprintf(
    "  [LRT p = %.3f; \u0394AIC (add - int) = %.2f; class = %s; family = %s]\n",
    p_int_ny_inter, deltaAIC_ny_inter, interaction_class_ny_inter, ny_inter_best_n
  )
)

## 5) Diagnostics + Type-III tests for chosen NY-only INTER-ROW model ---

set.seed(123)
res_ny_inter <- DHARMa::simulateResiduals(wbm_inter_glmm_ny)
plot(res_ny_inter)
DHARMa::testDispersion(wbm_inter_glmm_ny)
DHARMa::testZeroInflation(wbm_inter_glmm_ny)

car::Anova(wbm_inter_glmm_ny, type = 3)

```


```{r}
## Quick check: full interaction model (weed_trt * weeds) ----------------
## Uses the same family / ZI / dispersion structure as weed_glmm

wbm_int_full <- update(
  weed_glmm,
  . ~ weed_trt * weeds + site_year +
    (1 | site_year) +
    (1 | site_year:block) +
    (1 | site_year:block:weed_trt)
)

# Optional: brief diagnostics just to be sure it’s sane
set.seed(123)
res_int <- DHARMa::simulateResiduals(wbm_int_full)
plot(res_int)
DHARMa::testDispersion(res_int)
DHARMa::testZeroInflation(res_int)

# Type-III Wald tests for the interaction model
anova_wbm_int <- car::Anova(wbm_int_full, type = 3)
anova_wbm_int

```


# Summary tables
## Total weed biomass
###Ecobean
```{r}
## Ecobean: TOTAL weed biomass (kg ha^-1) summary tables -----------------
## Updated for final model where site_year is RANDOM (not fixed):
##   - No emmeans / CLDs for site_year (not in reference grid)
##   - Keep: Type III p-values, treatment means, weediness means, and
##           treatment means within weediness (interaction) using emmeans
##   - Optional: raw site_year means as a descriptive table

# Directory for all Ecobean weed-biomass tables -------------------------
tab_dir_wbm_eco <- here("analysis", "tables", "weed-biomass", "ecobean", "total")
dir.create(tab_dir_wbm_eco, showWarnings = FALSE, recursive = TRUE)

## 1) P-value summary (Type III Wald tests) ------------------------------

anova_wbm_eco <- car::Anova(weed_glmm_eco, type = 3)

anova_wbm_eco_df <- anova_wbm_eco |>
  as.data.frame() |>
  tibble::rownames_to_column("Effect")

p_trt_eco   <- anova_wbm_eco_df$`Pr(>Chisq)`[anova_wbm_eco_df$Effect == "weed_trt"]
p_weeds_eco <- anova_wbm_eco_df$`Pr(>Chisq)`[anova_wbm_eco_df$Effect == "weeds"]
p_int_eco   <- anova_wbm_eco_df$`Pr(>Chisq)`[anova_wbm_eco_df$Effect == "weed_trt:weeds"]

pvals_wbm_eco <- tibble::tibble(
  Effect = c(
    "Mowing (weed_trt)",
    "Weediness (weeds)",
    "Mowing × Weediness (weed_trt × weeds)"
  ),
  p_raw = c(p_trt_eco, p_weeds_eco, p_int_eco)
) |>
  dplyr::mutate(
    `P-value` = dplyr::case_when(
      is.na(p_raw)  ~ NA_character_,
      p_raw < 0.001 ~ "<0.001",
      p_raw < 0.01  ~ "<0.01",
      TRUE          ~ sprintf("%.3f", p_raw)
    )
  ) |>
  dplyr::select(Effect, `P-value`)

readr::write_csv(
  pvals_wbm_eco,
  file.path(tab_dir_wbm_eco, "tab_eco-total-wbm_Anova_pvals.csv")
)

pvals_wbm_eco |>
  kable(
    caption   = "Ecobean total weed biomass (kg ha\u207b\u00b9): Type III ANOVA p-values (final model)",
    col.names = c("Effect", "P-value")
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

## 2) OPTIONAL descriptive block: RAW site-year means --------------------
## (site_year is random, so we report RAW means only; no model CLDs)

raw_loc_wbm_eco <- weed_biomass_eco |>
  dplyr::group_by(site_year) |>
  dplyr::summarise(
    n        = dplyr::n(),
    raw_mean = mean(weed_biomass_kg_ha, na.rm = TRUE),
    raw_se   = sd(weed_biomass_kg_ha, na.rm = TRUE) / sqrt(sum(!is.na(weed_biomass_kg_ha))),
    .groups  = "drop"
  ) |>
  dplyr::mutate(
    site_year = as.factor(site_year),
    raw_mean  = round(raw_mean, 1),
    raw_se    = round(raw_se, 1)
  ) |>
  dplyr::arrange(site_year)

readr::write_csv(
  raw_loc_wbm_eco,
  file.path(tab_dir_wbm_eco, "tab_eco-total-wbm_site-year_RAW_means.csv")
)

raw_loc_wbm_eco |>
  kable(
    caption   = "Ecobean weed biomass (kg ha\u207b\u00b9): raw site-year means \u00b1 SE (descriptive only)",
    col.names = c("Site-year", "n", "Raw mean", "Raw SE")
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

## 3) Treatment block: mowing means (model + raw) ------------------------

emm_wbm_eco <- emmeans(
  weed_glmm_eco,
  ~ weed_trt,
  type = "response"
)

emm_trt_wbm_eco_df <- tidy_emm(
  emm_wbm_eco,
  trt_var    = "weed_trt",
  ref_levels = mow_levels
) |>
  dplyr::mutate(
    weed_trt   = factor(weed_trt, levels = mow_levels),
    model_mean = response
  ) |>
  dplyr::select(weed_trt, model_mean, SE, ci_low, ci_high)

cld_wbm_eco <- multcomp::cld(
  emm_wbm_eco,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE
) |>
  as_tibble() |>
  dplyr::mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    trt_CLD  = stringr::str_trim(.group)
  ) |>
  dplyr::select(weed_trt, trt_CLD)

raw_trt_wbm_eco <- weed_biomass_eco |>
  dplyr::group_by(weed_trt) |>
  dplyr::summarise(
    raw_mean = mean(weed_biomass_kg_ha, na.rm = TRUE),
    .groups  = "drop"
  ) |>
  dplyr::mutate(weed_trt = factor(weed_trt, levels = mow_levels))

trt_summary_wbm_eco <- emm_trt_wbm_eco_df |>
  dplyr::left_join(cld_wbm_eco,     by = "weed_trt") |>
  dplyr::left_join(raw_trt_wbm_eco, by = "weed_trt") |>
  dplyr::mutate(
    model_mean = round(model_mean, 1),
    SE         = round(SE, 1),
    ci_low     = round(ci_low, 1),
    ci_high    = round(ci_high, 1),
    raw_mean   = round(raw_mean, 1),
    raw_CLD    = trt_CLD
  ) |>
  dplyr::arrange(weed_trt)

readr::write_csv(
  trt_summary_wbm_eco,
  file.path(tab_dir_wbm_eco, "tab_eco-total-wbm_treatment_means_CLD.csv")
)

trt_summary_wbm_eco |>
  kable(
    caption   = "Ecobean weed biomass (kg ha\u207b\u00b9): mowing-treatment means with CLDs",
    col.names = c(
      "Treatment", "Model mean", "SE",
      "Lower CI", "Upper CI",
      "Model CLD", "Raw mean", "Raw CLD"
    )
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

## 3b) Weediness block: ambient vs surrogate means (model + raw) --------

emm_wbm_weed_eco <- emmeans(
  weed_glmm_eco,
  ~ weeds,
  type = "response"
)

emm_weeds_wbm_eco_df <- tidy_emm(
  emm_wbm_weed_eco,
  trt_var    = "weeds",
  ref_levels = c("Ambient weeds", "Surrogate weeds")
) |>
  dplyr::mutate(
    weeds      = factor(weeds, levels = c("Ambient weeds", "Surrogate weeds")),
    model_mean = response
  ) |>
  dplyr::select(weeds, model_mean, SE, ci_low, ci_high)

cld_wbm_weed_eco <- multcomp::cld(
  emm_wbm_weed_eco,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE
) |>
  as_tibble() |>
  dplyr::mutate(
    weeds     = factor(weeds, levels = c("Ambient weeds", "Surrogate weeds")),
    weeds_CLD = stringr::str_trim(.group)
  ) |>
  dplyr::select(weeds, weeds_CLD)

raw_weeds_wbm_eco <- weed_biomass_eco |>
  dplyr::group_by(weeds) |>
  dplyr::summarise(
    raw_mean = mean(weed_biomass_kg_ha, na.rm = TRUE),
    .groups  = "drop"
  ) |>
  dplyr::mutate(
    weeds = factor(weeds, levels = c("Ambient weeds", "Surrogate weeds"))
  )

weediness_summary_wbm_eco <- emm_weeds_wbm_eco_df |>
  dplyr::left_join(cld_wbm_weed_eco,  by = "weeds") |>
  dplyr::left_join(raw_weeds_wbm_eco, by = "weeds") |>
  dplyr::mutate(
    model_mean = round(model_mean, 1),
    SE         = round(SE, 1),
    ci_low     = round(ci_low, 1),
    ci_high    = round(ci_high, 1),
    raw_mean   = round(raw_mean, 1)
  ) |>
  dplyr::arrange(weeds)

readr::write_csv(
  weediness_summary_wbm_eco,
  file.path(tab_dir_wbm_eco, "tab_eco-total-wbm_weediness_means_CLD.csv")
)

weediness_summary_wbm_eco |>
  kable(
    caption   = "Ecobean weed biomass (kg ha\u207b\u00b9): weediness (ambient vs surrogate) means with CLDs",
    col.names = c(
      "Weediness", "Model mean", "SE",
      "Lower CI", "Upper CI",
      "Model CLD", "Raw mean"
    )
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

## 4) Interaction block: mowing means within weediness -------------------
## This corresponds to the fixed-effect interaction in the model.
## (More useful than site_year x treatment now that site_year is random.)

emm_int_wbm_eco <- emmeans(
  weed_glmm_eco,
  ~ weed_trt | weeds,
  type = "response"
)

emm_int_wbm_eco_df <- tidy_emm(
  emm_int_wbm_eco,
  trt_var    = "weed_trt",
  ref_levels = mow_levels
) |>
  dplyr::mutate(
    weeds      = factor(weeds, levels = c("Ambient weeds", "Surrogate weeds")),
    weed_trt   = factor(weed_trt, levels = mow_levels),
    model_mean = response
  ) |>
  dplyr::select(weeds, weed_trt, model_mean, SE, ci_low, ci_high)

cld_int_wbm_eco <- multcomp::cld(
  emm_int_wbm_eco,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE
) |>
  as_tibble() |>
  dplyr::mutate(
    weeds    = factor(weeds, levels = c("Ambient weeds", "Surrogate weeds")),
    weed_trt = factor(weed_trt, levels = mow_levels),
    int_CLD  = stringr::str_trim(.group)
  ) |>
  dplyr::select(weeds, weed_trt, int_CLD)

raw_int_wbm_eco <- weed_biomass_eco |>
  dplyr::group_by(weeds, weed_trt) |>
  dplyr::summarise(
    raw_mean = mean(weed_biomass_kg_ha, na.rm = TRUE),
    .groups  = "drop"
  ) |>
  dplyr::mutate(
    weeds    = factor(weeds, levels = c("Ambient weeds", "Surrogate weeds")),
    weed_trt = factor(weed_trt, levels = mow_levels)
  )

int_summary_wbm_eco <- emm_int_wbm_eco_df |>
  dplyr::left_join(cld_int_wbm_eco, by = c("weeds", "weed_trt")) |>
  dplyr::left_join(raw_int_wbm_eco, by = c("weeds", "weed_trt")) |>
  dplyr::mutate(
    model_mean = round(model_mean, 1),
    SE         = round(SE, 1),
    ci_low     = round(ci_low, 1),
    ci_high    = round(ci_high, 1),
    raw_mean   = round(raw_mean, 1),
    raw_CLD    = int_CLD
  ) |>
  dplyr::arrange(weeds, weed_trt)

readr::write_csv(
  int_summary_wbm_eco,
  file.path(tab_dir_wbm_eco, "tab_eco-total-wbm_weeds_treatment_means_CLD.csv")
)

int_summary_wbm_eco |>
  kable(
    caption   = "Ecobean weed biomass (kg ha\u207b\u00b9): mowing-treatment means within weediness with CLDs",
    col.names = c(
      "Weediness", "Treatment",
      "Model mean", "SE", "Lower CI", "Upper CI",
      "Model CLD", "Raw mean", "Raw CLD"
    )
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

## 5) Model-info row for global response summary -------------------------

fixed_effects_eco  <- "weed_trt * weeds"
random_effects_eco <- "(1 | site_year) + (1 | site_year:block)"

final_aic_eco <- round(AIC(weed_glmm_eco), 2)
final_disp_eco <- tryCatch(
  format(stats::formula(weed_glmm_eco$modelInfo$dispformula)),
  error = function(e) NA_character_
)

model_info_wbm_eco <- tibble::tibble(
  response_label    = "Total weed biomass (kg ha^-1), Ecobean model-predicted means*",
  family_structure  = "Tweedie (log link)",
  fixed_effects     = fixed_effects_eco,
  random_effects    = random_effects_eco,
  dispersion_model  = final_disp_eco,
  AIC_selected      = final_aic_eco,
  pdHess            = isTRUE(weed_glmm_eco$sdr$pdHess)
)

readr::write_csv(
  model_info_wbm_eco,
  file.path(tab_dir_wbm_eco, "tab_eco-total-wbm_model-info.csv")
)

## 6) OPTIONAL: combine into one Ecobean workbook ------------------------

if (requireNamespace("writexl", quietly = TRUE)) {
  wbm_total_tables_eco <- list(
    Anova_pvals            = pvals_wbm_eco,
    SiteYear_RAW_means     = raw_loc_wbm_eco,
    Treatment_means_CLD    = trt_summary_wbm_eco,
    Weediness_means_CLD    = weediness_summary_wbm_eco,
    Weeds_x_Treatment_means = int_summary_wbm_eco,
    Model_info             = model_info_wbm_eco
  )

  writexl::write_xlsx(
    wbm_total_tables_eco,
    path = file.path(tab_dir_wbm_eco, "Ecobean_total-weed-biomass_all-tables.xlsx")
  )
} else {
  message("Package 'writexl' not installed; skipping Ecobean Excel export.")
}

```
### New York Only
```{r}
## New York: TOTAL weed biomass (kg ha^-1) summary tables ----------------
## Updated for final NY model where site_year is RANDOM (not fixed):
##   - No emmeans / CLDs for site_year (not in reference grid)
##   - Keep: Type III p-values, treatment means, weediness means, and
##           treatment means within weediness (interaction) using emmeans
##   - Optional: raw site_year means as a descriptive table

# Directory for all NY weed-biomass tables ------------------------------
tab_dir_wbm_ny <- here("analysis", "tables", "weed-biomass", "newyork", "total")
dir.create(tab_dir_wbm_ny, showWarnings = FALSE, recursive = TRUE)

## 1) P-value summary (Type III Wald tests) ------------------------------

anova_wbm_ny <- car::Anova(weed_glmm_ny, type = 3)

anova_wbm_ny_df <- anova_wbm_ny |>
  as.data.frame() |>
  tibble::rownames_to_column("Effect")

p_trt_ny   <- anova_wbm_ny_df$`Pr(>Chisq)`[anova_wbm_ny_df$Effect == "weed_trt"]
p_weeds_ny <- anova_wbm_ny_df$`Pr(>Chisq)`[anova_wbm_ny_df$Effect == "weeds"]
p_int_ny   <- anova_wbm_ny_df$`Pr(>Chisq)`[anova_wbm_ny_df$Effect == "weed_trt:weeds"]

pvals_wbm_ny <- tibble::tibble(
  Effect = c(
    "Mowing (weed_trt)",
    "Weediness (weeds)",
    "Mowing × Weediness (weed_trt × weeds)"
  ),
  p_raw = c(p_trt_ny, p_weeds_ny, p_int_ny)
) |>
  dplyr::mutate(
    `P-value` = dplyr::case_when(
      is.na(p_raw)  ~ NA_character_,
      p_raw < 0.001 ~ "<0.001",
      p_raw < 0.01  ~ "<0.01",
      TRUE          ~ sprintf("%.3f", p_raw)
    )
  ) |>
  dplyr::select(Effect, `P-value`)

readr::write_csv(
  pvals_wbm_ny,
  file.path(tab_dir_wbm_ny, "tab_ny-total-wbm_Anova_pvals.csv")
)

pvals_wbm_ny |>
  kable(
    caption   = "New York total weed biomass (kg ha\u207b\u00b9): Type III ANOVA p-values (final model)",
    col.names = c("Effect", "P-value")
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

## 2) OPTIONAL descriptive block: RAW site-year means --------------------
## (site_year is random, so we report RAW means only; no model CLDs)

raw_loc_wbm_ny <- weed_biomass_ny |>
  dplyr::group_by(site_year) |>
  dplyr::summarise(
    n        = dplyr::n(),
    raw_mean = mean(weed_biomass_kg_ha, na.rm = TRUE),
    raw_se   = sd(weed_biomass_kg_ha, na.rm = TRUE) / sqrt(sum(!is.na(weed_biomass_kg_ha))),
    .groups  = "drop"
  ) |>
  dplyr::mutate(
    site_year = as.factor(site_year),
    raw_mean  = round(raw_mean, 1),
    raw_se    = round(raw_se, 1)
  ) |>
  dplyr::arrange(site_year)

readr::write_csv(
  raw_loc_wbm_ny,
  file.path(tab_dir_wbm_ny, "tab_ny-total-wbm_site-year_RAW_means.csv")
)

raw_loc_wbm_ny |>
  kable(
    caption   = "New York weed biomass (kg ha\u207b\u00b9): raw site-year means \u00b1 SE (descriptive only)",
    col.names = c("Site-year", "n", "Raw mean", "Raw SE")
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

## 3) Treatment block: mowing means (model + raw) ------------------------

emm_wbm_ny <- emmeans(
  weed_glmm_ny,
  ~ weed_trt,
  type = "response"
)

emm_trt_wbm_ny_df <- tidy_emm(
  emm_wbm_ny,
  trt_var    = "weed_trt",
  ref_levels = mow_levels
) |>
  dplyr::mutate(
    weed_trt   = factor(weed_trt, levels = mow_levels),
    model_mean = response
  ) |>
  dplyr::select(weed_trt, model_mean, SE, ci_low, ci_high)

cld_wbm_ny <- multcomp::cld(
  emm_wbm_ny,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE
) |>
  as_tibble() |>
  dplyr::mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    trt_CLD  = stringr::str_trim(.group)
  ) |>
  dplyr::select(weed_trt, trt_CLD)

raw_trt_wbm_ny <- weed_biomass_ny |>
  dplyr::group_by(weed_trt) |>
  dplyr::summarise(
    raw_mean = mean(weed_biomass_kg_ha, na.rm = TRUE),
    .groups  = "drop"
  ) |>
  dplyr::mutate(weed_trt = factor(weed_trt, levels = mow_levels))

trt_summary_wbm_ny <- emm_trt_wbm_ny_df |>
  dplyr::left_join(cld_wbm_ny,     by = "weed_trt") |>
  dplyr::left_join(raw_trt_wbm_ny, by = "weed_trt") |>
  dplyr::mutate(
    model_mean = round(model_mean, 1),
    SE         = round(SE, 1),
    ci_low     = round(ci_low, 1),
    ci_high    = round(ci_high, 1),
    raw_mean   = round(raw_mean, 1),
    raw_CLD    = trt_CLD
  ) |>
  dplyr::arrange(weed_trt)

readr::write_csv(
  trt_summary_wbm_ny,
  file.path(tab_dir_wbm_ny, "tab_ny-total-wbm_treatment_means_CLD.csv")
)

trt_summary_wbm_ny |>
  kable(
    caption   = "New York weed biomass (kg ha\u207b\u00b9): mowing-treatment means with CLDs",
    col.names = c(
      "Treatment", "Model mean", "SE",
      "Lower CI", "Upper CI",
      "Model CLD", "Raw mean", "Raw CLD"
    )
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

## 3b) Weediness block: ambient vs surrogate means (model + raw) --------

emm_wbm_weed_ny <- emmeans(
  weed_glmm_ny,
  ~ weeds,
  type = "response"
)

emm_weeds_wbm_ny_df <- tidy_emm(
  emm_wbm_weed_ny,
  trt_var    = "weeds",
  ref_levels = c("Ambient weeds", "Surrogate weeds")
) |>
  dplyr::mutate(
    weeds      = factor(weeds, levels = c("Ambient weeds", "Surrogate weeds")),
    model_mean = response
  ) |>
  dplyr::select(weeds, model_mean, SE, ci_low, ci_high)

cld_wbm_weed_ny <- multcomp::cld(
  emm_wbm_weed_ny,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE
) |>
  as_tibble() |>
  dplyr::mutate(
    weeds     = factor(weeds, levels = c("Ambient weeds", "Surrogate weeds")),
    weeds_CLD = stringr::str_trim(.group)
  ) |>
  dplyr::select(weeds, weeds_CLD)

raw_weeds_wbm_ny <- weed_biomass_ny |>
  dplyr::group_by(weeds) |>
  dplyr::summarise(
    raw_mean = mean(weed_biomass_kg_ha, na.rm = TRUE),
    .groups  = "drop"
  ) |>
  dplyr::mutate(
    weeds = factor(weeds, levels = c("Ambient weeds", "Surrogate weeds"))
  )

weediness_summary_wbm_ny <- emm_weeds_wbm_ny_df |>
  dplyr::left_join(cld_wbm_weed_ny,  by = "weeds") |>
  dplyr::left_join(raw_weeds_wbm_ny, by = "weeds") |>
  dplyr::mutate(
    model_mean = round(model_mean, 1),
    SE         = round(SE, 1),
    ci_low     = round(ci_low, 1),
    ci_high    = round(ci_high, 1),
    raw_mean   = round(raw_mean, 1)
  ) |>
  dplyr::arrange(weeds)

readr::write_csv(
  weediness_summary_wbm_ny,
  file.path(tab_dir_wbm_ny, "tab_ny-total-wbm_weediness_means_CLD.csv")
)

weediness_summary_wbm_ny |>
  kable(
    caption   = "New York weed biomass (kg ha\u207b\u00b9): weediness (ambient vs surrogate) means with CLDs",
    col.names = c(
      "Weediness", "Model mean", "SE",
      "Lower CI", "Upper CI",
      "Model CLD", "Raw mean"
    )
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

## 4) Interaction block: mowing means within weediness -------------------

emm_int_wbm_ny <- emmeans(
  weed_glmm_ny,
  ~ weed_trt | weeds,
  type = "response"
)

emm_int_wbm_ny_df <- tidy_emm(
  emm_int_wbm_ny,
  trt_var    = "weed_trt",
  ref_levels = mow_levels
) |>
  dplyr::mutate(
    weeds      = factor(weeds, levels = c("Ambient weeds", "Surrogate weeds")),
    weed_trt   = factor(weed_trt, levels = mow_levels),
    model_mean = response
  ) |>
  dplyr::select(weeds, weed_trt, model_mean, SE, ci_low, ci_high)

cld_int_wbm_ny <- multcomp::cld(
  emm_int_wbm_ny,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE
) |>
  as_tibble() |>
  dplyr::mutate(
    weeds    = factor(weeds, levels = c("Ambient weeds", "Surrogate weeds")),
    weed_trt = factor(weed_trt, levels = mow_levels),
    int_CLD  = stringr::str_trim(.group)
  ) |>
  dplyr::select(weeds, weed_trt, int_CLD)

raw_int_wbm_ny <- weed_biomass_ny |>
  dplyr::group_by(weeds, weed_trt) |>
  dplyr::summarise(
    raw_mean = mean(weed_biomass_kg_ha, na.rm = TRUE),
    .groups  = "drop"
  ) |>
  dplyr::mutate(
    weeds    = factor(weeds, levels = c("Ambient weeds", "Surrogate weeds")),
    weed_trt = factor(weed_trt, levels = mow_levels)
  )

int_summary_wbm_ny <- emm_int_wbm_ny_df |>
  dplyr::left_join(cld_int_wbm_ny, by = c("weeds", "weed_trt")) |>
  dplyr::left_join(raw_int_wbm_ny, by = c("weeds", "weed_trt")) |>
  dplyr::mutate(
    model_mean = round(model_mean, 1),
    SE         = round(SE, 1),
    ci_low     = round(ci_low, 1),
    ci_high    = round(ci_high, 1),
    raw_mean   = round(raw_mean, 1),
    raw_CLD    = int_CLD
  ) |>
  dplyr::arrange(weeds, weed_trt)

readr::write_csv(
  int_summary_wbm_ny,
  file.path(tab_dir_wbm_ny, "tab_ny-total-wbm_weeds_treatment_means_CLD.csv")
)

int_summary_wbm_ny |>
  kable(
    caption   = "New York weed biomass (kg ha\u207b\u00b9): mowing-treatment means within weediness with CLDs",
    col.names = c(
      "Weediness", "Treatment",
      "Model mean", "SE", "Lower CI", "Upper CI",
      "Model CLD", "Raw mean", "Raw CLD"
    )
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

## 5) Model-info row for global response summary -------------------------

fixed_effects_ny  <- "weed_trt * weeds"
random_effects_ny <- "(1 | site_year) + (1 | site_year:block)"

final_aic_ny <- round(AIC(weed_glmm_ny), 2)
final_disp_ny <- tryCatch(
  format(stats::formula(weed_glmm_ny$modelInfo$dispformula)),
  error = function(e) NA_character_
)

model_info_wbm_ny <- tibble::tibble(
  response_label    = "Total weed biomass (kg ha^-1), New York model-predicted means*",
  family_structure  = "Tweedie (log link)",
  fixed_effects     = fixed_effects_ny,
  random_effects    = random_effects_ny,
  dispersion_model  = final_disp_ny,
  AIC_selected      = final_aic_ny,
  pdHess            = isTRUE(weed_glmm_ny$sdr$pdHess)
)

readr::write_csv(
  model_info_wbm_ny,
  file.path(tab_dir_wbm_ny, "tab_ny-total-wbm_model-info.csv")
)

## 6) OPTIONAL: combine into one New York workbook -----------------------

if (requireNamespace("writexl", quietly = TRUE)) {
  wbm_total_tables_ny <- list(
    Anova_pvals             = pvals_wbm_ny,
    SiteYear_RAW_means      = raw_loc_wbm_ny,
    Treatment_means_CLD     = trt_summary_wbm_ny,
    Weediness_means_CLD     = weediness_summary_wbm_ny,
    Weeds_x_Treatment_means = int_summary_wbm_ny,
    Model_info              = model_info_wbm_ny
  )

  writexl::write_xlsx(
    wbm_total_tables_ny,
    path = file.path(tab_dir_wbm_ny, "NewYork_total-weed-biomass_all-tables.xlsx")
  )
} else {
  message("Package 'writexl' not installed; skipping New York Excel export.")
}

```

```{r}
## New York only (Cornell + Farm Hub): summary tables for total weed biomass (kg ha^-1)

# Assumes available:
#   weed_glmm_ny
#   ny_best_n
#   primary_model_name_ny
#   AIC_add_ny, AIC_int_ny, deltaAIC_ny
#   p_int_ny, interaction_class_ny
#   weed_biomass_ny, mow_levels
#   tidy_emm()

# 0) Directory for NY weed-biomass tables -------------------------------

tab_dir_wbm_ny <- here("analysis", "tables", "weed-biomass", "NY-only", "total")
dir.create(tab_dir_wbm_ny, showWarnings = FALSE, recursive = TRUE)


## 1) Global ANOVA / LRT summary ----------------------------------------

anova_wbm_ny <- car::Anova(weed_glmm_ny, type = 3)

anova_wbm_ny_df <- anova_wbm_ny |>
  as.data.frame() |>
  tibble::rownames_to_column("Effect")

p_trt_ny   <- anova_wbm_ny_df$`Pr(>Chisq)`[anova_wbm_ny_df$Effect == "weed_trt"]
p_weeds_ny <- anova_wbm_ny_df$`Pr(>Chisq)`[anova_wbm_ny_df$Effect == "weeds"]
p_site_ny  <- anova_wbm_ny_df$`Pr(>Chisq)`[anova_wbm_ny_df$Effect == "site_year"]

pvals_wbm_ny <- tibble::tibble(
  Effect = c(
    "Mowing treatment (weed_trt)",
    "Weediness (weeds: ambient vs surrogate)",
    "Site-year"
  ),
  p_raw = c(p_trt_ny, p_weeds_ny, p_site_ny)
) |>
  dplyr::mutate(
    `P-value` = dplyr::case_when(
      p_raw < 0.001 ~ "<0.001",
      p_raw < 0.01  ~ "<0.01",
      TRUE          ~ sprintf("%.3f", p_raw)
    )
  ) |>
  dplyr::select(Effect, `P-value`)

readr::write_csv(
  pvals_wbm_ny,
  file.path(tab_dir_wbm_ny, "tab_ny-total-wbm_Anova_pvals.csv")
)

pvals_wbm_ny |>
  kable(
    caption   = "New York (Cornell + Farm Hub) weed biomass (kg ha\u207b\u00b9): Type-III Wald tests (GLMM)",
    col.names = c("Effect", "P-value")
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


## 1b) Likelihood-ratio test: additive vs interaction -------------------

lrt_table_wbm_ny <- tibble::tibble(
  Test  = "LRT (additive vs interaction: weed_trt * weeds)",
  p_raw = p_int_ny
) |>
  dplyr::mutate(
    `P-value` = dplyr::case_when(
      p_raw < 0.001 ~ "<0.001",
      p_raw < 0.01  ~ "<0.01",
      TRUE          ~ sprintf("%.3f", p_raw)
    )
  ) |>
  dplyr::select(Test, `P-value`)

readr::write_csv(
  lrt_table_wbm_ny,
  file.path(tab_dir_wbm_ny, "tab_ny-total-wbm_LRT_add-vs-int.csv")
)

lrt_table_wbm_ny |>
  kable(
    caption   = "New York weed biomass (kg ha\u207b\u00b9): LRT comparing additive vs interaction (weed_trt \u00d7 weeds)",
    col.names = c("Test", "P-value")
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


## 2) Site-year block: means (model + raw) ------------------------------

emm_loc_wbm_ny <- emmeans(
  weed_glmm_ny,
  ~ site_year,
  type = "response"
)

emm_loc_wbm_ny_df <- as_tibble(emm_loc_wbm_ny) |>
  dplyr::mutate(
    site_year  = as.factor(site_year),
    model_mean = response   # kg ha^-1
  ) |>
  dplyr::select(site_year, model_mean)

cld_loc_wbm_ny <- multcomp::cld(
  emm_loc_wbm_ny,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE
) |>
  as_tibble() |>
  dplyr::mutate(
    site_year = as.factor(site_year),
    loc_CLD   = stringr::str_trim(.group)
  ) |>
  dplyr::select(site_year, loc_CLD)

raw_loc_wbm_ny <- weed_biomass_ny |>
  dplyr::group_by(site_year) |>
  dplyr::summarise(
    raw_mean = mean(weed_biomass_kg_ha, na.rm = TRUE),
    .groups  = "drop"
  ) |>
  dplyr::mutate(site_year = as.factor(site_year))

loc_summary_wbm_ny <- emm_loc_wbm_ny_df |>
  dplyr::left_join(cld_loc_wbm_ny, by = "site_year") |>
  dplyr::left_join(raw_loc_wbm_ny, by = "site_year") |>
  dplyr::mutate(
    model_mean = round(model_mean, 1),
    raw_mean   = round(raw_mean, 1),
    raw_CLD    = loc_CLD
  ) |>
  dplyr::arrange(site_year)

readr::write_csv(
  loc_summary_wbm_ny,
  file.path(tab_dir_wbm_ny, "tab_ny-total-wbm_site-year_means_CLD.csv")
)

loc_summary_wbm_ny |>
  kable(
    caption   = "New York weed biomass (kg ha\u207b\u00b9): site-year means with CLDs",
    col.names = c("Site-year", "Model mean", "Model CLD", "Raw mean", "Raw CLD")
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


## 3) Mowing-treatment block: means (model + raw) -----------------------

emm_wbm_ny <- emmeans(
  weed_glmm_ny,
  ~ weed_trt,
  type = "response"
)

emm_trt_wbm_ny_df <- tidy_emm(
  emm_wbm_ny,
  trt_var    = "weed_trt",
  ref_levels = mow_levels
)

mean_col_ny <- if ("response" %in% names(emm_trt_wbm_ny_df)) {
  "response"
} else {
  "emmean"
}

emm_trt_wbm_ny_df <- emm_trt_wbm_ny_df |>
  dplyr::mutate(
    weed_trt   = factor(weed_trt, levels = mow_levels),
    model_mean = .data[[mean_col_ny]]
  ) |>
  dplyr::select(weed_trt, model_mean, SE, ci_low, ci_high)

cld_wbm_ny <- multcomp::cld(
  emm_wbm_ny,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE
) |>
  as_tibble() |>
  dplyr::mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    trt_CLD  = stringr::str_trim(.group)
  ) |>
  dplyr::select(weed_trt, trt_CLD)

raw_trt_wbm_ny <- weed_biomass_ny |>
  dplyr::group_by(weed_trt) |>
  dplyr::summarise(
    raw_mean = mean(weed_biomass_kg_ha, na.rm = TRUE),
    .groups  = "drop"
  ) |>
  dplyr::mutate(weed_trt = factor(weed_trt, levels = mow_levels))

trt_summary_wbm_ny <- emm_trt_wbm_ny_df |>
  dplyr::left_join(cld_wbm_ny,     by = "weed_trt") |>
  dplyr::left_join(raw_trt_wbm_ny, by = "weed_trt") |>
  dplyr::mutate(
    model_mean = round(model_mean, 1),
    SE         = round(SE, 1),
    ci_low     = round(ci_low, 1),
    ci_high    = round(ci_high, 1),
    raw_mean   = round(raw_mean, 1),
    raw_CLD    = trt_CLD
  ) |>
  dplyr::arrange(weed_trt)

readr::write_csv(
  trt_summary_wbm_ny,
  file.path(tab_dir_wbm_ny, "tab_ny-total-wbm_mowing_means_CLD.csv")
)

trt_summary_wbm_ny |>
  kable(
    caption   = "New York weed biomass (kg ha\u207b\u00b9): mowing-treatment means with CLDs",
    col.names = c(
      "Treatment", "Model mean", "SE",
      "Lower CI", "Upper CI",
      "Model CLD", "Raw mean", "Raw CLD"
    )
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


## 3b) Weediness block: ambient vs surrogate means ----------------------

emm_weeds_ny <- emmeans(
  weed_glmm_ny,
  ~ weeds,
  type = "response"
)

emm_weeds_ny_df <- tidy_emm(emm_weeds_ny)

mean_col_weeds_ny <- if ("response" %in% names(emm_weeds_ny_df)) {
  "response"
} else {
  "emmean"
}

emm_weeds_ny_df <- emm_weeds_ny_df |>
  dplyr::mutate(
    weeds      = factor(weeds),
    model_mean = .data[[mean_col_weeds_ny]]
  ) |>
  dplyr::select(weeds, model_mean, SE, ci_low, ci_high)

cld_weeds_ny <- multcomp::cld(
  emm_weeds_ny,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE
) |>
  as_tibble() |>
  dplyr::mutate(
    weeds     = factor(weeds),
    weeds_CLD = stringr::str_trim(.group)
  ) |>
  dplyr::select(weeds, weeds_CLD)

raw_weeds_ny <- weed_biomass_ny |>
  dplyr::group_by(weeds) |>
  dplyr::summarise(
    raw_mean = mean(weed_biomass_kg_ha, na.rm = TRUE),
    .groups  = "drop"
  ) |>
  dplyr::mutate(weeds = factor(weeds))

weeds_summary_wbm_ny <- emm_weeds_ny_df |>
  dplyr::left_join(cld_weeds_ny, by = "weeds") |>
  dplyr::left_join(raw_weeds_ny, by = "weeds") |>
  dplyr::mutate(
    model_mean = round(model_mean, 1),
    SE         = round(SE, 1),
    ci_low     = round(ci_low, 1),
    ci_high    = round(ci_high, 1),
    raw_mean   = round(raw_mean, 1),
    raw_CLD    = weeds_CLD
  ) |>
  dplyr::arrange(weeds)

readr::write_csv(
  weeds_summary_wbm_ny,
  file.path(tab_dir_wbm_ny, "tab_ny-total-wbm_weediness_means_CLD.csv")
)

weeds_summary_wbm_ny |>
  kable(
    caption   = "New York weed biomass (kg ha\u207b\u00b9): weediness (ambient vs surrogate) means with CLDs",
    col.names = c(
      "Weediness", "Model mean", "SE",
      "Lower CI", "Upper CI",
      "Model CLD", "Raw mean", "Raw CLD"
    )
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


## 4) OPTIONAL: site-year × mowing means (only if interaction selected) -

int_summary_wbm_ny <- NULL

if (interaction_class_ny == "interaction") {

  emm_sy_wbm_ny <- emmeans(
    weed_glmm_ny,
    ~ weed_trt | site_year,
    type = "response"
  )

  emm_sy_wbm_ny_df <- as_tibble(emm_sy_wbm_ny) |>
    dplyr::mutate(
      weed_trt   = factor(weed_trt, levels = mow_levels),
      site_year  = as.factor(site_year),
      model_mean = response   # kg ha^-1
    ) |>
    dplyr::select(site_year, weed_trt, model_mean)

  cld_sy_wbm_ny <- multcomp::cld(
    emm_sy_wbm_ny,
    adjust   = "none",
    Letters  = letters,
    sort     = TRUE,
    reversed = TRUE
  ) |>
    as_tibble() |>
    dplyr::mutate(
      weed_trt  = factor(weed_trt, levels = mow_levels),
      site_year = as.factor(site_year),
      int_CLD   = stringr::str_trim(.group)
    ) |>
    dplyr::select(site_year, weed_trt, int_CLD)

  raw_sy_wbm_ny <- weed_biomass_ny |>
    dplyr::group_by(site_year, weed_trt) |>
    dplyr::summarise(
      raw_mean = mean(weed_biomass_kg_ha, na.rm = TRUE),
      .groups  = "drop"
    ) |>
    dplyr::mutate(
      site_year = as.factor(site_year),
      weed_trt  = factor(weed_trt, levels = mow_levels)
    )

  int_summary_wbm_ny <- emm_sy_wbm_ny_df |>
    dplyr::left_join(cld_sy_wbm_ny, by = c("site_year", "weed_trt")) |>
    dplyr::left_join(raw_sy_wbm_ny, by = c("site_year", "weed_trt")) |>
    dplyr::mutate(
      model_mean = round(model_mean, 1),
      raw_mean   = round(raw_mean, 1),
      raw_CLD    = int_CLD
    ) |>
    dplyr::arrange(site_year, weed_trt)

  readr::write_csv(
    int_summary_wbm_ny,
    file.path(tab_dir_wbm_ny, "tab_ny-total-wbm_site-year_mowing_means_CLD.csv")
  )

  int_summary_wbm_ny |>
    kable(
      caption   = "New York weed biomass (kg ha\u207b\u00b9): site-year \u00d7 mowing-treatment means with CLDs (interaction model)",
      col.names = c(
        "Site-year", "Treatment",
        "Model mean", "Raw mean", "Raw CLD"
      )
    ) |>
    kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))
}


## 5) Model-info row for NY global response summary ---------------------

model_info_wbm_ny <- tibble::tibble(
  response_label    = "Weed biomass (kg ha^-1), New York only, model-predicted means*",
  family_structure  = ny_best_n,
  fixed_effects     = primary_model_name_ny,
  random_effects    = "(1 | site_year) + (1 | site_year:block) + (1 | site_year:block:weed_trt)",
  AIC_additive      = round(AIC_add_ny, 2),
  AIC_interaction   = round(AIC_int_ny, 2),
  deltaAIC_add_int  = round(deltaAIC_ny, 2),
  LRT_p_int_raw     = p_int_ny,
  LRT_p_int_label   = dplyr::case_when(
    p_int_ny < 0.001 ~ "<0.001",
    p_int_ny < 0.01  ~ "<0.01",
    TRUE             ~ sprintf("%.3f", p_int_ny)
  ),
  interaction_class = interaction_class_ny
)

readr::write_csv(
  model_info_wbm_ny,
  file.path(tab_dir_wbm_ny, "tab_ny-total-wbm_model-info.csv")
)


## 6) OPTIONAL: combine into one Excel workbook -------------------------

if (requireNamespace("writexl", quietly = TRUE)) {
  wbm_total_tables_ny <- list(
    Anova_pvals         = pvals_wbm_ny,
    LRT_add_vs_int      = lrt_table_wbm_ny,
    SiteYear_means_CLD  = loc_summary_wbm_ny,
    Mowing_means_CLD    = trt_summary_wbm_ny,
    Weediness_means_CLD = weeds_summary_wbm_ny,
    Model_info          = model_info_wbm_ny
  )

  # Only add the interaction sheet if it exists (i.e., interaction model selected)
  if (!is.null(int_summary_wbm_ny)) {
    wbm_total_tables_ny$SiteYear_Mowing_CLD <- int_summary_wbm_ny
  }

  writexl::write_xlsx(
    wbm_total_tables_ny,
    path = file.path(tab_dir_wbm_ny, "NY_total-weed-biomass_all-tables.xlsx")
  )
}


```

## In-row weed biomass
###Ecobean
```{r}
## Ecobean IN-ROW weed biomass (kg ha^-1): summary tables ---------------

library(writexl)  # if not already loaded

# 0) Directory for Ecobean in-row tables --------------------------------
tab_dir_wbm_eco_in <- here("analysis", "tables", "weed-biomass", "Ecobean", "inrow")
dir.create(tab_dir_wbm_eco_in, showWarnings = FALSE, recursive = TRUE)


## 1) ANOVA p-value summary (mowing, weeds, site-year) -------------------

anova_wbm_eco_in <- car::Anova(wbm_inrow_glmm_eco, type = 3)

anova_wbm_eco_in_df <- anova_wbm_eco_in |>
  as.data.frame() |>
  tibble::rownames_to_column("Effect")

p_site_in <- anova_wbm_eco_in_df$`Pr(>Chisq)`[anova_wbm_eco_in_df$Effect == "site_year"]
p_trt_in  <- anova_wbm_eco_in_df$`Pr(>Chisq)`[anova_wbm_eco_in_df$Effect == "weed_trt"]
p_weed_in <- anova_wbm_eco_in_df$`Pr(>Chisq)`[anova_wbm_eco_in_df$Effect == "weeds"]

pvals_wbm_eco_in <- tibble::tibble(
  Effect = c(
    "Site-year",
    "Mowing treatment (weed_trt)",
    "Weediness (ambient vs surrogate)"
  ),
  p_raw = c(p_site_in, p_trt_in, p_weed_in)
) |>
  dplyr::mutate(
    `P-value` = dplyr::case_when(
      p_raw < 0.001 ~ "<0.001",
      p_raw < 0.01  ~ "<0.01",
      TRUE          ~ sprintf("%.3f", p_raw)
    )
  ) |>
  dplyr::select(Effect, `P-value`)

# Save ANOVA p-values
readr::write_csv(
  pvals_wbm_eco_in,
  file.path(tab_dir_wbm_eco_in, "tab_eco-inrow-wbm_Anova_pvals.csv")
)

pvals_wbm_eco_in |>
  kable(
    caption   = "Ecobean IN-ROW weed biomass (kg ha\u207b\u00b9): ANOVA p-values",
    col.names = c("Effect", "P-value")
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


## 1b) LRT: additive vs interaction (weed_trt × weeds) -------------------

lrt_table_wbm_eco_in <- tibble::tibble(
  Test  = "LRT (additive vs interaction: weed_trt * weeds)",
  p_raw = lrt_eco_in$`Pr(>Chisq)`[2]
) |>
  dplyr::mutate(
    `P-value` = dplyr::case_when(
      p_raw < 0.001 ~ "<0.001",
      p_raw < 0.01  ~ "<0.01",
      TRUE          ~ sprintf("%.3f", p_raw)
    )
  ) |>
  dplyr::select(Test, `P-value`)

readr::write_csv(
  lrt_table_wbm_eco_in,
  file.path(tab_dir_wbm_eco_in, "tab_eco-inrow-wbm_LRT_add-vs-int.csv")
)

lrt_table_wbm_eco_in |>
  kable(
    caption   = "Ecobean IN-ROW weed biomass: LRT comparing additive vs interaction (weed_trt × weeds)",
    col.names = c("Test", "P-value")
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


## 2) Site-year means (model + raw) -------------------------------------

emm_loc_in_eco <- emmeans(
  wbm_inrow_glmm_eco,
  ~ site_year,
  type = "response"
)

emm_loc_in_eco_df <- tidy_emm(emm_loc_in_eco) |>
  dplyr::mutate(
    site_year  = as.factor(site_year),
    model_mean = .data$response
  ) |>
  dplyr::select(site_year, model_mean, SE, ci_low, ci_high)

cld_loc_in_eco <- multcomp::cld(
  emm_loc_in_eco,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE
) |>
  as_tibble() |>
  dplyr::mutate(
    site_year = as.factor(site_year),
    loc_CLD   = stringr::str_trim(.group)
  ) |>
  dplyr::select(site_year, loc_CLD)

raw_loc_in_eco <- eco_inrow |>
  dplyr::group_by(site_year) |>
  dplyr::summarise(
    raw_mean = mean(inrow_weed_biomass_kg_ha, na.rm = TRUE),
    .groups  = "drop"
  ) |>
  dplyr::mutate(site_year = as.factor(site_year))

loc_summary_wbm_eco_in <- emm_loc_in_eco_df |>
  dplyr::left_join(cld_loc_in_eco, by = "site_year") |>
  dplyr::left_join(raw_loc_in_eco, by = "site_year") |>
  dplyr::mutate(
    model_mean = round(model_mean, 1),
    SE         = round(SE, 1),
    ci_low     = round(ci_low, 1),
    ci_high    = round(ci_high, 1),
    raw_mean   = round(raw_mean, 1)
  ) |>
  dplyr::arrange(site_year)

readr::write_csv(
  loc_summary_wbm_eco_in,
  file.path(tab_dir_wbm_eco_in, "tab_eco-inrow-wbm_site-year_means_CLD.csv")
)

loc_summary_wbm_eco_in |>
  kable(
    caption   = "Ecobean IN-ROW weed biomass (kg ha\u207b\u00b9): site-year means with CLDs",
    col.names = c(
      "Site-year", "Model mean", "SE",
      "Lower CI", "Upper CI",
      "Model CLD", "Raw mean"
    )
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


## 3) Mowing means (model + raw) with CLDs ------------------------------

emm_trt_in_eco <- emmeans(
  wbm_inrow_glmm_eco,
  ~ weed_trt,
  type = "response"
)

emm_trt_in_eco_df <- tidy_emm(
  emm_trt_in_eco,
  trt_var    = "weed_trt",
  ref_levels = mow_levels
) |>
  dplyr::mutate(
    weed_trt   = factor(weed_trt, levels = mow_levels),
    model_mean = .data$response
  ) |>
  dplyr::select(weed_trt, model_mean, SE, ci_low, ci_high)

cld_trt_in_eco <- multcomp::cld(
  emm_trt_in_eco,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE
) |>
  as_tibble() |>
  dplyr::mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    trt_CLD  = stringr::str_trim(.group)
  ) |>
  dplyr::select(weed_trt, trt_CLD)

raw_trt_in_eco <- eco_inrow |>
  dplyr::group_by(weed_trt) |>
  dplyr::summarise(
    raw_mean = mean(inrow_weed_biomass_kg_ha, na.rm = TRUE),
    .groups  = "drop"
  ) |>
  dplyr::mutate(weed_trt = factor(weed_trt, levels = mow_levels))

trt_summary_wbm_eco_in <- emm_trt_in_eco_df |>
  dplyr::left_join(cld_trt_in_eco, by = "weed_trt") |>
  dplyr::left_join(raw_trt_in_eco, by = "weed_trt") |>
  dplyr::mutate(
    model_mean = round(model_mean, 1),
    SE         = round(SE, 1),
    ci_low     = round(ci_low, 1),
    ci_high    = round(ci_high, 1),
    raw_mean   = round(raw_mean, 1),
    raw_CLD    = trt_CLD
  ) |>
  dplyr::arrange(weed_trt)

readr::write_csv(
  trt_summary_wbm_eco_in,
  file.path(tab_dir_wbm_eco_in, "tab_eco-inrow-wbm_mowing_means_CLD.csv")
)

trt_summary_wbm_eco_in |>
  kable(
    caption   = "Ecobean IN-ROW weed biomass (kg ha\u207b\u00b9): mowing-treatment means with CLDs",
    col.names = c(
      "Treatment", "Model mean", "SE",
      "Lower CI", "Upper CI",
      "Model CLD", "Raw mean", "Raw CLD"
    )
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


## 4) Weediness means (ambient vs surrogate) ----------------------------

emm_weeds_in_eco <- emmeans(
  wbm_inrow_glmm_eco,
  ~ weeds,
  type = "response"
)

emm_weeds_in_eco_df <- tidy_emm(emm_weeds_in_eco) |>
  dplyr::mutate(
    weeds      = factor(weeds),
    model_mean = .data$response
  ) |>
  dplyr::select(weeds, model_mean, SE, ci_low, ci_high)

cld_weeds_in_eco <- multcomp::cld(
  emm_weeds_in_eco,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE
) |>
  as_tibble() |>
  dplyr::mutate(
    weeds     = factor(weeds),
    weeds_CLD = stringr::str_trim(.group)
  ) |>
  dplyr::select(weeds, weeds_CLD)

raw_weeds_in_eco <- eco_inrow |>
  dplyr::group_by(weeds) |>
  dplyr::summarise(
    raw_mean = mean(inrow_weed_biomass_kg_ha, na.rm = TRUE),
    .groups  = "drop"
  )

weeds_summary_wbm_eco_in <- emm_weeds_in_eco_df |>
  dplyr::left_join(cld_weeds_in_eco, by = "weeds") |>
  dplyr::left_join(raw_weeds_in_eco, by = "weeds") |>
  dplyr::mutate(
    model_mean = round(model_mean, 1),
    SE         = round(SE, 1),
    ci_low     = round(ci_low, 1),
    ci_high    = round(ci_high, 1),
    raw_mean   = round(raw_mean, 1)
  ) |>
  dplyr::arrange(weeds)

readr::write_csv(
  weeds_summary_wbm_eco_in,
  file.path(tab_dir_wbm_eco_in, "tab_eco-inrow-wbm_weediness_means_CLD.csv")
)

weeds_summary_wbm_eco_in |>
  kable(
    caption   = "Ecobean IN-ROW weed biomass (kg ha\u207b\u00b9): ambient vs surrogate means with CLDs",
    col.names = c(
      "Weediness", "Model mean", "SE",
      "Lower CI", "Upper CI",
      "Model CLD", "Raw mean"
    )
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


## 5) Model-info row -----------------------------------------------------

model_info_wbm_eco_in <- tibble::tibble(
  response_label    = "Ecobean IN-ROW weed biomass (kg ha^-1), model-predicted means*",
  family_structure  = eco_in_best_n,
  fixed_effects     = primary_model_name_eco_in,
  random_effects    = "(1 | site_year) + (1 | site_year:block) + (1 | site_year:block:weed_trt)",
  AIC_additive      = round(AIC_add_eco_in, 2),
  AIC_interaction   = round(AIC_int_eco_in, 2),
  deltaAIC_add_int  = round(deltaAIC_eco_in, 2),
  LRT_p_int_raw     = p_int_eco_in,
  LRT_p_int_label   = dplyr::case_when(
    p_int_eco_in < 0.001 ~ "<0.001",
    p_int_eco_in < 0.01  ~ "<0.01",
    TRUE                 ~ sprintf("%.3f", p_int_eco_in)
  ),
  interaction_class = interaction_class_eco_in
)

readr::write_csv(
  model_info_wbm_eco_in,
  file.path(tab_dir_wbm_eco_in, "tab_eco-inrow-wbm_model-info.csv")
)


## 6) Bundle all Ecobean IN-ROW tables into one workbook ----------------

wbm_eco_in_tables <- list(
  Anova_pvals         = pvals_wbm_eco_in,
  LRT_add_vs_int      = lrt_table_wbm_eco_in,
  SiteYear_means_CLD  = loc_summary_wbm_eco_in,
  Mowing_means_CLD    = trt_summary_wbm_eco_in,
  Weediness_means_CLD = weeds_summary_wbm_eco_in,
  Model_info          = model_info_wbm_eco_in
)

writexl::write_xlsx(
  wbm_eco_in_tables,
  path = file.path(tab_dir_wbm_eco_in, "Ecobean_inrow_weed-biomass_all-tables.xlsx")
)


```
### New York Only
```{r}
## NY-only IN-ROW weed biomass (kg ha^-1): summary tables ---------------

library(writexl)  # if not already loaded

# 0) Directory for NY-only in-row tables --------------------------------
tab_dir_wbm_ny_in <- here("analysis", "tables", "weed-biomass", "NY-only", "inrow")
dir.create(tab_dir_wbm_ny_in, showWarnings = FALSE, recursive = TRUE)


## 1) ANOVA p-value summary (mowing, weeds, site-year) -------------------

anova_wbm_ny_in <- car::Anova(wbm_inrow_glmm_ny, type = 3)

anova_wbm_ny_in_df <- anova_wbm_ny_in |>
  as.data.frame() |>
  tibble::rownames_to_column("Effect")

p_site_in_ny <- anova_wbm_ny_in_df$`Pr(>Chisq)`[anova_wbm_ny_in_df$Effect == "site_year"]
p_trt_in_ny  <- anova_wbm_ny_in_df$`Pr(>Chisq)`[anova_wbm_ny_in_df$Effect == "weed_trt"]
p_weed_in_ny <- anova_wbm_ny_in_df$`Pr(>Chisq)`[anova_wbm_ny_in_df$Effect == "weeds"]

pvals_wbm_ny_in <- tibble::tibble(
  Effect = c(
    "Site-year",
    "Mowing treatment (weed_trt)",
    "Weediness (ambient vs surrogate)"
  ),
  p_raw = c(p_site_in_ny, p_trt_in_ny, p_weed_in_ny)
) |>
  dplyr::mutate(
    `P-value` = dplyr::case_when(
      p_raw < 0.001 ~ "<0.001",
      p_raw < 0.01  ~ "<0.01",
      TRUE          ~ sprintf("%.3f", p_raw)
    )
  ) |>
  dplyr::select(Effect, `P-value`)

readr::write_csv(
  pvals_wbm_ny_in,
  file.path(tab_dir_wbm_ny_in, "tab_ny-inrow-wbm_Anova_pvals.csv")
)

pvals_wbm_ny_in |>
  kable(
    caption   = "NY-only IN-ROW weed biomass (kg ha\u207b\u00b9): ANOVA p-values",
    col.names = c("Effect", "P-value")
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


## 1b) LRT: additive vs interaction (weed_trt × weeds) -------------------

lrt_table_wbm_ny_in <- tibble::tibble(
  Test  = "LRT (additive vs interaction: weed_trt * weeds)",
  p_raw = lrt_ny_in$`Pr(>Chisq)`[2]
) |>
  dplyr::mutate(
    `P-value` = dplyr::case_when(
      p_raw < 0.001 ~ "<0.001",
      p_raw < 0.01  ~ "<0.01",
      TRUE          ~ sprintf("%.3f", p_raw)
    )
  ) |>
  dplyr::select(Test, `P-value`)

readr::write_csv(
  lrt_table_wbm_ny_in,
  file.path(tab_dir_wbm_ny_in, "tab_ny-inrow-wbm_LRT_add-vs-int.csv")
)

lrt_table_wbm_ny_in |>
  kable(
    caption   = "NY-only IN-ROW weed biomass: LRT comparing additive vs interaction (weed_trt × weeds)",
    col.names = c("Test", "P-value")
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


## 2) Site-year means (model + raw) -------------------------------------

emm_loc_in_ny <- emmeans(
  wbm_inrow_glmm_ny,
  ~ site_year,
  type = "response"
)

emm_loc_in_ny_df <- tidy_emm(emm_loc_in_ny) |>
  dplyr::mutate(
    site_year  = as.factor(site_year),
    model_mean = .data$response
  ) |>
  dplyr::select(site_year, model_mean, SE, ci_low, ci_high)

cld_loc_in_ny <- multcomp::cld(
  emm_loc_in_ny,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE
) |>
  as_tibble() |>
  dplyr::mutate(
    site_year = as.factor(site_year),
    loc_CLD   = stringr::str_trim(.group)
  ) |>
  dplyr::select(site_year, loc_CLD)

raw_loc_in_ny <- ny_inrow |>
  dplyr::group_by(site_year) |>
  dplyr::summarise(
    raw_mean = mean(inrow_weed_biomass_kg_ha, na.rm = TRUE),
    .groups  = "drop"
  ) |>
  dplyr::mutate(site_year = as.factor(site_year))

loc_summary_wbm_ny_in <- emm_loc_in_ny_df |>
  dplyr::left_join(cld_loc_in_ny, by = "site_year") |>
  dplyr::left_join(raw_loc_in_ny, by = "site_year") |>
  dplyr::mutate(
    model_mean = round(model_mean, 1),
    SE         = round(SE, 1),
    ci_low     = round(ci_low, 1),
    ci_high    = round(ci_high, 1),
    raw_mean   = round(raw_mean, 1)
  ) |>
  dplyr::arrange(site_year)

readr::write_csv(
  loc_summary_wbm_ny_in,
  file.path(tab_dir_wbm_ny_in, "tab_ny-inrow-wbm_site-year_means_CLD.csv")
)

loc_summary_wbm_ny_in |>
  kable(
    caption   = "NY-only IN-ROW weed biomass (kg ha\u207b\u00b9): site-year means with CLDs",
    col.names = c(
      "Site-year", "Model mean", "SE",
      "Lower CI", "Upper CI",
      "Model CLD", "Raw mean"
    )
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


## 3) Mowing means (model + raw) with CLDs ------------------------------

emm_trt_in_ny <- emmeans(
  wbm_inrow_glmm_ny,
  ~ weed_trt,
  type = "response"
)

emm_trt_in_ny_df <- tidy_emm(
  emm_trt_in_ny,
  trt_var    = "weed_trt",
  ref_levels = mow_levels
) |>
  dplyr::mutate(
    weed_trt   = factor(weed_trt, levels = mow_levels),
    model_mean = .data$response
  ) |>
  dplyr::select(weed_trt, model_mean, SE, ci_low, ci_high)

cld_trt_in_ny <- multcomp::cld(
  emm_trt_in_ny,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE
) |>
  as_tibble() |>
  dplyr::mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    trt_CLD  = stringr::str_trim(.group)
  ) |>
  dplyr::select(weed_trt, trt_CLD)

raw_trt_in_ny <- ny_inrow |>
  dplyr::group_by(weed_trt) |>
  dplyr::summarise(
    raw_mean = mean(inrow_weed_biomass_kg_ha, na.rm = TRUE),
    .groups  = "drop"
  ) |>
  dplyr::mutate(weed_trt = factor(weed_trt, levels = mow_levels))

trt_summary_wbm_ny_in <- emm_trt_in_ny_df |>
  dplyr::left_join(cld_trt_in_ny, by = "weed_trt") |>
  dplyr::left_join(raw_trt_in_ny, by = "weed_trt") |>
  dplyr::mutate(
    model_mean = round(model_mean, 1),
    SE         = round(SE, 1),
    ci_low     = round(ci_low, 1),
    ci_high    = round(ci_high, 1),
    raw_mean   = round(raw_mean, 1),
    raw_CLD    = trt_CLD
  ) |>
  dplyr::arrange(weed_trt)

readr::write_csv(
  trt_summary_wbm_ny_in,
  file.path(tab_dir_wbm_ny_in, "tab_ny-inrow-wbm_mowing_means_CLD.csv")
)

trt_summary_wbm_ny_in |>
  kable(
    caption   = "NY-only IN-ROW weed biomass (kg ha\u207b\u00b9): mowing-treatment means with CLDs",
    col.names = c(
      "Treatment", "Model mean", "SE",
      "Lower CI", "Upper CI",
      "Model CLD", "Raw mean", "Raw CLD"
    )
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


## 4) Weediness means (ambient vs surrogate) ----------------------------

emm_weeds_in_ny <- emmeans(
  wbm_inrow_glmm_ny,
  ~ weeds,
  type = "response"
)

emm_weeds_in_ny_df <- tidy_emm(emm_weeds_in_ny) |>
  dplyr::mutate(
    weeds      = factor(weeds),
    model_mean = .data$response
  ) |>
  dplyr::select(weeds, model_mean, SE, ci_low, ci_high)

cld_weeds_in_ny <- multcomp::cld(
  emm_weeds_in_ny,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE
) |>
  as_tibble() |>
  dplyr::mutate(
    weeds     = factor(weeds),
    weeds_CLD = stringr::str_trim(.group)
  ) |>
  dplyr::select(weeds, weeds_CLD)

raw_weeds_in_ny <- ny_inrow |>
  dplyr::group_by(weeds) |>
  dplyr::summarise(
    raw_mean = mean(inrow_weed_biomass_kg_ha, na.rm = TRUE),
    .groups  = "drop"
  )

weeds_summary_wbm_ny_in <- emm_weeds_in_ny_df |>
  dplyr::left_join(cld_weeds_in_ny, by = "weeds") |>
  dplyr::left_join(raw_weeds_in_ny, by = "weeds") |>
  dplyr::mutate(
    model_mean = round(model_mean, 1),
    SE         = round(SE, 1),
    ci_low     = round(ci_low, 1),
    ci_high    = round(ci_high, 1),
    raw_mean   = round(raw_mean, 1)
  ) |>
  dplyr::arrange(weeds)

readr::write_csv(
  weeds_summary_wbm_ny_in,
  file.path(tab_dir_wbm_ny_in, "tab_ny-inrow-wbm_weediness_means_CLD.csv")
)

weeds_summary_wbm_ny_in |>
  kable(
    caption   = "NY-only IN-ROW weed biomass (kg ha\u207b\u00b9): ambient vs surrogate means with CLDs",
    col.names = c(
      "Weediness", "Model mean", "SE",
      "Lower CI", "Upper CI",
      "Model CLD", "Raw mean"
    )
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


## 5) Model-info row -----------------------------------------------------

model_info_wbm_ny_in <- tibble::tibble(
  response_label    = "NY-only IN-ROW weed biomass (kg ha^-1), model-predicted means*",
  family_structure  = ny_in_best_n,
  fixed_effects     = primary_model_name_ny_in,
  random_effects    = "(1 | site_year) + (1 | site_year:block) + (1 | site_year:block:weed_trt)",
  AIC_additive      = round(AIC_add_ny_in, 2),
  AIC_interaction   = round(AIC_int_ny_in, 2),
  deltaAIC_add_int  = round(deltaAIC_ny_in, 2),
  LRT_p_int_raw     = p_int_ny_in,
  LRT_p_int_label   = dplyr::case_when(
    p_int_ny_in < 0.001 ~ "<0.001",
    p_int_ny_in < 0.01  ~ "<0.01",
    TRUE                ~ sprintf("%.3f", p_int_ny_in)
  ),
  interaction_class = interaction_class_ny_in
)

readr::write_csv(
  model_info_wbm_ny_in,
  file.path(tab_dir_wbm_ny_in, "tab_ny-inrow-wbm_model-info.csv")
)


## 6) Bundle all NY-only IN-ROW tables into one workbook ----------------

wbm_ny_in_tables <- list(
  Anova_pvals         = pvals_wbm_ny_in,
  LRT_add_vs_int      = lrt_table_wbm_ny_in,
  SiteYear_means_CLD  = loc_summary_wbm_ny_in,
  Mowing_means_CLD    = trt_summary_wbm_ny_in,
  Weediness_means_CLD = weeds_summary_wbm_ny_in,
  Model_info          = model_info_wbm_ny_in
)

writexl::write_xlsx(
  wbm_ny_in_tables,
  path = file.path(tab_dir_wbm_ny_in, "NY-only_inrow_weed-biomass_all-tables.xlsx")
)


```
## Inter-row weed biomass
###Ecobean
```{r}
## Ecobean INTER-ROW weed biomass (kg ha^-1): summary tables ------------

library(writexl)  # if not already loaded

# 0) Directory for Ecobean inter-row tables -----------------------------
tab_dir_wbm_eco_inter <- here("analysis", "tables", "weed-biomass", "Ecobean", "interrow")
dir.create(tab_dir_wbm_eco_inter, showWarnings = FALSE, recursive = TRUE)


## 1) ANOVA p-value summary (mowing, weeds, site-year) -------------------

anova_wbm_eco_inter <- car::Anova(wbm_inter_glmm_eco, type = 3)

anova_wbm_eco_inter_df <- anova_wbm_eco_inter |>
  as.data.frame() |>
  tibble::rownames_to_column("Effect")

p_site_eco_inter  <- anova_wbm_eco_inter_df$`Pr(>Chisq)`[anova_wbm_eco_inter_df$Effect == "site_year"]
p_trt_eco_inter   <- anova_wbm_eco_inter_df$`Pr(>Chisq)`[anova_wbm_eco_inter_df$Effect == "weed_trt"]
p_weed_eco_inter  <- anova_wbm_eco_inter_df$`Pr(>Chisq)`[anova_wbm_eco_inter_df$Effect == "weeds"]

pvals_wbm_eco_inter <- tibble::tibble(
  Effect = c(
    "Site-year",
    "Mowing treatment (weed_trt)",
    "Weediness (ambient vs surrogate)"
  ),
  p_raw = c(p_site_eco_inter, p_trt_eco_inter, p_weed_eco_inter)
) |>
  dplyr::mutate(
    `P-value` = dplyr::case_when(
      p_raw < 0.001 ~ "<0.001",
      p_raw < 0.01  ~ "<0.01",
      TRUE          ~ sprintf("%.3f", p_raw)
    )
  ) |>
  dplyr::select(Effect, `P-value`)

readr::write_csv(
  pvals_wbm_eco_inter,
  file.path(tab_dir_wbm_eco_inter, "tab_eco-interrow-wbm_Anova_pvals.csv")
)

pvals_wbm_eco_inter |>
  kable(
    caption   = "Ecobean INTER-ROW weed biomass (kg ha\u207b\u00b9): ANOVA p-values",
    col.names = c("Effect", "P-value")
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


## 1b) LRT: additive vs interaction (weed_trt × weeds) -------------------

lrt_table_wbm_eco_inter <- tibble::tibble(
  Test  = "LRT (additive vs interaction: weed_trt * weeds)",
  p_raw = lrt_eco_inter$`Pr(>Chisq)`[2]
) |>
  dplyr::mutate(
    `P-value` = dplyr::case_when(
      p_raw < 0.001 ~ "<0.001",
      p_raw < 0.01  ~ "<0.01",
      TRUE          ~ sprintf("%.3f", p_raw)
    )
  ) |>
  dplyr::select(Test, `P-value`)

readr::write_csv(
  lrt_table_wbm_eco_inter,
  file.path(tab_dir_wbm_eco_inter, "tab_eco-interrow-wbm_LRT_add-vs-int.csv")
)

lrt_table_wbm_eco_inter |>
  kable(
    caption   = "Ecobean INTER-ROW weed biomass: LRT comparing additive vs interaction (weed_trt × weeds)",
    col.names = c("Test", "P-value")
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


## 2) Site-year means (model + raw) -------------------------------------

emm_loc_eco_inter <- emmeans(
  wbm_inter_glmm_eco,
  ~ site_year,
  type = "response"
)

emm_loc_eco_inter_df <- tidy_emm(emm_loc_eco_inter) |>
  dplyr::mutate(
    site_year  = as.factor(site_year),
    model_mean = .data$response   # kg ha^-1
  ) |>
  dplyr::select(site_year, model_mean, SE, ci_low, ci_high)

cld_loc_eco_inter <- multcomp::cld(
  emm_loc_eco_inter,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE
) |>
  as_tibble() |>
  dplyr::mutate(
    site_year = as.factor(site_year),
    loc_CLD   = stringr::str_trim(.group)
  ) |>
  dplyr::select(site_year, loc_CLD)

raw_loc_eco_inter <- eco_inter |>
  dplyr::group_by(site_year) |>
  dplyr::summarise(
    raw_mean = mean(interrow_weed_biomass_kg_ha, na.rm = TRUE),
    .groups  = "drop"
  ) |>
  dplyr::mutate(site_year = as.factor(site_year))

loc_summary_wbm_eco_inter <- emm_loc_eco_inter_df |>
  dplyr::left_join(cld_loc_eco_inter, by = "site_year") |>
  dplyr::left_join(raw_loc_eco_inter, by = "site_year") |>
  dplyr::mutate(
    model_mean = round(model_mean, 1),
    SE         = round(SE, 1),
    ci_low     = round(ci_low, 1),
    ci_high    = round(ci_high, 1),
    raw_mean   = round(raw_mean, 1)
  ) |>
  dplyr::arrange(site_year)

readr::write_csv(
  loc_summary_wbm_eco_inter,
  file.path(tab_dir_wbm_eco_inter, "tab_eco-interrow-wbm_site-year_means_CLD.csv")
)

loc_summary_wbm_eco_inter |>
  kable(
    caption   = "Ecobean INTER-ROW weed biomass (kg ha\u207b\u00b9): site-year means with CLDs",
    col.names = c(
      "Site-year", "Model mean", "SE",
      "Lower CI", "Upper CI",
      "Model CLD", "Raw mean"
    )
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


## 3) Mowing means (model + raw) with CLDs ------------------------------

emm_trt_eco_inter <- emmeans(
  wbm_inter_glmm_eco,
  ~ weed_trt,
  type = "response"
)

emm_trt_eco_inter_df <- tidy_emm(
  emm_trt_eco_inter,
  trt_var    = "weed_trt",
  ref_levels = mow_levels
) |>
  dplyr::mutate(
    weed_trt   = factor(weed_trt, levels = mow_levels),
    model_mean = .data$response
  ) |>
  dplyr::select(weed_trt, model_mean, SE, ci_low, ci_high)

cld_trt_eco_inter <- multcomp::cld(
  emm_trt_eco_inter,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE
) |>
  as_tibble() |>
  dplyr::mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    trt_CLD  = stringr::str_trim(.group)
  ) |>
  dplyr::select(weed_trt, trt_CLD)

raw_trt_eco_inter <- eco_inter |>
  dplyr::group_by(weed_trt) |>
  dplyr::summarise(
    raw_mean = mean(interrow_weed_biomass_kg_ha, na.rm = TRUE),
    .groups  = "drop"
  ) |>
  dplyr::mutate(weed_trt = factor(weed_trt, levels = mow_levels))

trt_summary_wbm_eco_inter <- emm_trt_eco_inter_df |>
  dplyr::left_join(cld_trt_eco_inter, by = "weed_trt") |>
  dplyr::left_join(raw_trt_eco_inter, by = "weed_trt") |>
  dplyr::mutate(
    model_mean = round(model_mean, 1),
    SE         = round(SE, 1),
    ci_low     = round(ci_low, 1),
    ci_high    = round(ci_high, 1),
    raw_mean   = round(raw_mean, 1),
    raw_CLD    = trt_CLD
  ) |>
  dplyr::arrange(weed_trt)

readr::write_csv(
  trt_summary_wbm_eco_inter,
  file.path(tab_dir_wbm_eco_inter, "tab_eco-interrow-wbm_mowing_means_CLD.csv")
)

trt_summary_wbm_eco_inter |>
  kable(
    caption   = "Ecobean INTER-ROW weed biomass (kg ha\u207b\u00b9): mowing-treatment means with CLDs",
    col.names = c(
      "Treatment", "Model mean", "SE",
      "Lower CI", "Upper CI",
      "Model CLD", "Raw mean", "Raw CLD"
    )
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


## 4) Weediness means (ambient vs surrogate) ----------------------------

emm_weeds_eco_inter <- emmeans(
  wbm_inter_glmm_eco,
  ~ weeds,
  type = "response"
)

emm_weeds_eco_inter_df <- tidy_emm(emm_weeds_eco_inter) |>
  dplyr::mutate(
    weeds      = factor(weeds),
    model_mean = .data$response
  ) |>
  dplyr::select(weeds, model_mean, SE, ci_low, ci_high)

cld_weeds_eco_inter <- multcomp::cld(
  emm_weeds_eco_inter,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE
) |>
  as_tibble() |>
  dplyr::mutate(
    weeds     = factor(weeds),
    weeds_CLD = stringr::str_trim(.group)
  ) |>
  dplyr::select(weeds, weeds_CLD)

raw_weeds_eco_inter <- eco_inter |>
  dplyr::group_by(weeds) |>
  dplyr::summarise(
    raw_mean = mean(interrow_weed_biomass_kg_ha, na.rm = TRUE),
    .groups  = "drop"
  )

weeds_summary_wbm_eco_inter <- emm_weeds_eco_inter_df |>
  dplyr::left_join(cld_weeds_eco_inter, by = "weeds") |>
  dplyr::left_join(raw_weeds_eco_inter, by = "weeds") |>
  dplyr::mutate(
    model_mean = round(model_mean, 1),
    SE         = round(SE, 1),
    ci_low     = round(ci_low, 1),
    ci_high    = round(ci_high, 1),
    raw_mean   = round(raw_mean, 1)
  ) |>
  dplyr::arrange(weeds)

readr::write_csv(
  weeds_summary_wbm_eco_inter,
  file.path(tab_dir_wbm_eco_inter, "tab_eco-interrow-wbm_weediness_means_CLD.csv")
)

weeds_summary_wbm_eco_inter |>
  kable(
    caption   = "Ecobean INTER-ROW weed biomass (kg ha\u207b\u00b9): ambient vs surrogate means with CLDs",
    col.names = c(
      "Weediness", "Model mean", "SE",
      "Lower CI", "Upper CI",
      "Model CLD", "Raw mean"
    )
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


## 5) Model-info row -----------------------------------------------------

model_info_wbm_eco_inter <- tibble::tibble(
  response_label    = "Ecobean INTER-ROW weed biomass (kg ha^-1), model-predicted means*",
  family_structure  = eco_inter_best_n,
  fixed_effects     = primary_model_name_eco_inter,
  random_effects    = "(1 | site_year) + (1 | site_year:block) + (1 | site_year:block:weed_trt)",
  AIC_additive      = round(AIC_add_eco_inter, 2),
  AIC_interaction   = round(AIC_int_eco_inter, 2),
  deltaAIC_add_int  = round(deltaAIC_eco_inter, 2),
  LRT_p_int_raw     = p_int_eco_inter,
  LRT_p_int_label   = dplyr::case_when(
    p_int_eco_inter < 0.001 ~ "<0.001",
    p_int_eco_inter < 0.01  ~ "<0.01",
    TRUE                    ~ sprintf("%.3f", p_int_eco_inter)
  ),
  interaction_class = interaction_class_eco_inter
)

readr::write_csv(
  model_info_wbm_eco_inter,
  file.path(tab_dir_wbm_eco_inter, "tab_eco-interrow-wbm_model-info.csv")
)


## 6) Bundle all Ecobean INTER-ROW tables into one workbook --------------

wbm_eco_inter_tables <- list(
  Anova_pvals         = pvals_wbm_eco_inter,
  LRT_add_vs_int      = lrt_table_wbm_eco_inter,
  SiteYear_means_CLD  = loc_summary_wbm_eco_inter,
  Mowing_means_CLD    = trt_summary_wbm_eco_inter,
  Weediness_means_CLD = weeds_summary_wbm_eco_inter,
  Model_info          = model_info_wbm_eco_inter
)

writexl::write_xlsx(
  wbm_eco_inter_tables,
  path = file.path(tab_dir_wbm_eco_inter, "Ecobean_interrow_weed-biomass_all-tables.xlsx")
)

```

### New York Only
```{r}
## NY-only INTER-ROW weed biomass (kg ha^-1): summary tables + export ---

library(writexl)

# Directory for NY-only INTER-ROW tables --------------------------------
tab_dir_wbm_ny_inter <- here(
  "analysis", "tables", "weed-biomass", "NY-only", "interrow"
)
dir.create(tab_dir_wbm_ny_inter, showWarnings = FALSE, recursive = TRUE)

# 1) ANOVA p-value summary ----------------------------------------------

anova_ny_inter <- car::Anova(wbm_inter_glmm_ny, type = 3)

anova_ny_inter_df <- as.data.frame(anova_ny_inter) |>
  tibble::rownames_to_column("Effect")

p_site  <- anova_ny_inter_df$`Pr(>Chisq)`[anova_ny_inter_df$Effect == "site_year"]
p_trt   <- anova_ny_inter_df$`Pr(>Chisq)`[anova_ny_inter_df$Effect == "weed_trt"]
p_weeds <- anova_ny_inter_df$`Pr(>Chisq)`[anova_ny_inter_df$Effect == "weeds"]

pvals_ny_inter <- tibble::tibble(
  Effect = c(
    "Site-year (site_year)",
    "Mowing treatment (weed_trt)",
    "Weediness (weeds)"
  ),
  p_raw = c(p_site, p_trt, p_weeds)
) |>
  dplyr::mutate(
    `P-value` = dplyr::case_when(
      is.na(p_raw)   ~ NA_character_,
      p_raw < 0.001  ~ "<0.001",
      p_raw < 0.01   ~ "<0.01",
      TRUE           ~ sprintf("%.3f", p_raw)
    )
  ) |>
  dplyr::select(Effect, `P-value`)

# Save ANOVA p-value summary
readr::write_csv(
  pvals_ny_inter,
  file.path(tab_dir_wbm_ny_inter, "tab_ny-interrow-wbm_Anova_pvals.csv")
)

pvals_ny_inter |>
  kable(
    caption   = "NY-only INTER-ROW weed biomass (kg ha\u207b\u00b9): Type-III Wald tests",
    col.names = c("Effect", "P-value")
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


# 2) LRT: additive vs interaction (weed_trt × weeds) --------------------

lrt_table_ny_inter <- tibble::tibble(
  Test  = "LRT (additive vs interaction: weed_trt × weeds)",
  p_raw = p_int_ny_inter
) |>
  dplyr::mutate(
    `P-value` = dplyr::case_when(
      is.na(p_raw)   ~ NA_character_,
      p_raw < 0.001  ~ "<0.001",
      p_raw < 0.01   ~ "<0.01",
      TRUE           ~ sprintf("%.3f", p_raw)
    )
  ) |>
  dplyr::select(Test, `P-value`)

readr::write_csv(
  lrt_table_ny_inter,
  file.path(tab_dir_wbm_ny_inter, "tab_ny-interrow-wbm_LRT_add-vs-int.csv")
)

lrt_table_ny_inter |>
  kable(
    caption   = "NY-only INTER-ROW weed biomass: likelihood-ratio test (additive vs interaction)",
    col.names = c("Test", "P-value")
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


# 3) Site-year means (model + raw + CLDs) -------------------------------

emm_loc_ny_inter <- emmeans(
  wbm_inter_glmm_ny,
  ~ site_year,
  type = "response"
)

emm_loc_ny_inter_tmp <- as_tibble(emm_loc_ny_inter)

emm_loc_ny_inter_df <- emm_loc_ny_inter_tmp |>
  dplyr::mutate(
    site_year  = as.factor(site_year),
    model_mean = if ("response" %in% names(emm_loc_ny_inter_tmp))
      response else emmean
  ) |>
  dplyr::select(site_year, model_mean)

cld_loc_ny_inter <- multcomp::cld(
  emm_loc_ny_inter,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE
) |>
  as_tibble() |>
  dplyr::mutate(
    site_year = as.factor(site_year),
    loc_CLD   = stringr::str_trim(.group)
  ) |>
  dplyr::select(site_year, loc_CLD)

# Raw means from ny_inter subset (non-missing interrow biomass)
raw_loc_ny_inter <- ny_inter |>
  dplyr::group_by(site_year) |>
  dplyr::summarise(
    raw_mean = mean(interrow_weed_biomass_kg_ha, na.rm = TRUE),
    .groups  = "drop"
  ) |>
  dplyr::mutate(site_year = as.factor(site_year))

loc_summary_ny_inter <- emm_loc_ny_inter_df |>
  dplyr::left_join(cld_loc_ny_inter, by = "site_year") |>
  dplyr::left_join(raw_loc_ny_inter, by = "site_year") |>
  dplyr::mutate(
    model_mean = round(model_mean, 1),
    raw_mean   = round(raw_mean, 1),
    raw_CLD    = loc_CLD
  ) |>
  dplyr::arrange(site_year)

readr::write_csv(
  loc_summary_ny_inter,
  file.path(tab_dir_wbm_ny_inter,
            "tab_ny-interrow-wbm_site-year_means_CLD.csv")
)

loc_summary_ny_inter |>
  kable(
    caption   = "NY-only INTER-ROW weed biomass (kg ha\u207b\u00b9): site-year means with CLDs",
    col.names = c("Site-year", "Model mean", "Model CLD", "Raw mean", "Raw CLD")
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


# 4) Mowing-treatment means (model + raw + CLDs) ------------------------

emm_trt_ny_inter <- emmeans(
  wbm_inter_glmm_ny,
  ~ weed_trt,
  type = "response"
)

emm_trt_ny_inter_tmp <- tidy_emm(
  emm_trt_ny_inter,
  trt_var    = "weed_trt",
  ref_levels = mow_levels
)

emm_trt_ny_inter_df <- emm_trt_ny_inter_tmp |>
  dplyr::mutate(
    weed_trt   = factor(weed_trt, levels = mow_levels),
    model_mean = if ("response" %in% names(emm_trt_ny_inter_tmp))
      response else emmean
  ) |>
  dplyr::select(weed_trt, model_mean, SE, ci_low, ci_high)

cld_trt_ny_inter <- multcomp::cld(
  emm_trt_ny_inter,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE
) |>
  as_tibble() |>
  dplyr::mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    trt_CLD  = stringr::str_trim(.group)
  ) |>
  dplyr::select(weed_trt, trt_CLD)

raw_trt_ny_inter <- ny_inter |>
  dplyr::group_by(weed_trt) |>
  dplyr::summarise(
    raw_mean = mean(interrow_weed_biomass_kg_ha, na.rm = TRUE),
    .groups  = "drop"
  ) |>
  dplyr::mutate(weed_trt = factor(weed_trt, levels = mow_levels))

trt_summary_ny_inter <- emm_trt_ny_inter_df |>
  dplyr::left_join(cld_trt_ny_inter, by = "weed_trt") |>
  dplyr::left_join(raw_trt_ny_inter, by = "weed_trt") |>
  dplyr::mutate(
    model_mean = round(model_mean, 1),
    SE         = round(SE, 1),
    ci_low     = round(ci_low, 1),
    ci_high    = round(ci_high, 1),
    raw_mean   = round(raw_mean, 1),
    raw_CLD    = trt_CLD
  ) |>
  dplyr::arrange(weed_trt)

readr::write_csv(
  trt_summary_ny_inter,
  file.path(tab_dir_wbm_ny_inter,
            "tab_ny-interrow-wbm_treatment_means_CLD.csv")
)

trt_summary_ny_inter |>
  kable(
    caption   = "NY-only INTER-ROW weed biomass (kg ha\u207b\u00b9): mowing-treatment means with CLDs",
    col.names = c(
      "Treatment", "Model mean", "SE",
      "Lower CI", "Upper CI",
      "Model CLD", "Raw mean", "Raw CLD"
    )
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


# 5) Weediness means (ambient vs surrogate; model + raw + CLDs) --------

emm_weeds_ny_inter <- emmeans(
  wbm_inter_glmm_ny,
  ~ weeds,
  type = "response"
)

emm_weeds_ny_inter_tmp <- tidy_emm(
  emm_weeds_ny_inter,
  trt_var    = "weeds",
  ref_levels = levels(ny_inter$weeds)
)

emm_weeds_ny_inter_df <- emm_weeds_ny_inter_tmp |>
  dplyr::mutate(
    weeds      = factor(weeds, levels = levels(ny_inter$weeds)),
    model_mean = if ("response" %in% names(emm_weeds_ny_inter_tmp))
      response else emmean
  ) |>
  dplyr::select(weeds, model_mean, SE, ci_low, ci_high)

cld_weeds_ny_inter <- multcomp::cld(
  emm_weeds_ny_inter,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE
) |>
  as_tibble() |>
  dplyr::mutate(
    weeds     = factor(weeds, levels = levels(ny_inter$weeds)),
    weeds_CLD = stringr::str_trim(.group)
  ) |>
  dplyr::select(weeds, weeds_CLD)

raw_weeds_ny_inter <- ny_inter |>
  dplyr::group_by(weeds) |>
  dplyr::summarise(
    raw_mean = mean(interrow_weed_biomass_kg_ha, na.rm = TRUE),
    .groups  = "drop"
  ) |>
  dplyr::mutate(weeds = factor(weeds, levels = levels(ny_inter$weeds)))

weeds_summary_ny_inter <- emm_weeds_ny_inter_df |>
  dplyr::left_join(cld_weeds_ny_inter, by = "weeds") |>
  dplyr::left_join(raw_weeds_ny_inter, by = "weeds") |>
  dplyr::mutate(
    model_mean = round(model_mean, 1),
    SE         = round(SE, 1),
    ci_low     = round(ci_low, 1),
    ci_high    = round(ci_high, 1),
    raw_mean   = round(raw_mean, 1),
    raw_CLD    = weeds_CLD
  ) |>
  dplyr::arrange(weeds)

readr::write_csv(
  weeds_summary_ny_inter,
  file.path(tab_dir_wbm_ny_inter,
            "tab_ny-interrow-wbm_weediness_means_CLD.csv")
)

weeds_summary_ny_inter |>
  kable(
    caption   = "NY-only INTER-ROW weed biomass (kg ha\u207b\u00b9): weediness (ambient vs surrogate) means with CLDs",
    col.names = c(
      "Weediness", "Model mean", "SE",
      "Lower CI", "Upper CI",
      "Model CLD", "Raw mean", "Raw CLD"
    )
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))


# 6) Model-info row -----------------------------------------------------

model_info_ny_inter <- tibble::tibble(
  response_label    = "INTER-ROW weed biomass (kg ha^-1), NY-only, model-predicted means*",
  family_structure  = ny_inter_best_n,
  fixed_effects     = primary_model_name_ny_inter,
  random_effects    = "(1 | site_year) + (1 | site_year:block) + (1 | site_year:block:weed_trt)",
  AIC_additive      = round(AIC_add_ny_inter, 2),
  AIC_interaction   = round(AIC_int_ny_inter, 2),
  deltaAIC_add_int  = round(deltaAIC_ny_inter, 2),
  LRT_p_int_raw     = p_int_ny_inter,
  LRT_p_int_label   = dplyr::case_when(
    is.na(p_int_ny_inter)   ~ NA_character_,
    p_int_ny_inter < 0.001  ~ "<0.001",
    p_int_ny_inter < 0.01   ~ "<0.01",
    TRUE                    ~ sprintf("%.3f", p_int_ny_inter)
  ),
  interaction_class = interaction_class_ny_inter
)

readr::write_csv(
  model_info_ny_inter,
  file.path(tab_dir_wbm_ny_inter,
            "tab_ny-interrow-wbm_model-info.csv")
)


# 7) OPTIONAL: bundle all NY-only INTER-ROW tables in one workbook ------

wbm_inter_tables_ny <- list(
  Anova_pvals          = pvals_ny_inter,
  LRT_add_vs_int       = lrt_table_ny_inter,
  SiteYear_means_CLD   = loc_summary_ny_inter,
  Mowing_means_CLD     = trt_summary_ny_inter,
  Weediness_means_CLD  = weeds_summary_ny_inter,
  Model_info           = model_info_ny_inter
)

writexl::write_xlsx(
  wbm_inter_tables_ny,
  path = file.path(tab_dir_wbm_ny_inter,
                   "NY-only_INTER-ROW_weed-biomass_all-tables.xlsx")
)

```

# Figures
##Total weed biomass
### Ecobean
```{r}
## Ecobean TOTAL weed biomass (kg ha^-1): figures -----------------------

kg_ha_to_lb_ac <- 0.892179

fig_dir_eco_total <- here("analysis", "figs", "weed-biomass", "Ecobean", "total")
dir.create(fig_dir_eco_total, showWarnings = FALSE, recursive = TRUE)

# 1) MODEL-PREDICTED MEANS (kg ha^-1) ----------------------------------

# uses trt_summary_wbm_eco / emm_trt_wbm_eco_df / cld_wbm_eco from the summary chunk

plot_df_wbm_eco_model <- emm_trt_wbm_eco_df |>
  dplyr::mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    mean     = model_mean,
    ymin     = pmax(mean - SE, 0),
    ymax     = mean + SE
  ) |>
  dplyr::left_join(cld_wbm_eco, by = "weed_trt")

fig_eco_wbm_total_model <- ggplot(
  plot_df_wbm_eco_model,
  aes(x = weed_trt, y = mean, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.14) +
  geom_text(
    aes(y = ymax * 1.08, label = trt_CLD),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = expression(Weed~biomass~"(kg"~ha^{-1}*")"),
    title   = "Total weed biomass by mowing ",
    #caption = "Bars show GLMM-predicted marginal means (kg ha\u207b\u00b9) \u00b1 SE; letters denote Fisher\u2019s LSD groups (\u03b1 = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_eco_wbm_total_model

ggsave(
  filename = file.path(fig_dir_eco_total, "fig_eco_weed_biomass_total_model_kg_ha.png"),
  plot     = fig_eco_wbm_total_model,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)


# 1a) MODEL-PREDICTED MEANS (lb ac^-1) – EXTENSION FIGURE --------------

plot_df_wbm_eco_model_lb <- plot_df_wbm_eco_model |>
  dplyr::mutate(
    mean_lb = mean * kg_ha_to_lb_ac,
    SE_lb   = SE   * kg_ha_to_lb_ac,
    ymin_lb = pmax(mean_lb - SE_lb, 0),
    ymax_lb = mean_lb + SE_lb
  )

fig_eco_wbm_total_model_lb <- ggplot(
  plot_df_wbm_eco_model_lb,
  aes(x = weed_trt, y = mean_lb, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin_lb, ymax = ymax_lb), width = 0.14) +
  geom_text(
    aes(y = ymax_lb * 1.08, label = trt_CLD),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = expression(Weed~biomass~"(lb"~ac^{-1}*")"),
    title   = "Total weed biomass by mowing ",
    #caption = "Bars show GLMM-predicted marginal means (lb ac\u207b\u00b9) \u00b1 SE; letters denote Fisher\u2019s LSD groups (\u03b1 = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_eco_wbm_total_model_lb

ggsave(
  filename = file.path(fig_dir_eco_total, "fig_eco_weed_biomass_total_model_lb_ac.png"),
  plot     = fig_eco_wbm_total_model_lb,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)


# 2) RAW MEANS (kg ha^-1) ----------------------------------------------

raw_eco_wbm_fig <- weed_biomass_eco |>
  dplyr::group_by(weed_trt) |>
  dplyr::summarise(
    n    = dplyr::n(),
    mean = mean(weed_biomass_kg_ha, na.rm = TRUE),
    sd   = stats::sd(weed_biomass_kg_ha, na.rm = TRUE),
    se   = sd / sqrt(n),
    .groups = "drop"
  ) |>
  dplyr::mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    ymin     = pmax(mean - se, 0),
    ymax     = mean + se
  ) |>
  dplyr::left_join(cld_wbm_eco, by = "weed_trt")

fig_eco_wbm_total_raw_kg <- ggplot(
  raw_eco_wbm_fig,
  aes(x = weed_trt, y = mean, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.14) +
  geom_text(
    aes(y = ymax * 1.08, label = trt_CLD),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = expression(Weed~biomass~"(kg"~ha^{-1}*")"),
    title   = "Total weed biomass by mowing )",
    caption = "Bars show raw treatment means (kg ha\u207b\u00b9) \u00b1 SE; letters reuse GLMM-based Fisher\u2019s LSD groups (\u03b1 = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_eco_wbm_total_raw_kg

ggsave(
  filename = file.path(fig_dir_eco_total, "fig_eco_weed_biomass_total_raw_kg_ha.png"),
  plot     = fig_eco_wbm_total_raw_kg,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)


# 3) RAW MEANS (lb ac^-1) ----------------------------------------------

raw_eco_wbm_fig_lb <- raw_eco_wbm_fig |>
  dplyr::mutate(
    mean_lb = mean * kg_ha_to_lb_ac,
    se_lb   = se   * kg_ha_to_lb_ac,
    ymin_lb = pmax(mean_lb - se_lb, 0),
    ymax_lb = mean_lb + se_lb
  )

fig_eco_wbm_total_raw_lb <- ggplot(
  raw_eco_wbm_fig_lb,
  aes(x = weed_trt, y = mean_lb, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin_lb, ymax = ymax_lb), width = 0.14) +
  geom_text(
    aes(y = ymax_lb * 1.08, label = trt_CLD),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = expression(Weed~biomass~"(lb"~ac^{-1}*")"),
    title   = "Total weed biomass by mowing",
    caption = "Bars show raw treatment means (lb ac\u207b\u00b9) \u00b1 SE; letters reuse GLMM-based Fisher\u2019s LSD groups (\u03b1 = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_eco_wbm_total_raw_lb

ggsave(
  filename = file.path(fig_dir_eco_total, "fig_eco_weed_biomass_total_raw_lb_ac.png"),
  plot     = fig_eco_wbm_total_raw_lb,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)

```

```{r}
## Ecobean: total weed biomass figures ----------------------------------

# Conversion constant
kg_ha_to_lb_ac <- 0.892179 # 1 kg ha^-1 ≈ 0.892 lb ac^-1

# 0) Directory for Ecobean total weed-biomass figures -------------------
fig_dir_eco_total <- here("analysis", "figs", "weed-biomass", "Ecobean", "total")
dir.create(fig_dir_eco_total, showWarnings = FALSE, recursive = TRUE)

## A) MODEL-PREDICTED means (kg ha^-1) ----------------------------------

# 1) Model-based emmeans by mowing treatment
emm_wbm_eco <- emmeans(
  weed_glmm_eco,
  ~ weed_trt,
  type = "response"   # back-transform (kg ha^-1)
)

# 2) Tidy emmeans and SE-based error bars
emm_wbm_eco_df <- as_tibble(emm_wbm_eco) |>
  mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    mean     = response,
    ymin     = pmax(mean - SE, 0),
    ymax     = mean + SE
  )

# 3) Model-based CLDs for treatment main effect (Fisher's LSD)
cld_wbm_eco <- multcomp::cld(
  emm_wbm_eco,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE   # so "a" = highest biomass group(s)
) |>
  as_tibble() |>
  mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    .group   = stringr::str_trim(.group)
  ) |>
  select(weed_trt, .group)

# 4) Join model-predicted means + CLDs
plot_df_wbm_eco_model <- emm_wbm_eco_df |>
  left_join(cld_wbm_eco, by = "weed_trt")

# 5) Plot: Ecobean model-predicted means (kg ha^-1)
fig_eco_wbm_total_model <- ggplot(
  plot_df_wbm_eco_model,
  aes(x = weed_trt, y = mean, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.14) +
  geom_text(
    aes(y = ymax * 1.08, label = .group),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = expression(Weed~biomass~"(kg"~ha^{-1}*")"),
    title   = "Ecobean: total weed biomass by mowing treatment",
    caption = "Bars show GLMM-predicted marginal means (kg ha^{-1}) ± SE; letters denote Fisher’s LSD groups (α = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_eco_wbm_total_model  # print in Rmd

# 6) Save model figure
ggsave(
  filename = file.path(fig_dir_eco_total, "fig_eco_weed_biomass_total_model_kg_ha.png"),
  plot     = fig_eco_wbm_total_model,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)


## B) RAW means (kg ha^-1) ----------------------------------------------

# 1) Raw treatment means + SE
raw_eco_wbm <- weed_biomass_eco |>
  group_by(weed_trt) |>
  summarise(
    n        = n(),
    mean     = mean(weed_biomass_kg_ha, na.rm = TRUE),
    sd       = sd(weed_biomass_kg_ha, na.rm = TRUE),
    se       = sd / sqrt(n),
    .groups  = "drop"
  ) |>
  mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    ymin     = pmax(mean - se, 0),
    ymax     = mean + se
  )

# 2) Attach the SAME model-based CLDs for consistency
plot_df_wbm_eco_raw <- raw_eco_wbm |>
  left_join(cld_wbm_eco, by = "weed_trt")

# 3) Plot: Ecobean raw means (kg ha^-1)
fig_eco_wbm_total_raw_kg <- ggplot(
  plot_df_wbm_eco_raw,
  aes(x = weed_trt, y = mean, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.14) +
  geom_text(
    aes(y = ymax * 1.08, label = .group),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = expression(Weed~biomass~"(kg"~ha^{-1}*")"),
    title   = "Ecobean: total weed biomass (raw means)",
    caption = "Bars show raw treatment means (kg ha^{-1}) ± SE; letters reuse GLMM-based Fisher’s LSD groups (α = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_eco_wbm_total_raw_kg  # print in Rmd

# 4) Save raw kg/ha figure
ggsave(
  filename = file.path(fig_dir_eco_total, "fig_eco_weed_biomass_total_raw_kg_ha.png"),
  plot     = fig_eco_wbm_total_raw_kg,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)


## C) RAW means for extension (lb ac^-1) --------------------------------

# 1) Convert raw means + SE to lb ac^-1
plot_df_wbm_eco_raw_lb <- plot_df_wbm_eco_raw |>
  mutate(
    mean_lb = mean * kg_ha_to_lb_ac,
    se_lb   = se   * kg_ha_to_lb_ac,
    ymin_lb = pmax(mean_lb - se_lb, 0),
    ymax_lb = mean_lb + se_lb
  )

# 2) Plot: Ecobean raw means (lb ac^-1)
fig_eco_wbm_total_raw_lb <- ggplot(
  plot_df_wbm_eco_raw_lb,
  aes(x = weed_trt, y = mean_lb, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin_lb, ymax = ymax_lb), width = 0.14) +
  geom_text(
    aes(y = ymax_lb * 1.08, label = .group),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = expression(Weed~biomass~"(lb"~ac^{-1}*")"),
    title   = "Ecobean: total weed biomass by mowing (raw means, lb ac⁻¹)",
    caption = "Bars show raw treatment means (lb ac⁻¹) ± SE; letters reuse GLMM-based Fisher’s LSD groups (α = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_eco_wbm_total_raw_lb  # print in Rmd

# 3) Save raw lb/ac figure
ggsave(
  filename = file.path(fig_dir_eco_total, "fig_eco_weed_biomass_total_raw_lb_ac.png"),
  plot     = fig_eco_wbm_total_raw_lb,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)

```

### New York only
```{r}
### New York ONLY (Cornell + Farm Hub): TOTAL weed biomass figures -------
### Updated for final NY model:
###   weed_glmm_ny: weed_trt * weeds + (1|site_year) + (1|site_year:block),
###                Tweedie(log), disp = ~ site_year * weeds, zi = ~0
### Requested: facet with an upper row panel = Ambient weeds + Surrogate weeds

# Conversions -----------------------------------------------------------
kg_ha_to_lb_ac  <- 0.892179
lb_per_bu_beans <- 60
kg_ha_to_bu_ac  <- kg_ha_to_lb_ac / lb_per_bu_beans

# Figure directory ------------------------------------------------------
fig_dir_ny_total <- here("analysis", "figs", "weed-biomass", "NY-only", "total")
dir.create(fig_dir_ny_total, showWarnings = FALSE, recursive = TRUE)

# Facet order (top row = Ambient weeds, then Surrogate weeds) -----------
weeds_levels <- c("Ambient weeds", "Surrogate weeds")

# ----------------------------------------------------------------------
# 1) MODEL-PREDICTED MEANS by mowing WITHIN weediness (kg ha^-1)
# ----------------------------------------------------------------------
# Requires from your updated summary chunk:
#   - emm_int_wbm_ny_df (weeds, weed_trt, model_mean, SE, ci_low, ci_high)
#   - cld_int_wbm_ny    (weeds, weed_trt, int_CLD)
#
# If you *don't* have those objects in memory, uncomment the block below
# to generate them directly from weed_glmm_ny.

# ---- optional re-generate emmeans objects (safe) ----------------------
# emm_int_wbm_ny <- emmeans::emmeans(weed_glmm_ny, ~ weed_trt | weeds, type = "response")
# emm_int_wbm_ny_df <- tidy_emm(emm_int_wbm_ny, trt_var = "weed_trt", ref_levels = mow_levels) |>
#   dplyr::mutate(
#     weeds      = factor(weeds, levels = weeds_levels),
#     weed_trt   = factor(weed_trt, levels = mow_levels),
#     model_mean = response
#   ) |>
#   dplyr::select(weeds, weed_trt, model_mean, SE, ci_low, ci_high)
#
# cld_int_wbm_ny <- multcomp::cld(
#   emm_int_wbm_ny, adjust = "none", Letters = letters, sort = TRUE, reversed = TRUE
# ) |>
#   tibble::as_tibble() |>
#   dplyr::mutate(
#     weeds    = factor(weeds, levels = weeds_levels),
#     weed_trt = factor(weed_trt, levels = mow_levels),
#     int_CLD  = stringr::str_trim(.group)
#   ) |>
#   dplyr::select(weeds, weed_trt, int_CLD)

plot_df_wbm_ny_model <- emm_int_wbm_ny_df |>
  dplyr::mutate(
    weeds    = factor(weeds, levels = weeds_levels),
    weed_trt = factor(weed_trt, levels = mow_levels),
    mean     = model_mean,
    ymin     = pmax(mean - SE, 0),
    ymax     = mean + SE
  ) |>
  dplyr::left_join(cld_int_wbm_ny, by = c("weeds", "weed_trt")) |>
  dplyr::mutate(
    cld_y = ymax * 1.08
  )

fig_ny_wbm_total_model <- ggplot(
  plot_df_wbm_ny_model,
  aes(x = weed_trt, y = mean, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.14) +
  geom_text(
    aes(y = cld_y, label = int_CLD),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  facet_wrap(~ weeds, nrow = 1) +   # <- 1 row, left-to-right: Ambient then Surrogate
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = expression(Weed~biomass~"(kg"~ha^{-1}*")"),
    title   = "New York (Cornell + Farm Hub): total weed biomass by mowing and weediness",
    caption = "Panels show GLMM-predicted marginal means (kg ha\u207b\u00b9) \u00b1 SE. Letters denote Fisher\u2019s LSD groups (\u03b1 = 0.05) within each panel."
  ) +
  theme_classic(base_size = 18) +
  theme(
    strip.background = element_blank(),
    strip.text       = element_text(face = "bold"),
    axis.text.x      = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y     = element_text(margin = margin(r = 8)),
    plot.title       = element_text(face = "bold"),
    plot.caption     = element_text(size = 9, hjust = 0)
  )

fig_ny_wbm_total_model

ggsave(
  filename = file.path(fig_dir_ny_total, "fig_ny_weed_biomass_total_model_byWeeds_kg_ha.png"),
  plot     = fig_ny_wbm_total_model,
  width    = 12,
  height   = 5.5,
  dpi      = 300
)

# ----------------------------------------------------------------------
# 1a) MODEL-PREDICTED MEANS by mowing WITHIN weediness (lb/ac)
# ----------------------------------------------------------------------

plot_df_wbm_ny_model_lb <- plot_df_wbm_ny_model |>
  dplyr::mutate(
    mean_lb = mean * kg_ha_to_lb_ac,
    SE_lb   = SE   * kg_ha_to_lb_ac,
    ymin_lb = pmax(mean_lb - SE_lb, 0),
    ymax_lb = mean_lb + SE_lb,
    cld_y_lb = ymax_lb * 1.08
  )

fig_ny_wbm_total_model_lb <- ggplot(
  plot_df_wbm_ny_model_lb,
  aes(x = weed_trt, y = mean_lb, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin_lb, ymax = ymax_lb), width = 0.14) +
  geom_text(
    aes(y = cld_y_lb, label = int_CLD),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  facet_wrap(~ weeds, nrow = 1) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x = NULL,
    y = "Weed biomass (lb/ac)"
  ) +
  theme_classic(base_size = 14) +
  theme(
    strip.background = element_blank(),
    strip.text       = element_text(face = "bold", size = 18),
    axis.text.x      = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y     = element_text(margin = margin(r = 8))
  )

fig_ny_wbm_total_model_lb

ggsave(
  filename = file.path(fig_dir_ny_total, "fig_ny_weed_biomass_total_model_byWeeds_lb_ac.png"),
  plot     = fig_ny_wbm_total_model_lb,
  width    = 12,
  height   = 5.5,
  dpi      = 300
)

# ----------------------------------------------------------------------
# 1b) MODEL-PREDICTED MEANS by mowing WITHIN weediness (bu/ac)
# ----------------------------------------------------------------------

plot_df_wbm_ny_model_bu <- plot_df_wbm_ny_model |>
  dplyr::mutate(
    mean_bu = mean * kg_ha_to_bu_ac,
    SE_bu   = SE   * kg_ha_to_bu_ac,
    ymin_bu = pmax(mean_bu - SE_bu, 0),
    ymax_bu = mean_bu + SE_bu,
    cld_y_bu = ymax_bu * 1.08
  )

fig_ny_wbm_total_model_bu <- ggplot(
  plot_df_wbm_ny_model_bu,
  aes(x = weed_trt, y = mean_bu, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin_bu, ymax = ymax_bu), width = 0.14) +
  geom_text(
    aes(y = cld_y_bu, label = int_CLD),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  facet_wrap(~ weeds, nrow = 1) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x = NULL,
    y = expression(Weed~biomass~"(bu"~ac^{-1}*")")
  ) +
  theme_classic(base_size = 18) +
  theme(
    strip.background = element_blank(),
    strip.text       = element_text(face = "bold"),
    axis.text.x      = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y     = element_text(margin = margin(r = 8))
  )

fig_ny_wbm_total_model_bu

ggsave(
  filename = file.path(fig_dir_ny_total, "fig_ny_weed_biomass_total_model_byWeeds_bu_ac.png"),
  plot     = fig_ny_wbm_total_model_bu,
  width    = 12,
  height   = 5.5,
  dpi      = 300
)

# ----------------------------------------------------------------------
# 2) RAW MEANS by mowing WITHIN weediness (kg ha^-1)
#    + reuse model CLDs (int_CLD) for letters
# ----------------------------------------------------------------------

raw_ny_wbm_fig <- weed_biomass_ny |>
  dplyr::group_by(weeds, weed_trt) |>
  dplyr::summarise(
    n    = dplyr::n(),
    mean = mean(weed_biomass_kg_ha, na.rm = TRUE),
    sd   = stats::sd(weed_biomass_kg_ha, na.rm = TRUE),
    se   = sd / sqrt(n),
    .groups = "drop"
  ) |>
  dplyr::mutate(
    weeds    = factor(weeds, levels = weeds_levels),
    weed_trt = factor(weed_trt, levels = mow_levels),
    ymin     = pmax(mean - se, 0),
    ymax     = mean + se,
    cld_y    = ymax * 1.08
  ) |>
  dplyr::left_join(cld_int_wbm_ny, by = c("weeds", "weed_trt"))

fig_ny_wbm_total_raw_kg <- ggplot(
  raw_ny_wbm_fig,
  aes(x = weed_trt, y = mean, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.14) +
  geom_text(
    aes(y = cld_y, label = int_CLD),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  facet_wrap(~ weeds, nrow = 1) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = expression(Weed~biomass~"(kg"~ha^{-1}*")"),
    title   = "New York (Cornell + Farm Hub): total weed biomass by mowing and weediness",
    caption = "Panels show raw means (kg ha\u207b\u00b9) \u00b1 SE. Letters reuse GLMM-based Fisher\u2019s LSD groups (\u03b1 = 0.05) within each panel."
  ) +
  theme_classic(base_size = 1) +
  theme(
    strip.background = element_blank(),
    strip.text       = element_text(face = "bold"),
    axis.text.x      = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y     = element_text(margin = margin(r = 8)),
    plot.title       = element_text(face = "bold"),
    plot.caption     = element_text(size = 9, hjust = 0)
  )

fig_ny_wbm_total_raw_kg

ggsave(
  filename = file.path(fig_dir_ny_total, "fig_ny_weed_biomass_total_raw_byWeeds_kg_ha.png"),
  plot     = fig_ny_wbm_total_raw_kg,
  width    = 12,
  height   = 5.5,
  dpi      = 300
)

# ----------------------------------------------------------------------
# 3) RAW MEANS by mowing WITHIN weediness (lb/ac)
# ----------------------------------------------------------------------

weeds_levels <- c("Ambient weeds", "Surrogate weeds")

raw_ny_wbm_fig <- weed_biomass_ny |>
  dplyr::group_by(weeds, weed_trt) |>
  dplyr::summarise(
    n    = dplyr::n(),
    mean = mean(weed_biomass_kg_ha, na.rm = TRUE),
    sd   = sd(weed_biomass_kg_ha, na.rm = TRUE),
    se   = sd / sqrt(sum(!is.na(weed_biomass_kg_ha))),
    .groups = "drop"
  ) |>
  dplyr::mutate(
    weeds    = factor(weeds, levels = weeds_levels),
    weed_trt = factor(weed_trt, levels = mow_levels)
  )
raw_ny_wbm_fig_lb <- raw_ny_wbm_fig |>
  dplyr::mutate(
    mean_lb  = mean * kg_ha_to_lb_ac,
    se_lb    = se   * kg_ha_to_lb_ac,
    ymin_lb  = pmax(mean_lb - se_lb, 0),
    ymax_lb  = mean_lb + se_lb,
    cld_y_lb = ymax_lb * 1.08
  ) |>
  dplyr::left_join(
    cld_int_wbm_ny |>
      dplyr::mutate(
        weeds    = factor(weeds, levels = weeds_levels),
        weed_trt = factor(weed_trt, levels = mow_levels)
      ),
    by = c("weeds", "weed_trt")
  )
fig_ny_wbm_total_raw_lb <- ggplot(
  raw_ny_wbm_fig_lb,
  aes(x = weed_trt, y = mean_lb, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin_lb, ymax = ymax_lb), width = 0.14) +
  geom_text(
    aes(y = cld_y_lb, label = int_CLD),
    vjust = 0, fontface = "bold", size = 6
  ) +
  facet_wrap(~ weeds, nrow = 1) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x = NULL,
    y = "Weed biomass (lb/ac)",
    #title = "Weed biomass by mowing and weediness",
    #caption = "Panels show raw means (lb/ac) ± SE. Letters are GLMM-based Fisher’s LSD groups (α = 0.05) within each panel."
  ) +
  theme_classic(base_size = 15) +
  theme(
    strip.background = element_blank(),
    strip.text       = element_text(face = "bold", size = 18),  # bigger facet titles
    axis.text.x      = element_text(lineheight = 0.95, margin = margin(t = 8)),
    plot.title       = element_text(face = "bold"),
    plot.caption     = element_text(size = 9, hjust = 0)
  )

fig_ny_wbm_total_raw_lb

ggsave(
  filename = file.path(fig_dir_ny_total, "fig_ny_weed_biomass_total_raw_byWeeds_lb_ac.png"),
  plot     = fig_ny_wbm_total_raw_lb,
  width    = 12,
  height   = 5.5,
  dpi      = 300
)



# ----------------------------------------------------------------------
# 3a) RAW MEANS by mowing WITHIN weediness (bu/ac)
# ----------------------------------------------------------------------


raw_ny_wbm_fig_bu <- raw_ny_wbm_fig |>
  dplyr::mutate(
    mean_bu  = mean * kg_ha_to_bu_ac,
    se_bu    = se   * kg_ha_to_bu_ac,
    ymin_bu  = pmax(mean_bu - se_bu, 0),
    ymax_bu  = mean_bu + se_bu,
    cld_y_bu = ymax_bu * 1.08
  )

fig_ny_wbm_total_raw_bu <- ggplot(
  raw_ny_wbm_fig_bu,
  aes(x = weed_trt, y = mean_bu, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin_bu, ymax = ymax_bu), width = 0.14) +
  geom_text(
    aes(y = cld_y_bu, label = int_CLD),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  facet_wrap(~ weeds, nrow = 1) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = expression(Weed~biomass~"(bu"~ac^{-1}*")"),
    title   = "Weed biomass by mowing and weediness",
    #caption = "Panels show raw means (bu ac\u207b\u00b9) \u00b1 SE. Letters reuse GLMM-based Fisher\u2019s LSD groups (\u03b1 = 0.05) within each panel."
  ) +
  theme_classic(base_size = 18) +
  theme(
    strip.background = element_blank(),
    strip.text       = element_text(face = "bold"),
    axis.text.x      = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y     = element_text(margin = margin(r = 8)),
    plot.title       = element_text(face = "bold"),
    plot.caption     = element_text(size = 9, hjust = 0)
  )

fig_ny_wbm_total_raw_bu

ggsave(
  filename = file.path(fig_dir_ny_total, "fig_ny_weed_biomass_total_raw_byWeeds_bu_ac.png"),
  plot     = fig_ny_wbm_total_raw_bu,
  width    = 12,
  height   = 5.5,
  dpi      = 300
)


```

##In-row weed biomass
### Ecobean
```{r}
## Ecobean IN-ROW weed biomass: figures (model + raw, kg/ha & lb/ac) ----

kg_ha_to_lb_ac <- 0.892179

fig_dir_eco_inrow <- here("analysis", "figs", "weed-biomass", "Ecobean", "inrow")
dir.create(fig_dir_eco_inrow, showWarnings = FALSE, recursive = TRUE)

# 1) MODEL-BASED MEANS (kg ha⁻¹) ---------------------------------------

emm_trt_in_eco <- emmeans(
  wbm_inrow_glmm_eco,
  ~ weed_trt,
  type = "response"
)

emm_trt_in_eco_df <- as_tibble(emm_trt_in_eco) |>
  dplyr::mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    mean     = response,
    ymin     = pmax(mean - SE, 0),
    ymax     = mean + SE
  )

cld_trt_in_eco <- multcomp::cld(
  emm_trt_in_eco,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE   # "a" = highest biomass
) |>
  as_tibble() |>
  dplyr::mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    .group   = stringr::str_trim(.group)
  ) |>
  dplyr::select(weed_trt, .group)

plot_df_inrow_eco_model <- emm_trt_in_eco_df |>
  dplyr::left_join(cld_trt_in_eco, by = "weed_trt")

fig_inrow_eco_model_kg <- ggplot(
  plot_df_inrow_eco_model,
  aes(x = weed_trt, y = mean, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.14) +
  geom_text(
    aes(y = ymax * 1.08, label = .group),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = "In-row weed biomass (kg ha\u207b\u00b9)",
    title   = "Ecobean in-row weed biomass by mowing treatment",
    caption = "Bars show GLMM-predicted marginal means (kg ha\u207b\u00b9) \u00b1 SE; letters denote Fisher\u2019s LSD groups (\u03b1 = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_inrow_eco_model_kg  # print in Rmd

ggsave(
  filename = file.path(fig_dir_eco_inrow, "fig_eco-inrow-wbm_model_kg_ha.png"),
  plot     = fig_inrow_eco_model_kg,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)


# 2) MODEL-BASED MEANS (lb ac⁻¹) ---------------------------------------

plot_df_inrow_eco_model_lb <- plot_df_inrow_eco_model |>
  dplyr::mutate(
    mean_lb = mean * kg_ha_to_lb_ac,
    ymin_lb = ymin * kg_ha_to_lb_ac,
    ymax_lb = ymax * kg_ha_to_lb_ac
  )

fig_inrow_eco_model_lb <- ggplot(
  plot_df_inrow_eco_model_lb,
  aes(x = weed_trt, y = mean_lb, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin_lb, ymax = ymax_lb), width = 0.14) +
  geom_text(
    aes(y = ymax_lb * 1.08, label = .group),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = "In-row weed biomass (lb ac\u207b\u00b9)",
    title   = "Ecobean in-row weed biomass by mowing treatment ",
    caption = "Bars show GLMM-predicted marginal means (lb ac\u207b\u00b9) \u00b1 SE; letters denote Fisher\u2019s LSD groups (\u03b1 = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_inrow_eco_model_lb  # print in Rmd

ggsave(
  filename = file.path(fig_dir_eco_inrow, "fig_eco-inrow-wbm_model_lb_ac.png"),
  plot     = fig_inrow_eco_model_lb,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)


# 3) RAW MEANS (kg ha⁻¹) ------------------------------------------------

raw_inrow_eco <- eco_inrow |>
  dplyr::group_by(weed_trt) |>
  dplyr::summarise(
    n    = dplyr::n(),
    mean = mean(inrow_weed_biomass_kg_ha, na.rm = TRUE),
    sd   = sd(inrow_weed_biomass_kg_ha, na.rm = TRUE),
    se   = sd / sqrt(n),
    .groups = "drop"
  ) |>
  dplyr::mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    ymin     = pmax(mean - se, 0),
    ymax     = mean + se
  )

plot_df_inrow_eco_raw <- raw_inrow_eco |>
  dplyr::left_join(cld_trt_in_eco, by = "weed_trt")

fig_inrow_eco_raw_kg <- ggplot(
  plot_df_inrow_eco_raw,
  aes(x = weed_trt, y = mean, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.14) +
  geom_text(
    aes(y = ymax * 1.08, label = .group),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = "In-row weed biomass (kg ha\u207b\u00b9)",
    title   = "Ecobean in-row weed biomass by mowing treatment",
    caption = "Bars show raw means (kg ha\u207b\u00b9) \u00b1 SE; letters denote Fisher\u2019s LSD groups (\u03b1 = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_inrow_eco_raw_kg  # print in Rmd

ggsave(
  filename = file.path(fig_dir_eco_inrow, "fig_eco-inrow-wbm_raw_kg_ha.png"),
  plot     = fig_inrow_eco_raw_kg,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)


# 4) RAW MEANS (lb ac⁻¹) -----------------------------------------------

plot_df_inrow_eco_raw_lb <- plot_df_inrow_eco_raw |>
  dplyr::mutate(
    mean_lb = mean * kg_ha_to_lb_ac,
    ymin_lb = ymin * kg_ha_to_lb_ac,
    ymax_lb = ymax * kg_ha_to_lb_ac
  )

fig_inrow_eco_raw_lb <- ggplot(
  plot_df_inrow_eco_raw_lb,
  aes(x = weed_trt, y = mean_lb, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin_lb, ymax = ymax_lb), width = 0.14) +
  geom_text(
    aes(y = ymax_lb * 1.08, label = .group),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = "In-row weed biomass (lb ac\u207b\u00b9)",
    title   = "Ecobean in-row weed biomass by mowing treatment",
    caption = "Bars show raw means (lb ac\u207b\u00b9) \u00b1 SE; letters denote Fisher\u2019s LSD groups (\u03b1 = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_inrow_eco_raw_lb  # print in Rmd

ggsave(
  filename = file.path(fig_dir_eco_inrow, "fig_eco-inrow-wbm_raw_lb_ac.png"),
  plot     = fig_inrow_eco_raw_lb,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)

```
### New York only
```{r}
## NY-only IN-ROW weed biomass: figures (model + raw, kg/ha & lb/ac) ----

kg_ha_to_lb_ac <- 0.892179

fig_dir_ny_inrow <- here("analysis", "figs", "weed-biomass", "NY-only", "inrow")
dir.create(fig_dir_ny_inrow, showWarnings = FALSE, recursive = TRUE)

# 1) MODEL-BASED MEANS (kg ha⁻¹) ---------------------------------------

emm_trt_in_ny <- emmeans(
  wbm_inrow_glmm_ny,
  ~ weed_trt,
  type = "response"
)

emm_trt_in_ny_df <- as_tibble(emm_trt_in_ny) |>
  dplyr::mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    mean     = response,
    ymin     = pmax(mean - SE, 0),
    ymax     = mean + SE
  )

cld_trt_in_ny <- multcomp::cld(
  emm_trt_in_ny,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE   # "a" = highest biomass
) |>
  as_tibble() |>
  dplyr::mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    .group   = stringr::str_trim(.group)
  ) |>
  dplyr::select(weed_trt, .group)

plot_df_inrow_ny_model <- emm_trt_in_ny_df |>
  dplyr::left_join(cld_trt_in_ny, by = "weed_trt")

fig_inrow_ny_model_kg <- ggplot(
  plot_df_inrow_ny_model,
  aes(x = weed_trt, y = mean, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.14) +
  geom_text(
    aes(y = ymax * 1.08, label = .group),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = "In-row weed biomass (kg ha\u207b\u00b9)",
    title   = "New York in-row weed biomass by mowing treatment",
    caption = "Bars show GLMM-predicted marginal means (kg ha\u207b\u00b9) \u00b1 SE; letters denote Fisher\u2019s LSD groups (\u03b1 = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_inrow_ny_model_kg  # print in Rmd

ggsave(
  filename = file.path(fig_dir_ny_inrow, "fig_ny-inrow-wbm_model_kg_ha.png"),
  plot     = fig_inrow_ny_model_kg,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)


# 2) MODEL-BASED MEANS (lb ac⁻¹) ---------------------------------------

plot_df_inrow_ny_model_lb <- plot_df_inrow_ny_model |>
  dplyr::mutate(
    mean_lb = mean * kg_ha_to_lb_ac,
    ymin_lb = ymin * kg_ha_to_lb_ac,
    ymax_lb = ymax * kg_ha_to_lb_ac
  )

fig_inrow_ny_model_lb <- ggplot(
  plot_df_inrow_ny_model_lb,
  aes(x = weed_trt, y = mean_lb, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin_lb, ymax = ymax_lb), width = 0.14) +
  geom_text(
    aes(y = ymax_lb * 1.08, label = .group),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = "In-row weed biomass (lb ac\u207b\u00b9)",
    title   = "New York in-row weed biomass by mowing treatment",
    caption = "Bars show GLMM-predicted marginal means (lb ac\u207b\u00b9) \u00b1 SE; letters denote Fisher\u2019s LSD groups (\u03b1 = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_inrow_ny_model_lb  # print in Rmd

ggsave(
  filename = file.path(fig_dir_ny_inrow, "fig_ny-inrow-wbm_model_lb_ac.png"),
  plot     = fig_inrow_ny_model_lb,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)


# 3) RAW MEANS (kg ha⁻¹) ------------------------------------------------

raw_inrow_ny <- ny_inrow |>
  dplyr::group_by(weed_trt) |>
  dplyr::summarise(
    n    = dplyr::n(),
    mean = mean(inrow_weed_biomass_kg_ha, na.rm = TRUE),
    sd   = sd(inrow_weed_biomass_kg_ha, na.rm = TRUE),
    se   = sd / sqrt(n),
    .groups = "drop"
  ) |>
  dplyr::mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    ymin     = pmax(mean - se, 0),
    ymax     = mean + se
  )

plot_df_inrow_ny_raw <- raw_inrow_ny |>
  dplyr::left_join(cld_trt_in_ny, by = "weed_trt")

fig_inrow_ny_raw_kg <- ggplot(
  plot_df_inrow_ny_raw,
  aes(x = weed_trt, y = mean, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.14) +
  geom_text(
    aes(y = ymax * 1.08, label = .group),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = "In-row weed biomass (kg ha\u207b\u00b9)",
    title   = "New York in-row weed biomass by mowing treatment",
    caption = "Bars show raw means (kg ha\u207b\u00b9) \u00b1 SE; letters denote Fisher\u2019s LSD groups (\u03b1 = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_inrow_ny_raw_kg  # print in Rmd

ggsave(
  filename = file.path(fig_dir_ny_inrow, "fig_ny-inrow-wbm_raw_kg_ha.png"),
  plot     = fig_inrow_ny_raw_kg,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)


# 4) RAW MEANS (lb ac⁻¹) -----------------------------------------------

plot_df_inrow_ny_raw_lb <- plot_df_inrow_ny_raw |>
  dplyr::mutate(
    mean_lb = mean * kg_ha_to_lb_ac,
    ymin_lb = ymin * kg_ha_to_lb_ac,
    ymax_lb = ymax * kg_ha_to_lb_ac
  )

fig_inrow_ny_raw_lb <- ggplot(
  plot_df_inrow_ny_raw_lb,
  aes(x = weed_trt, y = mean_lb, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin_lb, ymax = ymax_lb), width = 0.14) +
  geom_text(
    aes(y = ymax_lb * 1.08, label = .group),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = "In-row weed biomass (lb ac\u207b\u00b9)",
    title   = "New York in-row weed biomass by mowing treatment",
    caption = "Bars show raw means (lb ac\u207b\u00b9) \u00b1 SE; letters denote Fisher\u2019s LSD groups (\u03b1 = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_inrow_ny_raw_lb  # print in Rmd

ggsave(
  filename = file.path(fig_dir_ny_inrow, "fig_ny-inrow-wbm_raw_lb_ac.png"),
  plot     = fig_inrow_ny_raw_lb,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)

```
##Inter-row weed biomass
### Ecobean
```{r}
## Ecobean INTER-ROW weed biomass: figures (model + raw, kg/ha & lb/ac) --

kg_ha_to_lb_ac <- 0.892179

fig_dir_eco_inter <- here("analysis", "figs", "weed-biomass", "Ecobean", "interrow")
dir.create(fig_dir_eco_inter, showWarnings = FALSE, recursive = TRUE)

# 1) MODEL-BASED MEANS (kg ha⁻¹) ----------------------------------------

emm_trt_eco_inter <- emmeans(
  wbm_inter_glmm_eco,
  ~ weed_trt,
  type = "response"
)

emm_trt_eco_inter_df <- as_tibble(emm_trt_eco_inter) |>
  dplyr::mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    mean     = response,
    ymin     = pmax(mean - SE, 0),
    ymax     = mean + SE
  )

cld_trt_eco_inter <- multcomp::cld(
  emm_trt_eco_inter,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE   # "a" = highest biomass
) |>
  as_tibble() |>
  dplyr::mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    .group   = stringr::str_trim(.group)
  ) |>
  dplyr::select(weed_trt, .group)

plot_df_eco_inter_model <- emm_trt_eco_inter_df |>
  dplyr::left_join(cld_trt_eco_inter, by = "weed_trt")

fig_eco_inter_model_kg <- ggplot(
  plot_df_eco_inter_model,
  aes(x = weed_trt, y = mean, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.14) +
  geom_text(
    aes(y = ymax * 1.08, label = .group),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = "Inter-row weed biomass (kg ha\u207b\u00b9)",
    title   = "Ecobean inter-row weed biomass by mowing treatment",
    caption = "Bars show GLMM-predicted marginal means (kg ha\u207b\u00b9) \u00b1 SE; letters denote Fisher\u2019s LSD groups (\u03b1 = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_eco_inter_model_kg  # print in Rmd

ggsave(
  filename = file.path(fig_dir_eco_inter, "fig_eco-interrow-wbm_model_kg_ha.png"),
  plot     = fig_eco_inter_model_kg,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)


# 2) MODEL-BASED MEANS (lb ac⁻¹) ----------------------------------------

plot_df_eco_inter_model_lb <- plot_df_eco_inter_model |>
  dplyr::mutate(
    mean_lb = mean * kg_ha_to_lb_ac,
    ymin_lb = ymin * kg_ha_to_lb_ac,
    ymax_lb = ymax * kg_ha_to_lb_ac
  )

fig_eco_inter_model_lb <- ggplot(
  plot_df_eco_inter_model_lb,
  aes(x = weed_trt, y = mean_lb, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin_lb, ymax = ymax_lb), width = 0.14) +
  geom_text(
    aes(y = ymax_lb * 1.08, label = .group),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = "Inter-row weed biomass (lb ac\u207b\u00b9)",
    title   = "Ecobean inter-row weed biomass by mowing treatment ",
    caption = "Bars show GLMM-predicted marginal means (lb ac\u207b\u00b9) \u00b1 SE; letters denote Fisher\u2019s LSD groups (\u03b1 = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_eco_inter_model_lb  # print in Rmd

ggsave(
  filename = file.path(fig_dir_eco_inter, "fig_eco-interrow-wbm_model_lb_ac.png"),
  plot     = fig_eco_inter_model_lb,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)


# 3) RAW MEANS (kg ha⁻¹) -------------------------------------------------

raw_eco_inter <- eco_inter |>
  dplyr::group_by(weed_trt) |>
  dplyr::summarise(
    n    = dplyr::n(),
    mean = mean(interrow_weed_biomass_kg_ha, na.rm = TRUE),
    sd   = sd(interrow_weed_biomass_kg_ha, na.rm = TRUE),
    se   = sd / sqrt(n),
    .groups = "drop"
  ) |>
  dplyr::mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    ymin     = pmax(mean - se, 0),
    ymax     = mean + se
  )

plot_df_eco_inter_raw <- raw_eco_inter |>
  dplyr::left_join(cld_trt_eco_inter, by = "weed_trt")

fig_eco_inter_raw_kg <- ggplot(
  plot_df_eco_inter_raw,
  aes(x = weed_trt, y = mean, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.14) +
  geom_text(
    aes(y = ymax * 1.08, label = .group),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = "Inter-row weed biomass (kg ha\u207b\u00b9)",
    title   = "Ecobean inter-row weed biomass by mowing treatment ",
    caption = "Bars show raw means (kg ha\u207b\u00b9) \u00b1 SE; letters denote Fisher\u2019s LSD groups (\u03b1 = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_eco_inter_raw_kg  # print in Rmd

ggsave(
  filename = file.path(fig_dir_eco_inter, "fig_eco-interrow-wbm_raw_kg_ha.png"),
  plot     = fig_eco_inter_raw_kg,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)


# 4) RAW MEANS (lb ac⁻¹) -------------------------------------------------

plot_df_eco_inter_raw_lb <- plot_df_eco_inter_raw |>
  dplyr::mutate(
    mean_lb = mean * kg_ha_to_lb_ac,
    ymin_lb = ymin * kg_ha_to_lb_ac,
    ymax_lb = ymax * kg_ha_to_lb_ac
  )

fig_eco_inter_raw_lb <- ggplot(
  plot_df_eco_inter_raw_lb,
  aes(x = weed_trt, y = mean_lb, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin_lb, ymax = ymax_lb), width = 0.14) +
  geom_text(
    aes(y = ymax_lb * 1.08, label = .group),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = "Inter-row weed biomass (lb ac\u207b\u00b9)",
    title   = "Ecobean inter-row weed biomass by mowing treatment ",
    caption = "Bars show raw means (lb ac\u207b\u00b9) \u00b1 SE; letters denote Fisher\u2019s LSD groups (\u03b1 = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_eco_inter_raw_lb  # print in Rmd

ggsave(
  filename = file.path(fig_dir_eco_inter, "fig_eco-interrow-wbm_raw_lb_ac.png"),
  plot     = fig_eco_inter_raw_lb,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)

```
### New York only
```{r}
## NY-only INTER-ROW weed biomass: figures (model + raw, kg/ha & lb/ac) --

kg_ha_to_lb_ac <- 0.892179

fig_dir_ny_inter <- here("analysis", "figs", "weed-biomass", "NY-only", "interrow")
dir.create(fig_dir_ny_inter, showWarnings = FALSE, recursive = TRUE)

# 1) MODEL-BASED MEANS (kg ha⁻¹) ----------------------------------------

emm_trt_ny_inter <- emmeans(
  wbm_inter_glmm_ny,
  ~ weed_trt,
  type = "response"
)

emm_trt_ny_inter_df <- as_tibble(emm_trt_ny_inter) |>
  dplyr::mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    mean     = response,
    ymin     = pmax(mean - SE, 0),
    ymax     = mean + SE
  )

cld_trt_ny_inter <- multcomp::cld(
  emm_trt_ny_inter,
  adjust   = "none",
  Letters  = letters,
  sort     = TRUE,
  reversed = TRUE   # "a" = highest biomass
) |>
  as_tibble() |>
  dplyr::mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    .group   = stringr::str_trim(.group)
  ) |>
  dplyr::select(weed_trt, .group)

plot_df_ny_inter_model <- emm_trt_ny_inter_df |>
  dplyr::left_join(cld_trt_ny_inter, by = "weed_trt")

fig_ny_inter_model_kg <- ggplot(
  plot_df_ny_inter_model,
  aes(x = weed_trt, y = mean, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.14) +
  geom_text(
    aes(y = ymax * 1.08, label = .group),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = "Inter-row weed biomass (kg ha\u207b\u00b9)",
    title   = "NY-only inter-row weed biomass by mowing treatment",
    caption = "Bars show GLMM-predicted marginal means (kg ha\u207b\u00b9) \u00b1 SE; letters denote Fisher\u2019s LSD groups (\u03b1 = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_ny_inter_model_kg  # print in Rmd

ggsave(
  filename = file.path(fig_dir_ny_inter, "fig_ny-interrow-wbm_model_kg_ha.png"),
  plot     = fig_ny_inter_model_kg,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)


# 2) MODEL-BASED MEANS (lb ac⁻¹) ----------------------------------------

plot_df_ny_inter_model_lb <- plot_df_ny_inter_model |>
  dplyr::mutate(
    mean_lb = mean * kg_ha_to_lb_ac,
    ymin_lb = ymin * kg_ha_to_lb_ac,
    ymax_lb = ymax * kg_ha_to_lb_ac
  )

fig_ny_inter_model_lb <- ggplot(
  plot_df_ny_inter_model_lb,
  aes(x = weed_trt, y = mean_lb, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin_lb, ymax = ymax_lb), width = 0.14) +
  geom_text(
    aes(y = ymax_lb * 1.08, label = .group),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = "Inter-row weed biomass (lb ac\u207b\u00b9)",
    title   = "NY-only inter-row weed biomass by mowing treatment (extension scale)",
    caption = "Bars show GLMM-predicted marginal means (lb ac\u207b\u00b9) \u00b1 SE; letters denote Fisher\u2019s LSD groups (\u03b1 = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_ny_inter_model_lb  # print in Rmd

ggsave(
  filename = file.path(fig_dir_ny_inter, "fig_ny-interrow-wbm_model_lb_ac.png"),
  plot     = fig_ny_inter_model_lb,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)


# 3) RAW MEANS (kg ha⁻¹) -------------------------------------------------

raw_ny_inter <- ny_inter |>
  dplyr::group_by(weed_trt) |>
  dplyr::summarise(
    n    = dplyr::n(),
    mean = mean(interrow_weed_biomass_kg_ha, na.rm = TRUE),
    sd   = sd(interrow_weed_biomass_kg_ha, na.rm = TRUE),
    se   = sd / sqrt(n),
    .groups = "drop"
  ) |>
  dplyr::mutate(
    weed_trt = factor(weed_trt, levels = mow_levels),
    ymin     = pmax(mean - se, 0),
    ymax     = mean + se
  )

plot_df_ny_inter_raw <- raw_ny_inter |>
  dplyr::left_join(cld_trt_ny_inter, by = "weed_trt")

fig_ny_inter_raw_kg <- ggplot(
  plot_df_ny_inter_raw,
  aes(x = weed_trt, y = mean, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.14) +
  geom_text(
    aes(y = ymax * 1.08, label = .group),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = "Inter-row weed biomass (kg ha\u207b\u00b9)",
    title   = "NY-only inter-row weed biomass by mowing treatment ",
    caption = "Bars show raw means (kg ha\u207b\u00b9) \u00b1 SE; letters denote Fisher\u2019s LSD groups (\u03b1 = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_ny_inter_raw_kg  # print in Rmd

ggsave(
  filename = file.path(fig_dir_ny_inter, "fig_ny-interrow-wbm_raw_kg_ha.png"),
  plot     = fig_ny_inter_raw_kg,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)


# 4) RAW MEANS (lb ac⁻¹) -------------------------------------------------

plot_df_ny_inter_raw_lb <- plot_df_ny_inter_raw |>
  dplyr::mutate(
    mean_lb = mean * kg_ha_to_lb_ac,
    ymin_lb = ymin * kg_ha_to_lb_ac,
    ymax_lb = ymax * kg_ha_to_lb_ac
  )

fig_ny_inter_raw_lb <- ggplot(
  plot_df_ny_inter_raw_lb,
  aes(x = weed_trt, y = mean_lb, fill = weed_trt)
) +
  geom_col(width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = ymin_lb, ymax = ymax_lb), width = 0.14) +
  geom_text(
    aes(y = ymax_lb * 1.08, label = .group),
    vjust    = 0,
    fontface = "bold",
    size     = 6
  ) +
  scale_fill_manual(values = fill_cols, guide = "none") +
  scale_x_discrete(labels = label_break_comma_cult) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    x       = NULL,
    y       = "Inter-row weed biomass (lb ac\u207b\u00b9)",
    title   = "NY-only inter-row weed biomass by mowing treatment ",
    caption = "Bars show raw means (lb ac\u207b\u00b9) \u00b1 SE; letters denote Fisher\u2019s LSD groups (\u03b1 = 0.05)."
  ) +
  theme_classic(base_size = 18) +
  theme(
    axis.text.x  = element_text(lineheight = 0.95, margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.title   = element_text(face = "bold"),
    plot.caption = element_text(size = 9, hjust = 0)
  )

fig_ny_inter_raw_lb  # print in Rmd

ggsave(
  filename = file.path(fig_dir_ny_inter, "fig_ny-interrow-wbm_raw_lb_ac.png"),
  plot     = fig_ny_inter_raw_lb,
  width    = 9,
  height   = 5.5,
  dpi      = 300
)

```

#last chunk
