---
title: "IMT Weed seed production"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<br>
```{r message=FALSE, warning=FALSE}

#Set work directory
setwd("/Users/ey239/Github/IMT/rmarkdowns")

#Load packages 
library(tidyverse) ##install.packages("tidyverse")
library(knitr)
library(patchwork) ##install.packages("patchwork")
library(skimr)     ##install.packages("skimr")
library(readxl)
library(janitor) ##install.packages("janitor")

library(kableExtra) ##install.packages("kableExtra")
library(webshot) ##install.packages("webshot")
webshot::install_phantomjs()
library(viridis) ##install.packages("viridis")
library(lme4) ##install.packages("lme4")
library(lmerTest) ##install.packages("lmerTest")
library(emmeans) ##install.packages("emmeans")
library(rstatix) ##install.packages("rstatix")
#library(Matrix) ##install.packages("Matrix")
library(multcomp) ##install.packages("multcomp")
library(multcompView) ##install.packages("multcompView")
library(ggResidpanel) ##install.packages("ggResidpanel")
#library(car)
#library(TMB)  ##install.packages("TMB")
library(glmmTMB)  ##install.packages("glmmTMB")
library(DHARMa)  ##install.packages("DHARMa")
library(performance) ##install.packages("performance")
library(WrensBookshelf)##install.packages("WrensBookshelf")
#Load Functions
MeanPlusSe<-function(x) mean(x)+plotrix::std.error(x)

find_logw0=function(x){c=trunc(log(min(x[x>0],na.rm=T)))
d=exp(c)
return(d)}
```
<br>

# Load and clean data

## Load data

``` {r}
combined_weed_seeds <- read_excel("~/Github/IMT/raw-data/combined_weed_seeds.xlsx")
kable(head(combined_weed_seeds))
```

##Clean data
##ECOBEAN
```{r}
#Standardaze column names, convert to factors, check for outliers of variable**
clean_combined <- clean_names(combined_weed_seeds) |>  
  rename ('mowing'= treatment) |> 
  mutate(across(c(year, location, site_year, mowing, block, plot ), as.factor)) 
#select and convert data for wbm analysis
weed_seeds_clean <- clean_combined |>             
  mutate(
    seed_number_meter = round(seed_number * (1 / 0.0078)),
    seed_number_foot = round(seed_number * (1 / 0.0078) / 10.7639) # 1 square meter = 10.7639 square feet
  )

  
kable(head(weed_seeds_clean)) 
```

##FARMHUB REPORT
```{r}
#Standardaze column names, convert to factors, check for outliers of variable**
clean_combined_fh <- clean_names(combined_weed_seeds) |>  
  rename ('mowing'= treatment) |> 
  filter(location %in% c("FH", "CU")) |>
  mutate(across(c(year, location, site_year, mowing, block, plot ), as.factor)) 
#select and convert data for wbm analysis
weed_seeds_clean_fh <-clean_combined_fh |>             
  mutate(seed_number_meter = round(seed_number *(1/0.0078))) 
  
kable(head(weed_seeds_clean_fh)) 
```




# Model testing

##ECOBEAN
### Glmm Poisson
```{r}

model_poisson <- glmmTMB(seed_number_meter ~ mowing  + (1|site_year:block),  
                         data = weed_seeds_clean, 
                         family = poisson(link = "log"))

###It assumes that mowing effects may vary by block, in addition to site-year and block-level variation.
#This would be useful if you suspect that mowing impacts weed biomass differently in different blocks.
#The model accounts for hierarchical structure down to the mowing level within blocks.

### Two checks specifically for a generalize linear approach
simulateResiduals(model_poisson ,plot = TRUE) 
testDispersion(model_poisson )
check_model(model_poisson ) #Perfect, preditions match real data

summary(model_poisson )
VarCorr(model_poisson )
outlier_test <- testOutliers(model_poisson, type = "bootstrap")


```
###Glmm negative binomial
```{r}
model_nbinom <- glmmTMB(seed_number_meter ~ mowing + (1|site_year:block),  
                        data = weed_seeds_clean, 
                        family = nbinom2(link = "log"))

### Two checks specifically for a generalize linear approach
simulateResiduals(model_nbinom ,plot = TRUE) 
testDispersion(model_nbinom )
check_model(model_nbinom ) #Perfect, preditions match real data

summary(model_nbinom )
VarCorr(model_nbinom )
outlier_test <- testOutliers(model_nbinom, type = "bootstrap")
```
###Glmm Zero-inflated Poisson (mowing)
```{r}
model_zip <- glmmTMB(seed_number_meter ~ mowing + (1|site_year:block),  
                     data = weed_seeds_clean, 
                     family = poisson(link = "log"), 
                     zi = ~ mowing)  # Zero inflation part modeled by 'mowing'

### Two checks specifically for a generalize linear approach
simulateResiduals(model_zip ,plot = TRUE) 
testDispersion(model_zip )
check_model(model_zip) #Perfect, preditions match real data

summary(model_zip)
VarCorr(model_zip )
outlier_test <- testOutliers(model_zip, type = "bootstrap")
```

###Glmm Zero-inflated Poisson location
```{r}
model_zip_location <- glmmTMB(seed_number_meter ~ mowing + (1|site_year:block),  data = weed_seeds_clean, 
                               family = poisson(link = "log"), 
                               zi = ~ location)

### Two checks specifically for a generalize linear approach
simulateResiduals(model_zip_location ,plot = TRUE) 
testDispersion(model_zip_location )
check_model(model_zip_location) #Perfect, preditions match real data

summary(model_zip_location)
VarCorr(model_zip_location )
outlier_test <- testOutliers(model_zip_location, type = "bootstrap")
```

###Glmm zero-inflated negative bionomial (mowing)

```{r}
# Run a Zero-Inflated Negative Binomial model
model_zinb<- glmmTMB(seed_number_foot ~ mowing + (1|location:block),  
                       data = weed_seeds_clean, 
                       family = nbinom2(link = "log"), 
                       zi = ~ mowing)

### Two checks specifically for a generalize linear approach
simulateResiduals(model_zinb ,plot = TRUE) 
testDispersion(model_zinb )
check_model(model_zinb) #Perfect, preditions match real data

summary(model_zinb)

outlier_test <- testOutliers(model_zinb, type = "bootstrap")
```


#### Joint test (anova)
```{r}
model_zinb |> 
  joint_tests() |> 
  kable()  
```

#### Anova table
```{r}
options(contrasts = c("contr.sum", "contr.poly"))
Anova(model_zinb, type = 3)
```

#### Compact letter display
##### Weed control (Significant)

```{r}

tukey_mowing <- emmeans(model_zinb, list(pairwise ~ mowing), adjust = "tukey")
tukey_mowing

cld_mowing_tukey <- cld(emmeans(model_zinb, ~ mowing), adjust = "tukey", Letters = letters, sort = TRUE, reversed = TRUE)

cld_mowing_tukey

fisher_mowing <-cld(emmeans(model_zinb, ~  mowing, type = "response"), Letters = letters,adjust = "none", sort = TRUE, reversed=TRUE)
fisher_mowing



```
##### Location (Significant)

```{r}

tukey_location <- emmeans(model_zinb, list(pairwise ~ location), adjust = "tukey")
tukey_location

cld_location_tukey <- cld(emmeans(model_zinb, ~ location), adjust = "tukey", Letters = letters, sort = TRUE, reversed = TRUE)

cld_location_tukey


```

##### Location:location (Significant)

```{r}

tukey_mowing_location <- emmeans(model_zinb, list(pairwise ~ mowing|location), adjust = "tukey")
tukey_mowing_location

cld_mowing_location_tukey <- cld(emmeans(model_zinb, ~ mowing|location), adjust = "tukey", Letters = letters, sort = TRUE, reversed = TRUE)

cld_mowing_location_tukey


```

##FARMHUB REPORT
### Glmm Poisson
```{r}

model_poisson_fh <- glmmTMB(seed_number_meter ~ mowing  + (1|site_year:block),  
                         data = weed_seeds_clean_fh, 
                         family = poisson(link = "log"))

###It assumes that mowing effects may vary by block, in addition to site-year and block-level variation.
#This would be useful if you suspect that mowing impacts weed biomass differently in different blocks.
#The model accounts for hierarchical structure down to the mowing level within blocks.

### Two checks specifically for a generalize linear approach
simulateResiduals(model_poisson_fh,plot = TRUE) 
testDispersion(model_poisson_fh )
check_model(model_poisson_fh ) #Perfect, preditions match real data

summary(model_poisson_fh )
VarCorr(model_poisson_fh )
outlier_test <- testOutliers(model_poisson_fh, type = "bootstrap")


```
###Glmm negative binomial
```{r}
model_nbinom_fh<- glmmTMB(seed_number_meter ~ mowing + (1|site_year:block),  
                        data = weed_seeds_clean_fh, 
                        family = nbinom2(link = "log"))

### Two checks specifically for a generalize linear approach
simulateResiduals(model_nbinom_fh ,plot = TRUE) 
testDispersion(model_nbinom_fh)
check_model(model_nbinom_fh ) #Perfect, preditions match real data

summary(model_nbinom_fh )
VarCorr(model_nbinom_fh )
outlier_test <- testOutliers(model_nbinom_fh, type = "bootstrap")
```
###Glmm Zero-inflated Poisson (mowing)
```{r}
model_zip_fh <- glmmTMB(seed_number_meter ~ mowing + (1|site_year:block),  
                     data = weed_seeds_clean_fh, 
                     family = poisson(link = "log"), 
                     zi = ~ mowing)  # Zero inflation part modeled by 'mowing'

### Two checks specifically for a generalize linear approach
simulateResiduals(model_zip_fh ,plot = TRUE) 
testDispersion(model_zip_fh )
check_model(model_zip_fh) #Perfect, preditions match real data

summary(model_zip_fh)
VarCorr(model_zip_fh)
outlier_test <- testOutliers(model_zip_fh, type = "bootstrap")
```
###Glmm zero-inflated negative bionomial (mowing)

```{r}
# Run a Zero-Inflated Negative Binomial model
model_zinb_fh<- glmmTMB(seed_number_meter ~ mowing+ (1|site_year:block),  
                       data = weed_seeds_clean_fh, 
                       family = nbinom2(link = "log"), 
                       zi = ~ mowing)

### Two checks specifically for a generalize linear approach
simulateResiduals(model_zinb_fh ,plot = TRUE) 
testDispersion(model_zinb_fh )
check_model(model_zinb_fh) #Perfect, preditions match real data

summary(model_zinb_fh)

outlier_test <- testOutliers(model_zinb_fh, type = "bootstrap")
```

#### Joint test (anova)
```{r}
model_zinb_fh |> 
  joint_tests() |> 
  kable()  
```

#### Anova table
```{r}
options(contrasts = c("contr.sum", "contr.poly"))
Anova(model_zinb_fh, type = 3)
```

#### Fisher compact letter display
##### Weed control (Significant)

```{r}
cld_mowing_fisher_fh <-cld(emmeans(model_zinb_fh, ~  mowing, type = "response"), Letters = letters,adjust = "none", sort = TRUE, reversed=TRUE)
cld_mowing_fisher_fh


```

#Figures
##ECOBEAN
### Mowing (Significant)


```{r message=FALSE}
weed_seeds_clean |> 
  left_join(fisher_mowing ) |> 
  ggplot(aes(x = factor(mowing, levels = c("NWC", "EWC", "LWC", "AWC")), y = response, fill = mowing)) +
  #stat_summary(geom = "bar", fun = "mean", width = 0.7) +
  #stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2) +
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5) +
  geom_bar(stat="identity", position=position_dodge()) + 
  geom_errorbar(aes(ymin=response-SE, ymax=response+SE), width=.2,
                 position=position_dodge(.9))+
geom_text(aes(label = trimws(.group), y = response + (SE + )), size = 7) +
  labs(
    x = "",
      y = expression("Seed density" ~ (seeds/ft^{2})),
    #title = str_c("Influence of interrow weed control on weed biomass"),
    subtitle = expression(italic("P < 0.005"))) +
  
  scale_x_discrete(labels = c("No\nmowing", "Early\nmowing", "Late\nmowing", "As-needed\nmowing")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_WB_d(name = "BlueberriesForSal", direction = 1) +
   theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 12),
    axis.title = element_text(size = 24),  # Increase font size of axis titles
    axis.text = element_text(size = 24),   # Increase font size of axis labels
    plot.title = element_text(size = 24, face = "bold"),  # Increase font size of title
    plot.subtitle = element_text(size = 24, face = "italic")  # Increase font size of subtitle
  )
ggsave("weed_seeds_mowing_foot_eco.png", width = 10, height = 8, dpi = 300)
```


##FARMHUB REPORT
### Mowing (Significant)


```{r message=FALSE}
weed_seeds_clean_fh |> 
  left_join(cld_mowing_fisher_fh) |> 
  ggplot(aes(x = factor(mowing, levels = c("NWC", "EWC", "LWC", "AWC")), y = response, fill = mowing)) +
  #stat_summary(geom = "bar", fun = "mean", width = 0.7) +
  #stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2) +
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5) +
  geom_bar(stat="identity", position=position_dodge()) + 
  geom_errorbar(aes(ymin=response-SE, ymax=response+SE), width=.2,
                 position=position_dodge(.9))+
geom_text(aes(label = trimws(.group), y = response + (SE + 26)), size = 7) +
  labs(
    x = "",
     y = expression("Seed density" ~ (seeds~m^{-2})),
    #title = str_c("Influence of interrow weed control on weed biomass"),
    subtitle = expression(italic("P < 0.05"))) +
  
  scale_x_discrete(labels = c("No\nmowing", "Early\nmowing", "Late\nmowing", "As-needed\nmowing")) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3))) +
  scale_fill_WB_d(name = "BlueberriesForSal", direction = 1) +
   theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 12),
    axis.title = element_text(size = 24),  # Increase font size of axis titles
    axis.text = element_text(size = 24),   # Increase font size of axis labels
    plot.title = element_text(size = 24, face = "bold"),  # Increase font size of title
    plot.subtitle = element_text(size = 24, face = "italic")  # Increase font size of subtitle
  )
ggsave("weed_seeds_mowing_meter_fh.png", width = 10, height = 8, dpi = 300)
```