---
title: "Inter Row Mowing Analysis - Weed Biomass"
author: "Eric Youngerman"
date: "2024-02-15"
output: html_document
---


#LIBRARY 
```{r}
setwd("/Users/ey239/Library/CloudStorage/Box-Box/ECOBEAN/EXPERIMENTS/Interrow Mowing Trial/IMT 2023/R analysis")

#Load packages 

install.packages("patchwork")
library(readxl)
library(lme4)
library(lmerTest)
library(emmeans)
library(ggplot2)
library(viridis)
library(rstatix)
library(Matrix)
library(multcomp)
library(multcompView)
library(ggResidpanel)
library(tidyverse)
library(car)
library(glmmTMB)
library(DHARMa)
library(patchwork)
library(gt)
library(dplyr)
MeanPlusSe<-function(x) mean(x)+plotrix::std.error(x)
#find the value to add to x before ln(x)

find_logw0=function(x){c=trunc(log(min(x[x>0],na.rm=T)))
d=exp(c)
return(d)}
```
#LOAD and CLEAN DATA
```{r}
#Load data
#Farmhub
M_SW.FH <- read_excel("~/Library/CloudStorage/Box-Box/ECOBEAN/EXPERIMENTS/Interrow Mowing Trial/IMT 2023/R analysis/FH_IMT_RDATA.2023.xlsx", 
    sheet = "m_sw")

M_SW.FH<- M_SW.FH %>% rename('Mowing'= TRT)
M_SW.FH<- M_SW.FH %>% rename('Weeds'= MICROPLOT)


# Here is the easiest way to to recode to factors. There are shortcuts in tidyverse for situations where you have way more columns to deal with. You can copy and paste this code, and change the "factor" bit to "numeric" or "character" or "POSIX" (ie time series) as needed.

M_SW.FH$Mowing <- as.factor(M_SW.FH$Mowing)
M_SW.FH$BLOCK <- as.factor(M_SW.FH$BLOCK)
M_SW.FH$PLOT <- as.factor(M_SW.FH$PLOT)
M_SW.FH$Weeds <- as.factor(M_SW.FH$Weeds)

#Cornell 
#Load data
M_SW.CU <- read_excel("~/Library/CloudStorage/Box-Box/ECOBEAN/EXPERIMENTS/Interrow Mowing Trial/IMT 2023/R analysis/CU_IMT_RDATA.2023.xlsx", 
    sheet = "m_sw")

M_SW.CU<- M_SW.CU %>% rename('Mowing'= TRT)
M_SW.CU<- M_SW.CU %>% rename('Weeds'= MICROPLOT)

M_SW.CU$Mowing <- as.factor(M_SW.CU$Mowing)
M_SW.CU$BLOCK <- as.factor(M_SW.CU$BLOCK)
M_SW.CU$PLOT <- as.factor(M_SW.CU$PLOT)
M_SW.CU$Weeds <- as.factor(M_SW.CU$Weeds)

#Vermont
#Load data
M_SW.VT <- read_excel("~/Library/CloudStorage/Box-Box/ECOBEAN/EXPERIMENTS/Interrow Mowing Trial/IMT 2023/R analysis/VT_IMT_RDATA.2023.xlsx", 
    sheet = "m_sw")

M_SW.VT<- M_SW.VT %>% rename('Mowing'= TRT)
M_SW.VT<- M_SW.VT %>% rename('Weeds'= MICROPLOT)

M_SW.VT$Mowing <- as.factor(M_SW.VT$Mowing)
M_SW.VT$BLOCK <- as.factor(M_SW.VT$BLOCK)
M_SW.VT$PLOT <- as.factor(M_SW.VT$PLOT)
M_SW.VT$Weeds <- as.factor(M_SW.VT$Weeds)

#Wisconsin
#Load data
M_SW.WI <- read_excel("~/Library/CloudStorage/Box-Box/ECOBEAN/EXPERIMENTS/Interrow Mowing Trial/IMT 2023/R analysis/WI_IMT_RDATA.2023.xlsx", 
    sheet = "m_sw")

M_SW.WI<- M_SW.WI %>% rename('Mowing'= TRT)
M_SW.WI<- M_SW.WI %>% rename('Weeds'= MICROPLOT)

M_SW.WI$Mowing <- as.factor(M_SW.WI$Mowing)
M_SW.WI$BLOCK <- as.factor(M_SW.WI$BLOCK)
M_SW.WI$PLOT <- as.factor(M_SW.WI$PLOT)
M_SW.WI$Weeds <- as.factor(M_SW.WI$Weeds)

#MAINE
#Load data
M_SW.ME <- read_excel("~/Library/CloudStorage/Box-Box/ECOBEAN/EXPERIMENTS/Interrow Mowing Trial/IMT 2023/R analysis/ME_IMT_RDATA.2023.xlsx", 
    sheet = "m_sw")

M_SW.ME<- M_SW.ME %>% rename('Mowing'= TRT)
M_SW.ME<- M_SW.ME %>% rename('Weeds'= MICROPLOT)

M_SW.ME$Mowing <- as.factor(M_SW.ME$Mowing)
M_SW.ME$BLOCK <- as.factor(M_SW.ME$BLOCK)
M_SW.ME$PLOT <- as.factor(M_SW.ME$PLOT)
M_SW.ME$Weeds <- as.factor(M_SW.ME$Weeds)

#Combine all data

M_SW.ALL <- bind_rows(M_SW.CU, M_SW.FH, M_SW.VT, M_SW.WI, M_SW.ME)

M_SW.ALL$Mowing <- as.factor(M_SW.ALL$Mowing)
M_SW.ALL$BLOCK <- as.factor(M_SW.ALL$BLOCK)
M_SW.ALL$PLOT <- as.factor(M_SW.ALL$PLOT)
M_SW.ALL$Weeds <- as.factor(M_SW.ALL$Weeds)

#Combine all sites, No Maine

M_SW.ALLNM <- bind_rows(M_SW.CU, M_SW.FH, M_SW.VT, M_SW.WI)

M_SW.ALLNM$Mowing <- as.factor(M_SW.ALLNM$Mowing)
M_SW.ALLNM$BLOCK <- as.factor(M_SW.ALLNM$BLOCK)
M_SW.ALLNM$PLOT <- as.factor(M_SW.ALLNM$PLOT)
M_SW.ALLNM$Weeds <- as.factor(M_SW.ALLNM$Weeds)

```

#LEVENE'S TEST
```{r}
leveneTest((WBM1) ~ LOC, data = M_SW.ALL)
#Levene's test was significant so sites should be analyzed separately
#2.25e-05 

#Graph and check out residuals

```
#MODEL TESTING
##Pooled sites 
###LOC Fixed, LogFullWbmMod1Fix_ALL1

```{r}

FullWbmMod1Fix_ALL <- lmer(WBM1 ~  LOC*Mowing*Weeds + (1|LOC:BLOCK) +(1|LOC:BLOCK:Mowing) , data = M_SW.ALL)

summary(FullWbmMod1Fix_ALL)

#Three way random effect interaction has 0 variance, can be exluded from model

FullWbmMod1Fix_ALL1 <- lmer(WBM1 ~  LOC*Mowing*Weeds + (1|LOC:BLOCK) , data = M_SW.ALL)

summary(FullWbmMod1Fix_ALL1)

find_logw0(M_SW.ALL$WBM1)
#0.3678794

LogFullWbmMod1Fix_ALL1 <- lmer(log(WBM1+0.3678794) ~  LOC*Mowing*Weeds + (1|LOC:BLOCK) , data = M_SW.ALL)

summary(LogFullWbmMod1Fix_ALL1)
```
###LOC random, LogFullWbmMod1Ran_ALL
```{r}
#####LOC is Random
 
FullWbmMod1Ran_ALL <- lmer(WBM1 ~  Mowing*Weeds +(1+Mowing+Weeds+Mowing:Weeds|LOC) +(1|LOC)+ (1|LOC:BLOCK) , data = M_SW.ALL)

summary(FullWbmMod1Ran_ALL)

#Data sets need to be transformed

find_logw0(M_SW.ALL$WBM1)
#0.3678794


LogFullWbmMod1Ran_ALL <- lmer(log(WBM1+0.3679794) ~  Mowing*Weeds +(1+Mowing+Weeds+Mowing:Weeds|LOC) +(1|LOC)+ (1|LOC:BLOCK) , data = M_SW.ALL)

summary(LogFullWbmMod1Ran_ALL)
```
###Residuals
```{r}

##comparison of models with log transformation
list(FullWbmMod1Fix_ALL1 , FullWbmMod1Ran_ALL, LogFullWbmMod1Fix_ALL1, LogFullWbmMod1Ran_ALL ) %>%
  lapply(resid_panel, qqbands = TRUE, nrow=2) %>%
  wrap_plots() +
  plot_annotation(tag_levels = "A")

# LogFullWbmMod1Fix_ALL1 and LogFullWbmMod1Ran_ALL have best residuals
```

## Farm hub,  LogFullWbmMod1Fix_FH

```{r}

#lmer

#Block is Fixed, 
#Block was included in all models as a fixed factor because blocks were used to control the different field conditions across sections, and thus to reduce variance between eu's

FullWbmMod1Fix_FH <- lmer(WBM1 ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing)  , data = M_SW.FH)

#Block is Random
FullWbmMod1Ran_FH <- lmer(WBM1 ~ Mowing*Weeds + (1|BLOCK) + (1|BLOCK:Mowing)  , data = M_SW.FH)

find_logw0(M_SW.FH$WBM1)
# = 1

#Logged, Block is Fixed
LogFullWbmMod1Fix_FH <- lmer(log(WBM1 + 1) ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing)  , data = M_SW.FH)

#Logged, Block is Random
LogFullWbmMod1Ran_FH <- lmer(log(WBM1 + 1) ~ Mowing*Weeds + (1|BLOCK) + (1|BLOCK:Mowing)  , data = M_SW.FH)

##comparison of models with and without log transformation
list(FullWbmMod1Fix_FH , FullWbmMod1Ran_FH, LogFullWbmMod1Fix_FH,LogFullWbmMod1Ran_FH ) %>%
  lapply(resid_panel, qqbands = TRUE, nrow=2) %>%
  wrap_plots() +
  plot_annotation(tag_levels = "A")

# LogFullWbmMod1Fix_FH has better residuals
```
##Cornell, LogFullWbmMod1Fix_CU
```{r}

#lmer
#Block is Fixed, 
#Block was included in all models as a fixed factor because blocks were used to control the different field conditions across sections, and thus to reduce variance between eu's

FullWbmMod1Fix_CU <- lmer(WBM1 ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing)  , data = M_SW.CU)

#Block is Random
FullWbmMod1Ran_CU <- lmer(WBM1 ~ Mowing*Weeds + (1|BLOCK) + (1|BLOCK:Mowing)  , data = M_SW.CU)

find_logw0(M_SW.CU$WBM1)
# = 7.389056

#Logged, Block is Fixed
LogFullWbmMod1Fix_CU <- lmer(log(WBM1 + 7.389056) ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing)  , data = M_SW.CU)

#Logged, Block is Random
LogFullWbmMod1Ran_CU <- lmer(log(WBM1 + 7.389056) ~ Mowing*Weeds + (1|BLOCK) + (1|BLOCK:Mowing)  , data = M_SW.CU)

##comparison of models with and without log transformation
list(FullWbmMod1Fix_CU , FullWbmMod1Ran_CU, LogFullWbmMod1Fix_CU,LogFullWbmMod1Ran_CU ) %>%
  lapply(resid_panel, qqbands = TRUE, nrow=2) %>%
  wrap_plots() +
  plot_annotation(tag_levels = "A")

# LogFullWbmMod1Fix_CU has better residuals

```

##Vermont, LogFullWbmMod1Fix_VT

```{r}
#lmer
#Block is Fixed, 
#Block was included in all models as a fixed factor because blocks were used to control the different field conditions across sections, and thus to reduce variance between eu's

FullWbmMod1Fix_VT <- lmer(WBM1 ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing)  , data = M_SW.VT)

#Block is Random
FullWbmMod1Ran_VT <- lmer(WBM1 ~ Mowing*Weeds + (1|BLOCK) + (1|BLOCK:Mowing)  , data = M_SW.VT)

find_logw0(M_SW.VT$WBM1)
# =  0.3678794

#Logged, Block is Fixed
LogFullWbmMod1Fix_VT<- lmer(log(WBM1 +  0.3678794) ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing)  , data = M_SW.VT)

#Logged, Block is Random
LogFullWbmMod1Ran_VT <- lmer(log(WBM1 +  0.3678794) ~ Mowing*Weeds + (1|BLOCK) + (1|BLOCK:Mowing)  , data = M_SW.VT)

##comparison of models with and without log transformation
list(FullWbmMod1Fix_VT , FullWbmMod1Ran_VT, LogFullWbmMod1Fix_VT,LogFullWbmMod1Ran_VT ) %>%
  lapply(resid_panel, qqbands = TRUE, nrow=2) %>%
  wrap_plots() +
  plot_annotation(tag_levels = "A")

# LogFullWbmMod1Fix_VT has better residuals
```
##Wisconsin, LogFullWbmMod1Fix_WI
```{r}

#lmer
#Block is Fixed, 
#Block was included in all models as a fixed factor because blocks were used to control the different field conditions across sections, and thus to reduce variance between eu's

FullWbmMod1Fix_WI <- lmer(WBM1 ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing)  , data = M_SW.WI)

#Block is Random
FullWbmMod1Ran_WI <- lmer(WBM1 ~ Mowing*Weeds + (1|BLOCK) + (1|BLOCK:Mowing)  , data = M_SW.WI)

find_logw0(M_SW.WI$WBM1)
# =  1

#Logged, Block is Fixed
LogFullWbmMod1Fix_WI<- lmer(log(WBM1 + 1) ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing)  , data = M_SW.WI)

#Logged, Block is Random
LogFullWbmMod1Ran_WI <- lmer(log(WBM1 +  1) ~ Mowing*Weeds + (1|BLOCK) + (1|BLOCK:Mowing)  , data = M_SW.WI)

##comparison of models with and without log transformation
list(FullWbmMod1Fix_WI , FullWbmMod1Ran_WI, LogFullWbmMod1Fix_WI,LogFullWbmMod1Ran_WI ) %>%
  lapply(resid_panel, qqbands = TRUE, nrow=2) %>%
  wrap_plots() +
  plot_annotation(tag_levels = "A")

# FullWbmMod1Fix_WI has better residuals

```
##Maine, LogFullWbmMod1Fix_ME
```{r}
#lmer
#Block is Fixed, 
#Block was included in all models as a fixed factor because blocks were used to control the different field conditions across sections, and thus to reduce variance between eu's

FullWbmMod1Fix_ME <- lmer(WBM1 ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing)  , data = M_SW.ME)

#Block is Random
FullWbmMod1Ran_ME <- lmer(WBM1 ~ Mowing*Weeds + (1|BLOCK) + (1|BLOCK:Mowing)  , data = M_SW.ME)

find_logw0(M_SW.ME$WBM1)
# =  7.389056

#Logged, Block is Fixed
LogFullWbmMod1Fix_ME<- lmer(log(WBM1 + 7.389056) ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing)  , data = M_SW.ME)

#Logged, Block is Random
LogFullWbmMod1Ran_ME <- lmer(log(WBM1 + 7.389056) ~ Mowing*Weeds + (1|BLOCK) + (1|BLOCK:Mowing)  , data = M_SW.ME)

##comparison of models with and without log transformation
list(FullWbmMod1Fix_ME , FullWbmMod1Ran_ME, LogFullWbmMod1Fix_ME,LogFullWbmMod1Ran_ME ) %>%
  lapply(resid_panel, qqbands = TRUE, nrow=2) %>%
  wrap_plots() +
  plot_annotation(tag_levels = "A")
# LogFullWbmMod1Fix_ME has better residuals

```
#ANOVA
##Pooled Sites
###LOC Fixed, LogFullWbmMod1Fix_ALL1
```{r}
list( LogFullWbmMod1Fix_ALL1) %>%
setNames(c("All Sites"))%>%
  lapply(joint_tests)
```

###Anova table
```{r}
#Make a table of anova
# Step 1: Create a data frame from your results
results <- data.frame(
  Model_Term = c("LOC", "Mowing", "Weeds", "LOC:Mowing", "LOC:Weeds", "Mowing:Weeds", "LOC:Mowing:Weeds"),
  df1 = c(4, 3, 1, 12, 4, 3, 12),
  df2 = c(15, 105, 105, 105, 105, 105, 105),
  F_ratio = c(12.814, 7.006, 107.670, 1.421, 20.644, 2.637, 0.812),
  p_value = c(0.0001, 0.0002, "<.0001", 0.1680, "<.0001", 0.0535, 0.6374)
)

# Step 2: Format the data frame using gt
AnovaWB1table_gt <- gt(results) %>%
  tab_header(
    title = "ANOVA results", 
    subtitle = "Model = lmer(log(WBM1+0.3678794) ~  LOC*Mowing*Weeds + (1|LOC:BLOCK) , data = M_SW.ALL)"
  ) %>%
  cols_label(
    Model_Term = "Model Term",
    df1 = "df1",
    df2 = "df2",
    F_ratio = "F Ratio",
    p_value = "p Value"
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "black", weight = px(1)),
    locations = cells_body()
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "black", weight = px(2)),
    locations = list(
      cells_title(groups = "title"),
      cells_title(groups = "subtitle"),
      cells_column_labels()
    )
  ) %>%
  tab_options(
    table.border.top.width = px(2),
    table.border.top.color = "black",
    table.border.bottom.width = px(2),
    table.border.bottom.color = "black"
  )
AnovaWB1table_gt

# Step 3: Save the table as an image
gtsave(AnovaWB1table_gt, "Anova table weed biomass")
```

###LOC Random, LogFullWbmMod1Ran_ALL
```{r}
list(LogFullWbmMod1Ran_ALL) %>%
setNames(c("All Sites"))%>%
  lapply(joint_tests)
```
###Anova table
```{r}
#Make a table of anova
# Step 1: Create a data frame from your results
results1 <- data.frame(
  Model_Term = c("Mowing", "Weeds", "Mowing:Weeds"),
  df1 = c(3, 1, 3),
  df2 = c(4, 4, 4),
  F_ratio = c(4.218,  5.200 , 1.856),
  p_value = c(0.0991,  0.0848,  0.2776)
)


# Step 2: Format the data frame using gt
AnovaBEANYD2table_gt <- gt(results1) %>%
  tab_header(
    title = "ANOVA results", 
    subtitle = "Model = lmer(log(WBM1+0.3679794) ~  Mowing*Weeds +(1+Mowing+Weeds+Mowing:Weeds|LOC) +(1|LOC)+ (1|LOC:BLOCK) , data = M_SW.ALL)"
  ) %>%
  cols_label(
    Model_Term = "Model Term",
    df1 = "df1",
    df2 = "df2",
    F_ratio = "F Ratio",
    p_value = "p Value"
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "black", weight = px(1)),
    locations = cells_body()
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "black", weight = px(2)),
    locations = list(
      cells_title(groups = "title"),
      cells_title(groups = "subtitle"),
      cells_column_labels()
    )
  ) %>%
  tab_options(
    table.border.top.width = px(2),
    table.border.top.color = "black",
    table.border.bottom.width = px(2),
    table.border.bottom.color = "black"
  )
AnovaWB2table_gt

# Step 3: Save the table as an image
gtsave(AnovaWB2table_gt, "Anova table weed biomass2.png")
```
##Separated Sites, 
###BLOCK Fixed
```{r}
list(LogFullWbmMod1Fix_FH, LogFullWbmMod1Fix_CU, LogFullWbmMod1Fix_VT, LogFullWbmMod1Fix_WI,LogFullWbmMod1Fix_ME) %>%
setNames(c("Farm hub", "Cornell", "Vermont", "Wisconsin", "Maine"))%>%
  lapply(joint_tests)
joint_tests(LogFullWbmMod1Fix_ME)

```

#MEANs Comparison
##Pooled Sites
###LOC Fixed, LogFullWbmMod1Fix_ALL1
```{r}
summary(LogFullWbmMod1Fix_ALL1)
```

```{r}
joint_tests(LogFullWbmMod1Fix_ALL1)
```

```{r}
PooledMeansFix1<-list(LogFullWbmMod1Fix_ALL1) %>%
setNames(c("All Sites"))%>%
 #map(emmeans, pairwise~LOC, type = "response") 
 #map(emmeans, pairwise~Mowing, type = "response") 
 map(emmeans, pairwise~Weeds, type = "response") 
 #map(emmeans, pairwise ~Mowing|LOC, type = "response") 
 #map(emmeans, pairwise~Weeds|LOC, type = "response") 
 # map(emmeans, pairwise~Mowing|Weeds, type = "response") 
PooledMeansFix1
```
###LOC Random, LogFullWbmMod1Ran_ALL
```{r}
summary(LogFullWbmMod1Ran_ALL)
```

```{r}
joint_tests(LogFullWbmMod1Ran_ALL)
```

```{r}
PooledMeansRan1<-list(LogFullWbmMod1Ran_ALL) %>%
setNames(c("All Sites"))%>%
 #map(emmeans, pairwise~ Mowing , type = "response") 
 map(emmeans, pairwise~ Weeds , type = "response") 
PooledMeansRan1
```
##Individual Sites
###BLOCK Fixed
```{r}

SeparateMeans <- list(LogFullWbmMod1Fix_FH, LogFullWbmMod1Fix_CU, LogFullWbmMod1Fix_VT, LogFullWbmMod1Fix_WI,LogFullWbmMod1Fix_ME) %>%
setNames(c("Farm hub", "Cornell", "Vermont", "Wisconsin", "Maine"))%>%
  #map(emmeans, pairwise~ Weeds | Mowing , type = "response") 

 map(emmeans, pairwise~ Mowing| Weeds , type = "response") 
SeparateMeans
```

#FIGURES
##Pooled Sites
###LOC Fixed, LogFullWbmMod1Fix_ALL1

```{r}
summary(LogFullWbmMod1Fix_ALL1)
```

```{r}
joint_tests(LogFullWbmMod1Fix_ALL1)
```
####CLD
```{r}

#Fisher's method for comparing means
#Mowing
cld.LogFullWbmMod1Fix_ALL <-cld(emmeans(LogFullWbmMod1Fix_ALL1, ~ Mowing, type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)

#Mowing|LOC
cld.LogFullWbmMod1Fix_ALL1 <-cld(emmeans(LogFullWbmMod1Fix_ALL1, ~ Mowing|LOC,type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)

#Mowing|Weeds
cld.LogFullWbmMod1Fix_ALL2 <-cld(emmeans(LogFullWbmMod1Fix_ALL1, ~ Mowing|Weeds,type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)

#Mowing|Weeds|LOC
cld.LogFullWbmMod1Fix_ALL3 <-cld(emmeans(LogFullWbmMod1Fix_ALL1, ~ Mowing|Weeds|LOC,type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)

#Weeds
cld.LogFullWbmMod1Fix_ALL4 <-cld(emmeans(LogFullWbmMod1Fix_ALL1, ~ Weeds, type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)

#Weeds|LOC
cld.LogFullWbmMod1Fix_ALL5 <-cld(emmeans(LogFullWbmMod1Fix_ALL1, ~ Weeds|LOC, type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)

```
####Mowing (Significant)
```{r}
cld.LogFullWbmMod1Fix_ALL <-cld(emmeans(LogFullWbmMod1Fix_ALL1, ~ Mowing, type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)


#Graphing

#png("WBMFix_ALL1.png", res = 300, units = "in", width = 5.2, height = 4)
#left_join(M_SW.ALL,
cld.LogFullWbmMod1Fix_ALL %>% 
ggplot(.,aes(Mowing, response, fill=Mowing)) +  
  #facet_wrap(~LOC, labeller = labeller(LOC = c("CU" = "Aurora, NY", "FH" = "Hurley, NY",   "ME"= "Orono, ME", "VT" = "Alburgh, VT", "WI" = "Arlington, WI"  ))) +
 # stat_summary(geom = "bar", fun = "mean") +
  #stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5)+
  geom_bar(stat="identity", 
           position=position_dodge()) + 
  geom_errorbar(aes(ymin=response-SE, ymax=response+SE), width=.2,
                 position=position_dodge(.9))+
 geom_text(aes(label = trimws(.group), size=6.5,y=response +(SE+1.5) )) +
  labs(x="Timing of Mowing", y=expression("Weed biomass"~(g~m^{-2})))+
  scale_x_discrete(labels = c("As-needed\nmowing","Early\nmowing","Late\nmowing","As-needed\nmowing",  "No\nmowing"))+
  scale_y_continuous(expand=expansion(mult = c(0.05, 0.3)))+
  scale_fill_viridis(discrete=TRUE, option="E", direction=-1,end=.9,begin=.1)+
  theme_bw()+
  theme(legend.position="none")

#dev.off()
```
####Mowing|LOC (Not Significant)
```{r}
cld.LogFullWbmMod1Fix_ALL1 <-cld(emmeans(LogFullWbmMod1Fix_ALL1, ~ Mowing|LOC,type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)

#Graphing

#png("WBMFix_ALL1LOC.png", res = 300, units = "in", width = 11, height = 4)
#left_join(M_SW.ALL,
cld.LogFullWbmMod1Fix_ALL1 %>% 
ggplot(.,aes(Mowing, response, fill=Mowing))+  
  facet_wrap(~LOC,ncol= 5, labeller = labeller(LOC = c("CU" = "Aurora, NY", "FH" = "Hurley, NY",   "ME"= "Orono, ME", "VT" = "Alburgh, VT", "WI" = "Arlington, WI"  ))) +
 # stat_summary(geom = "bar", fun = "mean") +
  #stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5)+
  geom_bar(stat="identity", 
           position=position_dodge()) + 
  geom_errorbar(aes(ymin=response-SE, ymax=response+SE), width=.2,
                 position=position_dodge(.9))+
 geom_text(aes(label = trimws(.group), size=6.5,y=response +(SE+5) )) +
  labs(x="Timing of Mowing", y=expression("Weed biomass"~(g~m^{-2})))+
  scale_x_discrete(labels = c("Early\nmowing","Late\nmowing","As-needed\nmowing",  "No\nmowing"))+
  scale_y_continuous(expand=expansion(mult = c(0.05, 0.2)))+
  scale_fill_viridis(discrete=TRUE, option="E", direction=-1,end=.9,begin=.1)+
  theme_bw()+
  theme(legend.position="none")
#dev.off()
```
####Mowing|Weeds (almost Significant)
```{r}

cld.LogFullWbmMod1Fix_ALL2 <-cld(emmeans(LogFullWbmMod1Fix_ALL1, ~ Mowing|Weeds,type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)
```
```{r}
#Graphing
#Using Fisher's method for comparing means with pooled site data and location as a fixed effect, Interaction between location and weeds is significant
png("WbmFix_ALL1Weeds.png", res = 300, units = "in", width = 5.2, height = 4)
#left_join(M_SW.ALL,
cld.LogFullWbmMod1Fix_ALL2 %>% 
ggplot(.,aes(Mowing, response, fill=Mowing))+  facet_wrap(~Weeds, labeller = labeller(Weeds = c("M" = "Ambient Weeds", "SW" = "Surrogate Weeds" ))) +
 # stat_summary(geom = "bar", fun = "mean") +
  #stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5)+
  geom_bar(stat="identity", 
           position=position_dodge()) + 
  geom_errorbar(aes(ymin=response-SE, ymax=response+SE), width=.2,
                 position=position_dodge(.9))+
 geom_text(aes(label = trimws(.group), size=6.5, y = response +(SE+5))) +
  labs(x="Timing of Mowing", y=expression("Weed biomass"~(g~m^{-2})))+
  scale_x_discrete(labels = c("Early\nmowing","Late\nmowing","As-needed\nmowing",  "No\nmowing"))+
  scale_y_continuous(expand=expansion(mult = c(0.05, 0.3)))+
  scale_fill_viridis(discrete=TRUE, option="E", direction=-1,end=.9,begin=.1)+
  theme_bw()+
  theme(legend.position="none")
dev.off()
```

####Mowing|Weeds|LOC (Not signficant)
```{r}
cld.LogFullWbmMod1Fix_ALL3 <-cld(emmeans(LogFullWbmMod1Fix_ALL1, ~ Mowing|Weeds|LOC,type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)

#Graphing

png("WBM.Mow.Weeds.LOC.png", res = 300, units = "in", width = 11, height = 4)
#left_join(M_SW.ALL,
cld.LogFullWbmMod1Fix_ALL3 %>% 
ggplot(aes(Mowing, response, fill=Mowing)) +  
  facet_grid(Weeds ~ LOC, labeller = labeller(
    LOC = c("CU" = "Aurora, NY", "FH" = "Hurley, NY", "ME" = "Orono, ME", "VT" = "Alburgh, VT", "WI" = "Arlington, WI"),
    Weeds = c("M" = "Ambient Weeds", "SW" = "Surrogate Weeds")
  )) +
              
 # stat_summary(geom = "bar", fun = "mean") +
  #stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5)+
  geom_bar(stat="identity", 
           position=position_dodge()) + 
  geom_errorbar(aes(ymin=response-SE, ymax=response+SE), width=.2,
                 position=position_dodge(.9))+
geom_text(aes(label = trimws(.group), size=6.5, y = response +(SE+25))) +
  labs(x="Timing of Mowing", y=expression("Weed biomass"~(g~m^{-2})))+
  scale_x_discrete(labels = c("As-needed\nmowing","Early\nmowing","Late\nmowing",  "No\nmowing"))+
  scale_y_continuous(expand=expansion(mult = c(0.05, 0.3)))+
  scale_fill_viridis(discrete=TRUE, option="E", direction=-1,end=.9,begin=.1)+
  theme_bw()+
  theme(legend.position="none")
dev.off()
```
####Weeds (Significant)
```{r}

cld.LogFullWbmMod1Fix_ALL4 <-cld(emmeans(LogFullWbmMod1Fix_ALL1, ~ Weeds, type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)
```
```{r}
#Graphing
#Using Fisher's method for comparing means with pooled site data and location as a fixed effect, interaction between 
#png("WbmFix_ALL4.png", res = 300, units = "in", width = 5.2, height = 4)
#left_join(M_SW.ALL,
cld.LogFullWbmMod1Fix_ALL4 %>% 
ggplot(.,aes(Weeds, response, fill=Weeds))+  #facet_wrap(~LOC, ncol= 5, labeller = labeller(LOC = c("CU" = "Aurora, NY", "FH" = "Hurley, NY", "ME"= "Orono, ME", "VT" = "Alburgh, VT", "WI" = "Arlington, WI"  ))) +
 # stat_summary(geom = "bar", fun = "mean") +
  #stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5)+
  geom_bar(stat="identity", 
           position=position_dodge()) + 
  geom_errorbar(aes(ymin=response-SE, ymax=response+SE), width=.2,
                 position=position_dodge(.9))+
 geom_text(aes(label = trimws(.group), size=6.5, y = response+(SE+3))) +
  labs(x="Weed Type", y=expression("Weed biomass"~(g~m^{-2})))+
  scale_x_discrete(labels = c("Ambient\n Weeds", "Surrogate\n Weeds"
                             ))+
scale_y_continuous(limits = c (0, 100)) + #expand=expansion(mult = c(0.05, 0.3)))+
  scale_fill_viridis(discrete=TRUE, option="E", direction=-1,end=.9,begin=.1)+
  theme_bw()+
  theme(legend.position="none")
#dev.off()


```
####Weeds|LOC (Significant)
```{r}

cld.LogFullWbmMod1Fix_ALL5 <-cld(emmeans(LogFullWbmMod1Fix_ALL1, ~ Weeds|LOC, type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)
```
```{r}
#Graphing
#Using Fisher's method for comparing means with pooled site data and location as a fixed effect, interaction between 
png("WbmFix_ALL5.png", res = 300, units = "in", width = 8, height = 4)
#left_join(M_SW.ALL,
cld.LogFullWbmMod1Fix_ALL5 %>% 
ggplot(.,aes(Weeds, response, fill=Weeds))+  facet_wrap(~LOC, ncol= 5, labeller = labeller(LOC = c("CU" = "Aurora, NY", "FH" = "Hurley, NY", "ME"= "Orono, ME", "VT" = "Alburgh, VT", "WI" = "Arlington, WI"  ))) +
 # stat_summary(geom = "bar", fun = "mean") +
  #stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5)+
  geom_bar(stat="identity", 
           position=position_dodge()) + 
  geom_errorbar(aes(ymin=response-SE, ymax=response+SE), width=.2,
                 position=position_dodge(.9))+
 geom_text(aes(label = trimws(.group), size=6.5, y = response+(SE+5))) +
  labs(x="Weed Type", y=expression("Weed biomass"~(g~m^{-2})))+
  scale_x_discrete(labels = c("Ambient\n Weeds", "Surrogate\n Weeds"
                             ))+
scale_y_continuous(expand=expansion(mult = c(0.05, 0.2)))+
  scale_fill_viridis(discrete=TRUE, option="E", direction=-1,end=.9,begin=.1)+
  theme_bw()+
  theme(legend.position="none")
dev.off()


```
###LOC Random, LogFullWbmMod1Ran_ALL
```{r}
#Tukey method for comparing means
cld.LogFullWbmMod1Ran_ALL <-cld(emmeans(LogFullWbmMod1Ran_ALL, ~ Mowing), Letters = letters, sort = FALSE, reversed = FALSE)

cld.LogFullWbmMod1Ran_ALL1 <-cld(emmeans(LogFullWbmMod1Ran_ALL, ~ Mowing|LOC), Letters = letters, sort = FALSE, reversed = FALSE)

cld.LogFullWbmMod1Ran_ALL2 <-cld(emmeans(LogFullWbmMod1Ran_ALL, ~ Mowing|LOC|Weeds), Letters = letters, sort = FALSE, reversed = FALSE)

#Fisher's method for comparing means, designated by b at end of  name
cld.LogFullWbmMod1Ran_ALLb <-cld(emmeans(LogFullWbmMod1Ran_ALL, ~ Mowing, type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)

cld.LogFullWbmMod1Ran_ALL1b <-cld(emmeans(LogFullWbmMod1Ran_ALL, ~ Weeds,type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)

cld.LogFullWbmMod1Ran_ALL2b <-cld(emmeans(LogFullWbmMod1Ran_ALL, ~ Mowing|Weeds, type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)

```
####Mowing
```{r}

#Graphing
#Using Fisher's method for comparing means with pooled site data and location as a fixed effect, Interaction between location and weeds is significant
#png("LogFullWbmMod1Fix_ALL1.png", res = 300, units = "in", width = 8, height = 4)
#left_join(M_SW.ALL,
cld.LogFullWbmMod1Ran_ALLb %>% 
ggplot(.,aes(Mowing, response, fill=Mowing))+  #facet_wrap(~LOC, labeller = labeller(LOC = c("CU" = "Aurora, NY", "FH" = "Hurley, NY", "ME"= "Orono, ME", "VT" = "Alburgh, VT", "WI" = "Arlington, WI"  ))) +
 # stat_summary(geom = "bar", fun = "mean") +
  #stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5)+
  geom_bar(stat="identity", 
           position=position_dodge()) + 
  geom_errorbar(aes(ymin=response-SE, ymax=response+SE), width=.2,
                 position=position_dodge(.9))+
 geom_text(aes(label = trimws(.group), size=6.5, y = response +(SE+2))) +
  labs(x="Timing of Mowing", y=expression("Weed biomass"~(g~m^{-2})))+
  scale_x_discrete(labels = c("Early\nmowing","Late\nmowing","As-needed\nmowing",  "No\nmowing"))+
  scale_y_continuous(expand=expansion(mult = c(0.05, 0.3)))+
  scale_fill_viridis(discrete=TRUE, option="E", direction=-1,end=.9,begin=.1)+
  theme_bw()+
  theme(legend.position="none")
#dev.off()

#png("LogFullWbmMod1Fix_ALL1.png", res = 300, units = "in", width = 8, height = 4)
#left_join(M_SW.ALL,
cld.LogFullWbmMod1Ran_ALLb %>% 
ggplot(.,aes(Mowing, response, fill=Mowing))+  #facet_wrap(~LOC, labeller = labeller(LOC = c("CU" = "Aurora, NY", "FH" = "Hurley, NY", "ME"= "Orono, ME", "VT" = "Alburgh, VT", "WI" = "Arlington, WI"  ))) +
 # stat_summary(geom = "bar", fun = "mean") +
  #stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5)+
  geom_bar(stat="identity", 
           position=position_dodge()) + 
  geom_errorbar(aes(ymin=response-SE, ymax=response+SE), width=.2,
                 position=position_dodge(.9))+
 geom_text(aes(label = trimws(.group), size=6.5, y = response +(SE+2))) +
  labs(x="Timing of Mowing", y=expression("Weed biomass"~(g~m^{-2})))+
  scale_x_discrete(labels = c("Early\nmowing","Late\nmowing","As-needed\nmowing",  "No\nmowing"))+
  scale_y_continuous(expand=expansion(mult = c(0.05, 0.3)))+
  scale_fill_viridis(discrete=TRUE, option="E", direction=-1,end=.9,begin=.1)+
  theme_bw()+
  theme(legend.position="none")
#dev.off()
```
####Weeds
```{r}
#Graphing
#Using Fisher's method for comparing means with pooled site data and location as a fixed effect, interaction between 
#png("LogFullWbmMod1Fix_ALL.png", res = 300, units = "in", width = 8, height = 4)
#left_join(M_SW.ALL,
cld.LogFullWbmMod1Ran_ALL1b %>% 
ggplot(.,aes(Weeds, response, fill=Weeds))+  #facet_wrap(~LOC, ncol= 5, labeller = labeller(LOC = c("CU" = "Aurora, NY", "FH" = "Hurley, NY", "ME"= "Orono, ME", "VT" = "Alburgh, VT", "WI" = "Arlington, WI"  ))) +
 # stat_summary(geom = "bar", fun = "mean") +
  #stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5)+
  geom_bar(stat="identity", 
           position=position_dodge()) + 
  geom_errorbar(aes(ymin=response-SE, ymax=response+SE), width=.2,
                 position=position_dodge(.9))+
 geom_text(aes(label = trimws(.group), size=6.5, y = response+(SE+8))) +
  labs(x="Weed level", y=expression("Weed biomass"~(g~m^{-2})))+
  scale_x_discrete(labels = c("Ambient\n Weeds", "Surrogate\n Weeds"
                             ))+
scale_y_continuous(limits = c (0, 100)) + #expand=expansion(mult = c(0.05, 0.3)))+
  scale_fill_viridis(discrete=TRUE, option="E", direction=-1,end=.9,begin=.1)+
  theme_bw()+
  theme(legend.position="none")
#dev.off()
```
####Mowing|Weeds
```{r}

#Graphing
#Using Fisher's method for comparing means with pooled site data and location as a fixed effect, Interaction between location and weeds is significant
png("LogFullWbmMod1Ran_ALL3.png", res = 300, units = "in", width = 9, height = 4)
#left_join(M_SW.ALL,
cld.LogFullWbmMod1Ran_ALL2b %>% 
ggplot(.,aes(Mowing, response, fill=Mowing))+  facet_wrap(~Weeds, labeller = labeller(Weeds = c("M" = "Ambient Weeds", "SW" = "Surrogate Weeds" ))) +
 # stat_summary(geom = "bar", fun = "mean") +
  #stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5)+
  geom_bar(stat="identity", 
           position=position_dodge()) + 
  geom_errorbar(aes(ymin=response-SE, ymax=response+SE), width=.2,
                 position=position_dodge(.9))+
 geom_text(aes(label = trimws(.group), size=6.5, y = response +(SE+6))) +
  labs(x="Timing of Mowing", y=expression("Weed biomass"~(g~m^{-2})))+
  scale_x_discrete(labels = c("Early\nmowing","Late\nmowing","As-needed\nmowing",  "No\nmowing"))+
  scale_y_continuous(expand=expansion(mult = c(0.05, 0.3)))+
  scale_fill_viridis(discrete=TRUE, option="E", direction=-1,end=.9,begin=.1)+
  theme_bw()+
  theme(legend.position="none")
dev.off()
```
