---
title: "IMT SEED Counds"
author: "Eric Youngerman"
date: "2024-05-20"
output: html_document
---

#LIBRARY 
```{r}
setwd("/Users/ey239/Library/CloudStorage/Box-Box/ECOBEAN/EXPERIMENTS/Interrow Mowing Trial/IMT 2023/R analysis")

#Load packages 

install.packages("patchwork")
library(readxl)
library(lme4)
library(lmerTest)
library(emmeans)
library(ggplot2)
library(viridis)
library(rstatix)
library(Matrix)
library(multcomp)
library(multcompView)
library(ggResidpanel)
library(tidyverse)
library(car)
library(glmmTMB)
library(DHARMa)
library(patchwork)
library(gt)
library(dplyr)
MeanPlusSe<-function(x) mean(x)+plotrix::std.error(x)
#find the value to add to x before ln(x)

find_logw0=function(x){c=trunc(log(min(x[x>0],na.rm=T)))
d=exp(c)
return(d)}
```
#LOAD and CLEAN DATA
```{r}
#Farmhub 
#Load data
at_yield.FH <- read_excel("~/Library/CloudStorage/Box-Box/ECOBEAN/EXPERIMENTS/Interrow Mowing Trial/IMT 2023/R analysis/FH_IMT_SD_RDATA.2023.xlsx", 
    sheet = "at_yield")


at_yield.FH<- at_yield.FH %>% rename('Mowing'= TRT)

at_yield.FH$Mowing <- as.factor(at_yield.FH$Mowing)
at_yield.FH$BLOCK <- as.factor(at_yield.FH$BLOCK)
at_yield.FH$PLOT <- as.factor(at_yield.FH$PLOT)
at_yield.FH$WEEK <- as.factor(at_yield.FH$WEEK)
at_yield.FH$DATE <- as.factor(at_yield.FH$DATE)
at_yield.FH$SEEDNUM <- as.factor(at_yield.FH$SEEDNUM)
at_yield.FH$SEEDNUM <-as.numeric(as.character(at_yield.FH$SEEDNUM))
summary(at_yield.FH)
```
```{r}
#Cornell 
#Load data
at_yield.CU <- read_excel("~/Library/CloudStorage/Box-Box/ECOBEAN/EXPERIMENTS/Interrow Mowing Trial/IMT 2023/R analysis/CU_IMT_SD_RDATA_2023.xlsx", 
    sheet = "at_yield")


at_yield.CU<- at_yield.CU %>% rename('Mowing'= TRT)

at_yield.CU$Mowing <- as.factor(at_yield.CU$Mowing)
at_yield.CU$BLOCK <- as.factor(at_yield.CU$BLOCK)
at_yield.CU$PLOT <- as.factor(at_yield.CU$PLOT)
at_yield.CU$WEEK <- as.factor(at_yield.CU$WEEK)
at_yield.CU$DATE <- as.factor(at_yield.CU$DATE)
at_yield.CU$SEEDNUM <- as.factor(at_yield.CU$SEEDNUM)
at_yield.CU$SEEDNUM <-as.numeric(as.character(at_yield.CU$SEEDNUM))
summary(at_yield.CU)
```
```{r}
#Vermont 
#Load data
at_yield.VT <- read_excel("~/Library/CloudStorage/Box-Box/ECOBEAN/EXPERIMENTS/Interrow Mowing Trial/IMT 2023/R analysis/VT_IMT_SD_RDATA.2023.xlsx", 
    sheet = "at_yield")


at_yield.VT<- at_yield.VT %>% rename('Mowing'= TRT)

at_yield.VT$Mowing <- as.factor(at_yield.VT$Mowing)
at_yield.VT$BLOCK <- as.factor(at_yield.VT$BLOCK)
at_yield.VT$PLOT <- as.factor(at_yield.VT$PLOT)
at_yield.VT$WEEK <- as.factor(at_yield.VT$WEEK)
at_yield.VT$DATE <- as.factor(at_yield.VT$DATE)
at_yield.VT$SEEDNUM <- as.factor(at_yield.VT$SEEDNUM)
at_yield.VT$SEEDNUM <-as.numeric(as.character(at_yield.VT$SEEDNUM))
summary(at_yield.VT)
```
```{r}
#All Sites
#Combine all data

at_yield.ALL <- bind_rows(at_yield.FH,at_yield.CU, at_yield.VT )
at_yield.ALL$LOC <- as.factor(at_yield.ALL$LOC)
at_yield.ALL$Mowing <- as.factor(at_yield.ALL$Mowing)
at_yield.ALL$BLOCK <- as.factor(at_yield.ALL$BLOCK)
at_yield.ALL$PLOT <- as.factor(at_yield.ALL$PLOT)
 
#Assuming your dataset is named at_yield.ALL
conversion_factor <- 1333333

at_yield.ALL$SEEDNUM_per_hectare <- at_yield.ALL$SEEDNUM * conversion_factor
at_yield.ALL$SEEDNUM_per_hectare <- round(at_yield.ALL$SEEDNUM * conversion_factor)



summary(at_yield.ALL)
```

```{r}
#Farmhub
summarized_data.FH <- at_yield.FH %>%
  group_by(Mowing) %>%
  summarize(total_seeds = sum(SEEDNUM, na.rm = TRUE))
print(summarized_data.FH)
```

```{r}
#Cornell
summarized_data.CU <- at_yield.CU %>%
  group_by(Mowing) %>%
  summarize(total_seeds = sum(SEEDNUM, na.rm = TRUE))
print(summarized_data.CU)
```
```{r}
#Vermont
summarized_data.VT <- at_yield.VT %>%
  group_by(Mowing) %>%
  summarize(total_seeds = sum(SEEDNUM, na.rm = TRUE))
print(summarized_data.VT)

```
```{r}
#All
summarized_data.ALL <- at_yield.ALL %>%
  group_by(Mowing) %>%
  summarize(total_seeds = sum(SEEDNUM, na.rm = TRUE))
print(summarized_data.ALL)

```


#MODEL TESTING
###LMER
####LOC Fixed, LogFullat_yieldFIX.ALL
```{r}

Fullat_yieldFIX.ALL <- lmer(SEEDNUM ~  LOC*Mowing + (1|LOC:BLOCK) +(1|LOC:BLOCK:Mowing) , data = at_yield.ALL)

summary(Fullat_yieldFIX.ALL)

#Three way random effect interaction has 0 variance, can be excluded from model

Fullat_yieldFIX.ALL <- lmer(SEEDNUM ~  LOC*Mowing + (1|LOC:BLOCK) , data = at_yield.ALL)

summary(Fullat_yieldFIX.ALL)

find_logw0(at_yield.ALL$SEEDNUM)
1

LogFullat_yieldFIX.ALL <- lmer(log(SEEDNUM+1) ~  LOC*Mowing + (1|LOC:BLOCK) , data = at_yield.ALL)

summary(LogFullat_yieldFIX.ALL)
```
####LOC random, LogFullat_yieldRan.ALL

```{r}

Fullat_yieldRan.ALL <- lmer(SEEDNUM ~  Mowing + (1|LOC)+ (1|LOC:BLOCK)   , data = at_yield.ALL)

summary(Fullat_yieldRan.ALL)

#Three way random effect interaction has 0 variance, can be exluded from model

find_logw0(at_yield.ALL$SEEDNUM)
1

LogFullat_yieldRan.ALL <- lmer(log(SEEDNUM+1) ~  Mowing + (1|LOC) +(1|LOC:BLOCK) , data = at_yield.ALL)

summary(LogFullat_yieldRan.ALL)
```
##Residuals
```{r}

##comparison of models with log transformation
list(Fullat_yieldFIX.ALL, Fullat_yieldRan.ALL , LogFullat_yieldFIX.ALL, LogFullat_yieldRan.ALL) %>%
  lapply(resid_panel, qqbands = TRUE, nrow=2) %>%
  wrap_plots() +
  plot_annotation(tag_levels = "A")

# LogFullWbmMod1Fix_ALL1 and LogFullWbmMod1Ran_ALL have best residuals
```
##GLMER
#### Model 1 Fullat_yieldFIX.ALL2

```{r}
Fullat_yieldFIX.ALL2 <- glmer( SEEDNUM ~  LOC*Mowing + (1|LOC:BLOCK) , data = at_yield.ALL, family = poisson())

list(Fullat_yieldFIX.ALL2) %>%
setNames(c("All Sites"))%>%
  lapply(joint_tests)
```
####Model 2 Fullat_yieldFIX.ALL3

```{r}
Fullat_yieldFIX.ALL3 <- glmer(SEEDNUM ~ Mowing+LOC  +(1|LOC:BLOCK), data = at_yield.ALL, family = poisson())

list(FullSdnMod1Ran_ALL1) %>%
setNames(c("All Sites"))%>%
  lapply(joint_tests)
```
####Model 3 Fullat_yieldFIX.ALL4 

```{r}
Fullat_yieldFIX.ALL4 <-  glmer(SEEDNUM ~ Mowing + (1|LOC) +(1|LOC:BLOCK), data = at_yield.ALL, family = poisson())

list(Fullat_yieldFIX.ALL4) %>%
setNames(c("All Sites"))%>%
  lapply(joint_tests)
```
##Residuals
```{r}

##comparison of models 
list(Fullat_yieldFIX.ALL2, Fullat_yieldFIX.ALL3 , Fullat_yieldFIX.ALL4 ) %>%
  lapply(resid_panel, qqbands = TRUE, nrow=2) %>%
  wrap_plots() +
  plot_annotation(tag_levels = "A")

# LogFullWbmMod1Fix_ALL1 and LogFullWbmMod1Ran_ALL have best residuals
```
#####Watch tyler's talk, count data contains too many zeros resulting in overdispersion. Change to hurdle model or inflation model. r package, glmmTMB


#ANOVA
##LMER

####LOC Fixed,  LogFullat_yieldFIX.ALL
```{r}
list(  LogFullat_yieldFIX.ALL) %>%
setNames(c("All Sites"))%>%
  lapply(joint_tests)
```

###Table

```{r}
#Make a table of anova
# Step 1: Create a data frame from your results
results <- data.frame(
  Model_Term = c("LOC", "Mowing", "LOC:Mowing"),
  df1 = c(2, 3, 6),
  df2 = c(9, 699, 699),
  F_ratio = c(19.019, 15.524, 3.963),
  p_value = c("0.0006",  "<.0001", "0.0007")
)

# Step 2: Format the data frame using gt
AnovaSEEDNUMLMERtable_gt <- gt(results) %>%
  tab_header(
    title = "ANOVA results", 
    subtitle = "model = lmer(log(SEEDNUM+1) ~  LOC*Mowing + (1|LOC:BLOCK) , data = at_yield.ALL)"
  ) %>%
  cols_label(
    Model_Term = "Model Term",
    df1 = "df1",
    df2 = "df2",
    F_ratio = "F Ratio",
    p_value = "p Value"
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "black", weight = px(1)),
    locations = cells_body()
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "black", weight = px(2)),
    locations = list(
      cells_title(groups = "title"),
      cells_title(groups = "subtitle"),
      cells_column_labels()
    )
  ) %>%
  tab_options(
    table.border.top.width = px(2),
    table.border.top.color = "black",
    table.border.bottom.width = px(2),
    table.border.bottom.color = "black"
  )
AnovaSEEDNUMLMERtable_gt


```
##GLMER
###Loc fixed,  Fullat_yieldFIX.ALL2
```{r}
list(  Fullat_yieldFIX.ALL2) %>%
setNames(c("All Sites"))%>%
  lapply(joint_tests)
```
###ANOVA table
```{r}
#Make a table of anova
# Step 1: Create a data frame from your results
glm.results <- data.frame(
  Model_Term = c("LOC", "Mowing", "LOC:Mowing"),
  df1 = c(2, 3, 6),
  df2 = c(Inf, Inf, Inf),
  F_ratio = c(43.209, 57.872, 19.996),
  Chisq = c(86.418,173.616, 119.976),
  p_value = c("<.0001",  "<.0001", "<.0001")
)

# Step 2: Format the data frame using gt
AnovaSEEDNUMglmtable_gt <- gt(glm.results) %>%
  tab_header(
    title = "ANOVA results", 
    subtitle = " model = glmer( SEEDNUM ~  LOC*Mowing + (1|LOC:BLOCK) +(1|LOC:BLOCK:Mowing), data = at_yield.ALL, family = poisson())"
  ) %>%
  cols_label(
    Model_Term = "Model Term",
    df1 = "df1",
    df2 = "df2",
    F_ratio = "F Ratio",
    p_value = "p Value"
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "black", weight = px(1)),
    locations = cells_body()
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "black", weight = px(2)),
    locations = list(
      cells_title(groups = "title"),
      cells_title(groups = "subtitle"),
      cells_column_labels()
    )
  ) %>%
  tab_options(
    table.border.top.width = px(2),
    table.border.top.color = "black",
    table.border.bottom.width = px(2),
    table.border.bottom.color = "black"
  )
AnovaSEEDNUMglmtable_gt

```

#MEANs Comparison
##LMER
###LOC Fixed, LogFullat_yieldFIX.ALL
```{r}
summary(LogFullat_yieldFIX.ALL)
```

```{r}
joint_tests(LogFullat_yieldFIX.ALL)
anova(LogFullat_yieldFIX.ALL)

```

```{r}
PooledMeansFix1<-list(LogFullat_yieldFIX.ALL) %>%
setNames(c("All Sites"))%>%
 #map(emmeans, pairwise~LOC, type = "response") 
 #map(emmeans, pairwise ~ Mowing, type = "response") 
 #map(emmeans, pairwise~Weeds, type = "response") 
 map(emmeans, pairwise ~Mowing|LOC, type = "response") 
 #map(emmeans, pairwise~Weeds|LOC, type = "response") 
 # map(emmeans, pairwise~Mowing|Weeds, type = "response") 
PooledMeansFix1
```
##GLMER
### Fullat_yieldFIX.ALL2
```{r}
summary(Fullat_yieldFIX.ALL2)
```

```{r}
joint_tests(Fullat_yieldFIX.ALL2)
anova(Fullat_yieldFIX.ALL2)

```

```{r}
PooledMeansFix1<-list(Fullat_yieldFIX.ALL2) %>%
setNames(c("All Sites"))%>%
 #map(emmeans, pairwise~LOC, type = "response") 
 #map(emmeans, pairwise ~ Mowing, type = "response") 
 #map(emmeans, pairwise~Weeds, type = "response") 
 map(emmeans, pairwise ~Mowing|LOC, type = "response") 
 #map(emmeans, pairwise~Weeds|LOC, type = "response") 
 # map(emmeans, pairwise~Mowing|Weeds, type = "response") 
PooledMeansFix1
```
#FIGURES
##LMER, LogFullat_yieldFIX.ALL


```{r}
summary(LogFullat_yieldFIX.ALL)
```

```{r}
joint_tests(LogFullat_yieldFIX.ALL)
```
####CLD
```{r}

#Fisher's method for comparing means
#Mowing
cld.LogFullat_yieldFIX.ALL <-cld(emmeans(LogFullat_yieldFIX.ALL, ~ Mowing, type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)

#Mowing|LOC
cld.LogFullat_yieldFIX.ALL1 <-cld(emmeans(LogFullat_yieldFIX.ALL, ~ Mowing|LOC, type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)

#Mowing|LOC GLM
cld.Fullat_yieldFIX.ALL1 <-cld(emmeans(LogFullat_yieldFIX.ALL, ~ Mowing|LOC, type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)

```

####Mowing (Significant)
```{r}
cld.LogFullat_yieldFIX.ALL <-cld(emmeans(LogFullat_yieldFIX.ALL, ~ Mowing, type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)


#Graphing

#png("SEEDNUM.Mow.png", res = 300, units = "in", width = 5.2, height = 4)
#left_join(M_SW.ALL,
cld.LogFullat_yieldFIX.ALL %>% 
ggplot(.,aes(Mowing, response, fill=Mowing)) +  
  #facet_wrap(~LOC, labeller = labeller(LOC = c("CU" = "Aurora, NY", "FH" = "Hurley, NY",   "ME"= "Orono, ME", "VT" = "Alburgh, VT", "WI" = "Arlington, WI"  ))) +
 # stat_summary(geom = "bar", fun = "mean") +
  #stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5)+
  geom_bar(stat="identity", 
           position=position_dodge()) + 
  geom_errorbar(aes(ymin=response-SE, ymax=response+SE), width=.2,
                 position=position_dodge(.9))+
 geom_text(aes(label = trimws(.group), size=6.5,y=response +(SE+0.09) )) +
  labs(x="Timing of Mowing", y=expression("Seeds per trap" ~ (0.0078~m^{-2})))+
  scale_x_discrete(labels = c("As-needed\nmowing","Early\nmowing","Late\nmowing",  "No\nmowing"))+
  scale_y_continuous(expand=expansion(mult = c(0.05, 0.1)))+
  scale_fill_viridis(discrete=TRUE, option="E", direction=-1,end=.9,begin=.1)+
  theme_bw()+
  theme(legend.position="none")

#dev.off()
```
####Mowing|LOC (Significant)
```{r}

#Mowing|LOC
cld.LogFullat_yieldFIX.ALL1 <-cld(emmeans(LogFullat_yieldFIX.ALL, ~ Mowing|LOC, type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)

#Graphing

#png("SEEDNUM.Mow.LOC.png", res = 300, units = "in", width = 11.5, height = 4)
#left_join(M_SW.ALL,
cld.LogFullat_yieldFIX.ALL1 %>% 
ggplot(.,aes(Mowing, response, fill=Mowing)) +  
  facet_wrap(~LOC, labeller = labeller(LOC = c("CU" = "Aurora, NY", "FH" = "Hurley, NY", "VT" = "Alburgh, VT"  ))) +
 # stat_summary(geom = "bar", fun = "mean") +
  #stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5)+
  geom_bar(stat="identity", 
           position=position_dodge()) + 
  geom_errorbar(aes(ymin=response-SE, ymax=response+SE), width=.2,
                 position=position_dodge(.9))+
 geom_text(aes(label = trimws(.group), size=6.5,y=response +(SE+1) )) +
  labs(x="Timing of Mowing", y=expression("Weed seed density" ~ (seeds~0.0078~m^{-2})))+
  scale_x_discrete(labels = c("As-needed\nmowing","Early\nmowing","Late\nmowing", "No\nmowing"))+
  scale_y_continuous(expand=expansion(mult = c(0.05, 0.3)))+
  scale_fill_viridis(discrete=TRUE, option="E", direction=-1,end=.9,begin=.1)+
  theme_bw()+
  theme(legend.position="none")

#dev.off()
```
```{r}
#Mowing|LOC GLM
cld.Fullat_yieldFIX.ALL1 <-cld(emmeans(Fullat_yieldFIX.ALL, ~ Mowing|LOC, type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)

#Graphing

png("SEEDNUM.Mow.LOC.GLM.png", res = 300, units = "in", width = 11.5, height = 4)
#left_join(M_SW.ALL,
cld.Fullat_yieldFIX.ALL1 %>% 
ggplot(.,aes(Mowing, emmean, fill=Mowing)) +  
  facet_wrap(~LOC, labeller = labeller(LOC = c("CU" = "Aurora, NY", "FH" = "Hurley, NY", "VT" = "Alburgh, VT"  ))) +
 # stat_summary(geom = "bar", fun = "mean") +
  #stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5)+
  geom_bar(stat="identity", 
           position=position_dodge()) + 
  geom_errorbar(aes(ymin=emmean-SE, ymax=emmean+SE), width=.2,
                 position=position_dodge(.9))+
 geom_text(aes(label = trimws(.group), size=6.5,y=emmean +(SE+1) )) +
  labs(x="Timing of Mowing", y=expression("Seeds per trap" ~ (0.0078~m^{-2})))+
  scale_x_discrete(labels = c("As-needed\nmowing","Early\nmowing","Late\nmowing", "No\nmowing"))+
  scale_y_continuous(expand=expansion(mult = c(0.05, 0.3)))+
  scale_fill_viridis(discrete=TRUE, option="E", direction=-1,end=.9,begin=.1)+
  theme_bw()+
  theme(legend.position="none")

dev.off()
```
#GLM, Fullat_yieldFIX.ALL2

```{r}
summary(Fullat_yieldFIX.ALL2)
```

```{r}
joint_tests(Fullat_yieldFIX.ALL2)
```
####CLD
```{r}

#Fisher's method for comparing means
#Mowing
cld.Fullat_yieldGlmFIX1.ALL <-cld(emmeans(Fullat_yieldFIX.ALL2, ~ Mowing, type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)

#Mowing|LOC
cld.Fullat_yieldGlmFIX1.ALL <-cld(emmeans(Fullat_yieldFIX.ALL2, ~ Mowing|LOC, type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)

#Mowing|LOC GLM
cld.Fullat_yieldFIX.ALL1 <-cld(emmeans(LogFullat_yieldFIX.ALL, ~ Mowing|LOC, type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)

```

####Mowing (Significant)
```{r}
cld.LogFullat_yieldFIX.ALL <-cld(emmeans(LogFullat_yieldFIX.ALL, ~ Mowing, type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)


#Graphing

#png("SEEDNUM.Mow.png", res = 300, units = "in", width = 5.2, height = 4)
#left_join(M_SW.ALL,
cld.LogFullat_yieldFIX.ALL %>% 
ggplot(.,aes(Mowing, response, fill=Mowing)) +  
  #facet_wrap(~LOC, labeller = labeller(LOC = c("CU" = "Aurora, NY", "FH" = "Hurley, NY",   "ME"= "Orono, ME", "VT" = "Alburgh, VT", "WI" = "Arlington, WI"  ))) +
 # stat_summary(geom = "bar", fun = "mean") +
  #stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5)+
  geom_bar(stat="identity", 
           position=position_dodge()) + 
  geom_errorbar(aes(ymin=response-SE, ymax=response+SE), width=.2,
                 position=position_dodge(.9))+
 geom_text(aes(label = trimws(.group), size=6.5,y=response +(SE+0.09) )) +
  labs(x="Timing of Mowing", y=expression("Seeds per trap" ~ (0.0078~m^{-2})))+
  scale_x_discrete(labels = c("As-needed\nmowing","Early\nmowing","Late\nmowing",  "No\nmowing"))+
  scale_y_continuous(expand=expansion(mult = c(0.05, 0.1)))+
  scale_fill_viridis(discrete=TRUE, option="E", direction=-1,end=.9,begin=.1)+
  theme_bw()+
  theme(legend.position="none")

#dev.off()
```
####Mowing|LOC (Significant)
```{r}

#Mowing|LOC
cld.Fullat_yieldGlmFIX1.ALL <-cld(emmeans(Fullat_yieldFIX.ALL2, ~ Mowing|LOC, type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)

#Graphing

#png("SEEDNUM.GLM.Mow.LOC.TRAP.png", res = 300, units = "in", width = 11.5, height = 4)
#left_join(M_SW.ALL,
cld.Fullat_yieldGlmFIX1.ALL %>% 
ggplot(.,aes(Mowing, rate, fill=Mowing)) +  
  facet_wrap(~LOC, labeller = labeller(LOC = c("CU" = "Aurora, NY", "FH" = "Hurley, NY", "VT" = "Alburgh, VT"  ))) +
 # stat_summary(geom = "bar", fun = "mean") +
  #stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5)+
  geom_bar(stat="identity", 
           position=position_dodge()) + 
  geom_errorbar(aes(ymin=rate-SE, ymax=rate+SE), width=.2,
                 position=position_dodge(.9))+
 geom_text(aes(label = trimws(.group), size=6.5,y=rate +(SE+2) )) +
  labs(x="Timing of Mowing", y=expression("Weed seed density" ~ (seeds~0.0078~m^{-2}))) +
  scale_x_discrete(labels = c("As-needed\nmowing","Early\nmowing","Late\nmowing", "No\nmowing"))+
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3)), labels = scales::comma) +
  scale_fill_viridis(discrete=TRUE, option="E", direction=-1,end=.9,begin=.1)+
  theme_bw()+
  theme(legend.position="none")

#dev.off()
```
```{r}
#Mowing|LOC GLM
cld.Fullat_yieldFIX.ALL1 <-cld(emmeans(Fullat_yieldFIX.ALL, ~ Mowing|LOC, type="response"), Letters = letters, sort = TRUE, adjust="none", reversed=TRUE)

#Graphing

png("SEEDNUM.Mow.LOC.GLM.png", res = 300, units = "in", width = 11.5, height = 4)
#left_join(M_SW.ALL,
cld.Fullat_yieldFIX.ALL1 %>% 
ggplot(.,aes(Mowing, emmean, fill=Mowing)) +  
  facet_wrap(~LOC, labeller = labeller(LOC = c("CU" = "Aurora, NY", "FH" = "Hurley, NY", "VT" = "Alburgh, VT"  ))) +
 # stat_summary(geom = "bar", fun = "mean") +
  #stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  #stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5)+
  geom_bar(stat="identity", 
           position=position_dodge()) + 
  geom_errorbar(aes(ymin=emmean-SE, ymax=emmean+SE), width=.2,
                 position=position_dodge(.9))+
 geom_text(aes(label = trimws(.group), size=6.5,y=emmean +(SE+100) )) +
  labs(x="Timing of Mowing", y=expression("Seeds per hectare" ))+
  scale_x_discrete(labels = c("As-needed\nmowing","Early\nmowing","Late\nmowing", "No\nmowing"))+
  scale_y_continuous(expand=expansion(mult = c(0.05, 0.3)))+
  scale_fill_viridis(discrete=TRUE, option="E", direction=-1,end=.9,begin=.1)+
  theme_bw()+
  theme(legend.position="none")

dev.off()
```