---
title: "IMT. Bean Density"
author: "Eric Youngerman"
date: "2024-05-02"
output: html_document
---

#LIBRARY 
```{r}
setwd("/Users/ey239/Library/CloudStorage/Box-Box/ECOBEAN/EXPERIMENTS/Interrow Mowing Trial/IMT 2023/R analysis")

#Load packages 
install.packages("tidyverse")
install.packages("patchwork")
library(readxl)
library(lme4)
library(lmerTest)
library(emmeans)
library(ggplot2)
library(viridis)
library(rstatix)
library(Matrix)
library(multcomp)
library(multcompView)
library(ggResidpanel)
library(tidyverse)
library(car)
library(glmmTMB)
library(DHARMa)
library(patchwork)
MeanPlusSe<-function(x) mean(x)+plotrix::std.error(x)
#find the value to add to x before ln(x)

find_logw0=function(x){c=trunc(log(min(x[x>0],na.rm=T)))
d=exp(c)
return(d)}
```
#LOAD and CLEAN DATA
```{r}
#Load data
#Farmhub
M_SW.FH <- read_excel("~/Library/CloudStorage/Box-Box/ECOBEAN/EXPERIMENTS/Interrow Mowing Trial/IMT 2023/R analysis/FH_IMT_RDATA.2023.xlsx", 
    sheet = "m_sw")

M_SW.FH<- M_SW.FH %>% rename('Mowing'= TRT)
M_SW.FH<- M_SW.FH %>% rename('Weeds'= MICROPLOT)


# Here is the easiest way to to recode to factors. There are shortcuts in tidyverse for situations where you have way more columns to deal with. You can copy and paste this code, and change the "factor" bit to "numeric" or "character" or "POSIX" (ie time series) as needed.

M_SW.FH$Mowing <- as.factor(M_SW.FH$Mowing)
M_SW.FH$BLOCK <- as.factor(M_SW.FH$BLOCK)
M_SW.FH$PLOT <- as.factor(M_SW.FH$PLOT)
M_SW.FH$Weeds <- as.factor(M_SW.FH$Weeds)

#Cornell 
#Load data
M_SW.CU <- read_excel("~/Library/CloudStorage/Box-Box/ECOBEAN/EXPERIMENTS/Interrow Mowing Trial/IMT 2023/R analysis/CU_IMT_RDATA.2023.xlsx", 
    sheet = "m_sw")

M_SW.CU<- M_SW.CU %>% rename('Mowing'= TRT)
M_SW.CU<- M_SW.CU %>% rename('Weeds'= MICROPLOT)

M_SW.CU$Mowing <- as.factor(M_SW.CU$Mowing)
M_SW.CU$BLOCK <- as.factor(M_SW.CU$BLOCK)
M_SW.CU$PLOT <- as.factor(M_SW.CU$PLOT)
M_SW.CU$Weeds <- as.factor(M_SW.CU$Weeds)

#Vermont
#Load data
M_SW.VT <- read_excel("~/Library/CloudStorage/Box-Box/ECOBEAN/EXPERIMENTS/Interrow Mowing Trial/IMT 2023/R analysis/VT_IMT_RDATA.2023.xlsx", 
    sheet = "m_sw")

M_SW.VT<- M_SW.VT %>% rename('Mowing'= TRT)
M_SW.VT<- M_SW.VT %>% rename('Weeds'= MICROPLOT)

M_SW.VT$Mowing <- as.factor(M_SW.VT$Mowing)
M_SW.VT$BLOCK <- as.factor(M_SW.VT$BLOCK)
M_SW.VT$PLOT <- as.factor(M_SW.VT$PLOT)
M_SW.VT$Weeds <- as.factor(M_SW.VT$Weeds)

#Wisconsin
#Load data
M_SW.WI <- read_excel("~/Library/CloudStorage/Box-Box/ECOBEAN/EXPERIMENTS/Interrow Mowing Trial/IMT 2023/R analysis/WI_IMT_RDATA.2023.xlsx", 
    sheet = "m_sw")

M_SW.WI<- M_SW.WI %>% rename('Mowing'= TRT)
M_SW.WI<- M_SW.WI %>% rename('Weeds'= MICROPLOT)

M_SW.WI$Mowing <- as.factor(M_SW.WI$Mowing)
M_SW.WI$BLOCK <- as.factor(M_SW.WI$BLOCK)
M_SW.WI$PLOT <- as.factor(M_SW.WI$PLOT)
M_SW.WI$Weeds <- as.factor(M_SW.WI$Weeds)

#MAINE
#Load data
M_SW.ME <- read_excel("~/Library/CloudStorage/Box-Box/ECOBEAN/EXPERIMENTS/Interrow Mowing Trial/IMT 2023/R analysis/ME_IMT_RDATA.2023.xlsx", 
    sheet = "m_sw")

M_SW.ME<- M_SW.ME %>% rename('Mowing'= TRT)
M_SW.ME<- M_SW.ME %>% rename('Weeds'= MICROPLOT)

M_SW.ME$Mowing <- as.factor(M_SW.ME$Mowing)
M_SW.ME$BLOCK <- as.factor(M_SW.ME$BLOCK)
M_SW.ME$PLOT <- as.factor(M_SW.ME$PLOT)
M_SW.ME$Weeds <- as.factor(M_SW.ME$Weeds)

#Combine all data

M_SW.ALL <- bind_rows(M_SW.CU, M_SW.FH, M_SW.VT, M_SW.WI, M_SW.ME)

M_SW.ALL$Mowing <- as.factor(M_SW.ALL$Mowing)
M_SW.ALL$BLOCK <- as.factor(M_SW.ALL$BLOCK)
M_SW.ALL$PLOT <- as.factor(M_SW.ALL$PLOT)
M_SW.ALL$Weeds <- as.factor(M_SW.ALL$Weeds)

#Combine all sites, No Maine

M_SW.ALLNM <- bind_rows(M_SW.CU, M_SW.FH, M_SW.VT, M_SW.WI)

M_SW.ALLNM$Mowing <- as.factor(M_SW.ALLNM$Mowing)
M_SW.ALLNM$BLOCK <- as.factor(M_SW.ALLNM$BLOCK)
M_SW.ALLNM$PLOT <- as.factor(M_SW.ALLNM$PLOT)
M_SW.ALLNM$Weeds <- as.factor(M_SW.ALLNM$Weeds)

```
#LEVENE'S TEST
```{r}
leveneTest((DEN1) ~ LOC, data = M_SW.ALL)
#Levene's test was significant  p = 3.502e-08 *** so sites need to be analyzed separately

leveneTest((DEN1) ~ LOC, data = M_SW.ALL)
#Levene's test was significant  p = 3.502e-08 *** so sites need to be analyzed separately

```
#MODEL TESTING
##All sites,FullDenMod1_ALL 

```{r}

#lmer

FullDenMod1_ALL <- lmer(DEN1 ~  LOC*Mowing*Weeds + (1|LOC:BLOCK)+  (1|LOC:BLOCK:Mowing)  , data = M_SW.ALL)

# 

summary(FullDenMod1_ALL)
joint_tests(FullDenMod1_ALL)
resid_panel(FullDenMod1_ALL)

joint_tests(FullDenMod1_ALL)

find_logw0(M_SW.ALL$DEN1)


##comparison of model with and without log transformation
list(FullWbmMod1_ALL , LogFullWbmMod1_ALL) %>%
  lapply(resid_panel, qqbands = TRUE, nrow=2) %>%
  wrap_plots() +
  plot_annotation(tag_levels = "A")

# FullDenMod1_ALL has better residuals## Farm hub,FullDenMod1_FH
```
#Farmhub, FullDenMod1_FH
```{r}

#lmer

FullDenMod1_FH <- lmer(DEN1 ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing)  , data = M_SW.FH)

SqrtFullDenMod1_FH <- lmer(sqrt(DEN1) ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing) , data = M_SW.FH)

find_logw0(M_SW.FH$DEN1)

LogFullDenMod1_FH <- lmer(log(DEN1 + 59874.14) ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing)  , data = M_SW.FH)

##comparison of model with and without log transformation
list(FullDenMod1_FH , SqrtFullDenMod1_FH, LogFullDenMod1_FH) %>%
  lapply(resid_panel, qqbands = TRUE, nrow=2) %>%
  wrap_plots() +
  plot_annotation(tag_levels = "A")

# No difference between residuals, use FullDenMod1_FH
```
## Cornell,FullDenMod1_CU
```{r}

#lmer

FullDenMod1_CU <- lmer(DEN1 ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing)  , data = M_SW.CU)

SqrtFullDenMod1_CU <- lmer(sqrt(DEN1) ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing) , data = M_SW.CU)

find_logw0(M_SW.CU$DEN1)

LogFullDenMod1_CU <- lmer(log(DEN1 + 59874.14) ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing)  , data = M_SW.CU)

##comparison of model with and without log transformation
list(FullDenMod1_CU , SqrtFullDenMod1_CU, LogFullDenMod1_CU) %>%
  lapply(resid_panel, qqbands = TRUE, nrow=2) %>%
  wrap_plots() +
  plot_annotation(tag_levels = "A")

# No difference between residuals, use FullDenMod1_CU

```
## Vermont, FullDenMod1_VT
```{r}

FullDenMod1_VT <- lmer(DEN1 ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing)  , data = M_SW.VT)

SqrtFullDenMod1_VT <- lmer(sqrt(DEN1) ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing) , data = M_SW.VT)

find_logw0(M_SW.VT$DEN1)

LogFullDenMod1_VT <- lmer(log(DEN1 + 22026.47) ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing)  , data = M_SW.VT)

##comparison of model with and without log transformation
list(FullDenMod1_VT , SqrtFullDenMod1_VT, LogFullDenMod1_VT) %>%
  lapply(resid_panel, qqbands = TRUE, nrow=2) %>%
  wrap_plots() +
  plot_annotation(tag_levels = "A")

# No difference between residuals, use FullDenMod1_VT
```
## Wisconsin, FullDenMod1_WI
```{r}

#lmer

FullDenMod1_WI <- lmer(DEN1 ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing)  , data = M_SW.WI)

SqrtFullDenMod1_WI <- lmer(sqrt(DEN1) ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing) , data = M_SW.WI)

find_logw0(M_SW.WI$DEN1)

LogFullDenMod1_WI <- lmer(log(DEN1 + 59874.14) ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing)  , data = M_SW.WI)

##comparison of model with and without log transformation
list(FullDenMod1_WI , SqrtFullDenMod1_WI, LogFullDenMod1_WI) %>%
  lapply(resid_panel, qqbands = TRUE, nrow=2) %>%
  wrap_plots() +
  plot_annotation(tag_levels = "A")

# No difference between residuals, use FullDenMod1_WI
```
## Maine,FullDenMod1_ME 
```{r}

#lmer

FullDenMod1_ME <- lmer(DEN1 ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing)  , data = M_SW.ME)

SqrtFullDenMod1_ME <- lmer(sqrt(DEN1) ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing) , data = M_SW.ME)

find_logw0(M_SW.ME$DEN1)

LogFullDenMod1_ME <- lmer(log(DEN1 + 59874.14) ~ BLOCK + Mowing*Weeds + (1|BLOCK:Mowing)  , data = M_SW.ME)

##comparison of model with and without log transformation
list(FullDenMod1_ME , SqrtFullDenMod1_ME, LogFullDenMod1_ME) %>%
  lapply(resid_panel, qqbands = TRUE, nrow=2) %>%
  wrap_plots() +
  plot_annotation(tag_levels = "A")

# No difference between residuals, use FullDenMod1_ME

# FullBydMod1_VT has better residuals
```
#ANOVA

```{r}

list( FullDenMod1_FH, FullDenMod1_CU, FullDenMod1_VT , LogFullDenMod1_WI, FullDenMod1_ME ) %>%
setNames(c("Farm hub", "Cornell", "Vermont", "Wisconsin", "Maine"))%>%
  lapply(joint_tests)

# Weed are significant at Cornell and Wisconsin
```
#MEANs Comparison

```{r}
all_means <- list(FullDenMod1_FH, FullDenMod1_CU, FullDenMod1_VT , LogFullDenMod1_WI, FullDenMod1_ME ) %>%
setNames(c( "Farm hub", "Cornell", "Vermont", "Wisconsin", "Maine"))%>%
  #map(emmeans, pairwise~ Weeds | Mowing , type = "response") 

 map(emmeans, pairwise~ Mowing| Weeds , type = "response") 

```

```{r}
all_means$`Cornell`$emmeans

#all_means$`Farm hub`$contrasts
```
#FIGURES
##All sites
```{r}
#Tukey method for comparing means
cld.FullDenMod1_ALL.Mowing <-cld(emmeans(FullDenMod1_ALL, ~ Mowing), Letters = "abcde", sort = FALSE, reversed = TRUE)

cld.FullDenMod1_ALL.Weeds <-cld(emmeans(FullDenMod1_ALL, ~ Weeds), Letters = "abcde", sort = FALSE, reversed = TRUE)

#Fisher's method for comparing means
cld.FullDenMod1_ALL.Mowingb <-cld(emmeans(FullDenMod1_ALL, ~ Mowing), Letters = "abcde", sort = FALSE, adjust="none", reversed=TRUE)

cld.FullDenMod1_ALL.Weedsb <-cld(emmeans(FullDemMod1_ALL, ~ Weeds), Letters = "abcde", sort = FALSE, adjust="none", reversed=FALSE)

#Graphing
#Using Fisher's method for comparing means

png("FullDenMod1Mow_ALL.png", res = 300, units = "in", width = 5.2, height = 4)
left_join(M_SW.ALL,cld.FullDenMod1_ALL.Mowingb) %>% 
ggplot(.,aes(Mowing, DEN1, fill=Mowing, ))+  facet_wrap(~LOC,) +
  
  stat_summary(geom = "bar", fun = "mean") +
  stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=2.5,vjust=-0.5)+
  
  labs(x="Timing of Mowing", y=expression("Dry bean density" ~ (plants ~ ha^{-1})))+
  scale_x_discrete(labels = c("As-needed\nmowing", "Early\nmowing",
                              "Late\nmowing", "No\nmowing"))+
  scale_y_continuous(expand=expansion(mult = c(0.05, 0.3)))+
  scale_fill_viridis(discrete=TRUE, option="E", direction=-1,end=.9,begin=.1)+
  theme_bw()+
  theme(legend.position="none",
        axis.text.x = element_text(size = 5))
dev.off()
```
```{r}
png("FullDenMod1Mow1_ALL.png", res = 300, units = "in", width = 5.2, height = 4)
left_join(M_SW.ALL,cld.FullDenMod1_ALL.Mowingb) %>% 
ggplot(.,aes(Mowing, DEN1, fill=Mowing, )) +
  
  stat_summary(geom = "bar", fun = "mean") +
  stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=5,vjust=-0.5)+
  
  labs(x="Timing of Mowing", y=expression("Dry bean density" ~ (plants ~ ha^{-1})))+
  scale_x_discrete(labels = c("As-needed\nmowing", "Early\nmowing",
                              "Late\nmowing", "No\nmowing"))+
  scale_y_continuous(expand=expansion(mult = c(0.05, 0.3)))+
  scale_fill_viridis(discrete=TRUE, option="E", direction=-1,end=.9,begin=.1)+
  theme_bw()+
  theme(legend.position="none")
      
dev.off()
##Farm hub

```{r}
#Tukey method for comparing means
cld.LogFullDenMod1_FH.Mowing <-cld(emmeans(LogFullDenMod1_FH, ~ Mowing), Letters = "abcde", sort = FALSE, reversed = TRUE)

cld.LogFullDenMod1_FH.Weeds <-cld(emmeans(LogFullDenMod1_FH, ~ Weeds), Letters = "abcde", sort = FALSE, reversed = TRUE)

#Fisher's method for comparing means
cld.LogFullDenMod1_FH.Mowingb <-cld(emmeans(LogFullDenMod1_FH, ~ Mowing), Letters = "abcde", sort = FALSE, adjust="none", reversed=TRUE)

cld.LogFullDenMod1_FH.Weedsb <-cld(emmeans(LogFullDenMod1_FH, ~ Weeds), Letters = "abcde", sort = FALSE, adjust="none", reversed=FALSE)

#Graphing
#Using Fisher's method for comparing means

png("LogFullDEnMod1_FH.png", res = 300, units = "in", width = 5.2, height = 4)
left_join(M_SW.FH, cld.LogFullDenMod1_FH.Mowingb) %>% 
ggplot(.,aes(Mowing, DEN1, fill=Mowing))+
  stat_summary(geom = "bar", fun = "mean") +
  stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5)+
  labs(x="Treatment", y=expression("Dry bean density" ~ (plants ~ ha^{-1})))+
  scale_x_discrete(labels = c("As-needed\nmowing", "Early\nmowing",
                              "Late\nmowing", "No\nmowing"))+
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3)), 
                     labels = scales::comma) +  # Format labels with commas
  scale_fill_viridis(discrete = TRUE, option = "E", direction = -1, end = 0.9, begin = 0.1) +
  theme_bw() +
  theme(legend.position = "none")
dev.off()


```
##Cornell
```{r}
#Tukey method for comparing means
cld.LogFullDenMod1_CU.Mowing <-cld(emmeans(LogFullDenMod1_CU, ~ Mowing), Letters = "abcde", sort = FALSE, reversed = TRUE)

cld.LogFullDenMod1_CUWeeds <-cld(emmeans(LogFullDenMod1_CU, ~ Weeds), Letters = "abcde", sort = FALSE, reversed = TRUE)

#Fisher's method for comparing means
cld.LogFullDenMod1_CU.Mowingb <-cld(emmeans(LogFullDenMod1_CU, ~ Mowing), Letters = "abcde", sort = FALSE, adjust="none", reversed=TRUE)

cld.LogFullDenMod1_CU.Weedsb <-cld(emmeans(LogFullDenMod1_CU, ~ Weeds), Letters = "abcde", sort = FALSE, adjust="none", reversed=FALSE)

#Graphing
#Using Fisher's method for comparing means

png("LogFullDEnMod1_CU.png", res = 300, units = "in", width = 5.2, height = 4)
left_join(M_SW.CU, cld.LogFullDenMod1_CU.Mowingb) %>% 
ggplot(.,aes(Mowing, DEN1, fill=Mowing))+
  stat_summary(geom = "bar", fun = "mean") +
  stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5)+
  labs(x="Treatment", y=expression("Dry bean density" ~ (plants ~ ha^{-1})))+
  scale_x_discrete(labels = c("As-needed\nmowing", "Early\nmowing",
                              "Late\nmowing", "No\nmowing"))+
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3)), 
                     labels = scales::comma) +  # Format labels with commas
  scale_fill_viridis(discrete = TRUE, option = "E", direction = -1, end = 0.9, begin = 0.1) +
  theme_bw() +
  theme(legend.position = "none")
dev.off()

```
##Vermont


```{r}
#Tukey method for comparing means
cld.LogFullDenMod1_VT.Mowing <-cld(emmeans(LogFullDenMod1_VT, ~ Mowing), Letters = "abcde", sort = FALSE, reversed = TRUE)

cld.LogFullDenMod1_VT.Weeds <-cld(emmeans(LogFullDenMod1_VT, ~ Weeds), Letters = "abcde", sort = FALSE, reversed = TRUE)

#Fisher's method for comparing means
cld.LogFullDenMod1_VT.Mowingb <-cld(emmeans(LogFullDenMod1_VT, ~ Mowing), Letters = "abcde", sort = FALSE, adjust="none", reversed=TRUE)

cld.LogFullDenMod1_VT.Weedsb <-cld(emmeans(LogFullDenMod1_VT, ~ Weeds), Letters = "abcde", sort = FALSE, adjust="none", reversed=FALSE)

#Graphing
#Using Fisher's method for comparing means

png("LogFullDEnMod1_VT.png", res = 300, units = "in", width = 5.2, height = 4)
left_join(M_SW.VT, cld.LogFullDenMod1_VT.Mowingb) %>% 
ggplot(.,aes(Mowing, DEN1, fill=Mowing))+
  stat_summary(geom = "bar", fun = "mean") +
  stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5)+
  labs(x="Treatment", y=expression("Dry bean density" ~ (plants ~ ha^{-1})))+
  scale_x_discrete(labels = c("As-needed\nmowing", "Early\nmowing",
                              "Late\nmowing", "No\nmowing"))+
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3)), 
                     labels = scales::comma) +  # Format labels with commas
  scale_fill_viridis(discrete = TRUE, option = "E", direction = -1, end = 0.9, begin = 0.1) +
  theme_bw() +
  theme(legend.position = "none")
dev.off()

```
##Wisconsin 

```{r}
#Tukey method for comparing means
cld.LogFullDenMod1_WI.Mowing <-cld(emmeans(LogFullDenMod1_WI, ~ Mowing), Letters = "abcde", sort = FALSE, reversed = TRUE)

cld.LogFullDenMod1_WI.Weeds <-cld(emmeans(LogFullDenMod1_WI, ~ Weeds), Letters = "abcde", sort = FALSE, reversed = TRUE)

#Fisher's method for comparing means
cld.LogFullDenMod1_WI.Mowingb <-cld(emmeans(LogFullDenMod1_WI, ~ Mowing), Letters = "abcde", sort = FALSE, adjust="none", reversed=TRUE)

cld.LogFullDenMod1_WI.Weedsb <-cld(emmeans(LogFullDenMod1_WI, ~ Weeds), Letters = "abcde", sort = FALSE, adjust="none", reversed=FALSE)

#Graphing
#Using Fisher's method for comparing means

png("LogFullDEnMod1_WI.png", res = 300, units = "in", width = 5.2, height = 4)
left_join(M_SW.WI, cld.LogFullDenMod1_WI.Mowingb) %>% 
ggplot(.,aes(Mowing, DEN1, fill=Mowing))+
  stat_summary(geom = "bar", fun = "mean") +
  stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5)+
  labs(x="Treatment", y=expression("Dry bean density" ~ (plants ~ ha^{-1})))+
  scale_x_discrete(labels = c("As-needed\nmowing", "Early\nmowing",
                              "Late\nmowing", "No\nmowing"))+
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3)), 
                     labels = scales::comma) +  # Format labels with commas
  scale_fill_viridis(discrete = TRUE, option = "E", direction = -1, end = 0.9, begin = 0.1) +
  theme_bw() +
  theme(legend.position = "none")
dev.off()


```

##Maine


```{r}
#Tukey method for comparing means
cld.LogFullDenMod1_ME.Mowing <-cld(emmeans(LogFullDenMod1_ME, ~ Mowing), Letters = "abcde", sort = FALSE, reversed = TRUE)

cld.LogFullDenMod1_ME.Weeds <-cld(emmeans(LogFullDenMod1_ME, ~ Weeds), Letters = "abcde", sort = FALSE, reversed = TRUE)

#Fisher's method for comparing means
cld.LogFullDenMod1_ME.Mowingb <-cld(emmeans(LogFullDenMod1_ME, ~ Mowing), Letters = "abcde", sort = FALSE, adjust="none", reversed=TRUE)

cld.LogFullDenMod1_ME.Weedsb <-cld(emmeans(LogFullDenMod1_ME, ~ Weeds), Letters = "abcde", sort = FALSE, adjust="none", reversed=FALSE)

#Graphing
#Using Fisher's method for comparing means

png("LogFullDEnMod1_ME.png", res = 300, units = "in", width = 5.2, height = 4)
left_join(M_SW.ME, cld.LogFullDenMod1_ME.Mowingb) %>% 
ggplot(.,aes(Mowing, DEN1, fill=Mowing))+
  stat_summary(geom = "bar", fun = "mean") +
  stat_summary(geom = "errorbar", fun.data = "mean_se",width = 0.1)+
  stat_summary(geom="text", fun = "MeanPlusSe", aes(label= trimws(.group)),size=6.5,vjust=-0.5)+
  labs(x="Treatment", y=expression("Dry bean density" ~ (plants ~ ha^{-1})))+
  scale_x_discrete(labels = c("As-needed\nmowing", "Early\nmowing",
                              "Late\nmowing", "No\nmowing"))+
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.3)), 
                     labels = scales::comma) +  # Format labels with commas
  scale_fill_viridis(discrete = TRUE, option = "E", direction = -1, end = 0.9, begin = 0.1) +
  theme_bw() +
  theme(legend.position = "none")
dev.off()



```